---
title: "KQ1"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
output:
  html_document:
    font: Source Sans Pro
    theme: cosmo
    anchor_sections: TRUE
    toc_float: 
      collapsed: true
      smooth_scroll: TRUE
    toc_depth: 3
    linkcolor: blue
  latex_engine: xelatex
  pdf_document:
    toc: yes
    toc_depth: '3'
# bibliography: "bib/kq1.bib"
csl: jama.csl
link-citations: yes
workflowr:
  suppress_report: false
nocite: '@*'
---

```{=html}
<style type="text/css">
  body{
  font-size: 9.5pt;
  font-family: Source Sans Pro;
}

.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  color: #090909;
  background-color: #0909093d;
}

.lightable-classic.lightable-hover tbody tr:hover {
    background-color: #c5d4e4;
}
.btn-xs, .btn-group-xs>.btn { 
display: none; 
}

.btn-default {
display: none !important; 
}

<!-- :target {  /* fix target location so caption appears */ -->
<!--     display: block;     -->
<!--     position: relative;      -->
<!--     top: 10px; -->
<!--     visibility: hidden; -->
<!-- } -->

</style>
```

```{r setup, include = FALSE} 
## • (updated 2021/11/10 21:46) setup -------------------------------------
knitr::opts_chunk$set(echo = TRUE)
source("code/readfiles_nmb_102721.R")
```

```{r data, include = FALSE, eval = TRUE}
## • (updated 2021/11/16 09:02) create diag_ba.dat refids -----------------
## (updated 2022/01/07 08:54) verify correct refids -----------------------
tech_sc_refids <- study_char.dat %>% 
  filter(!is.na(tech_perf)) %>% 
  pull(refid) %>% 
  unique()

(tech_sa_refids <- study_arm.dat %>% 
  filter(!is.na(arm_tech_perf)) %>% 
# check discrepancy
  filter(!refid %in% tech_sc_refids) %>%
  pull(refid) %>%
  unique())

rm(tech_sa_refids, tech_sc_refids)

## (updated 2022/01/07 08:55) tech_perf refids verified -------------------
tech_refids <- study_arm.dat %>% 
  filter(!is.na(arm_tech_perf)) %>% 
  pull(refid) %>%
  unique()

# write refids to use in risk of bias
write_csv(tibble(tech_refids), "data/tech_refids.csv", na = "")

contin_tech.dat <- contin.dat %>% 
  filter(refid %in% tech_refids)

dichot_tech.dat <- dichot.dat %>% 
  filter(refid %in% tech_refids)

likert_tech.dat <- likert.dat %>% 
  filter(refid %in% tech_refids)
```

# **Included Studies** 

<br/>

<font size = 4> Table `r table_n`. Number of included studies according to age and design. </font>

```{r tablesIncluded, include = TRUE, echo = FALSE} 
## • (updated 2021/11/13 07:21) study_char_diag.dat -----------------------
# list of studies, age, surgical/non surgical, design 
study_char.dat %>% 
  filter(refid %in% tech_refids) %>% 
  group_by(age, design, .groups = "drop") %>%
  summarise(total = n()) %>%
  ungroup() %>%
  arrange(age, design) %>%
  group_by(age, .groups = "drop") %>%
  mutate(row = row_number()) %>%
  ungroup() %>%
  janitor::adorn_totals("row") %>%
  mutate(
    age = ifelse(row != 1, NA, age),
    design = case_when(
      design == "rct" ~ "RCT",
      design == "crossover" ~ "Crossover",
      design == "cluster" ~ "Cluster",
      design == "nrsi" ~ "Nonrandomized",
      design == "prospect_coh" ~ "Prospective Cohort",
      design == "retrospect_coh" ~ "Retrospective Cohort",
      design == "casecontrol" ~ "Case-Control",
      design == "other" ~ "Before-After",
      design == "fully_paired" ~ "Fully Paired"),
      age = ifelse(row_number() == n(), "Total", age)
  ) %>%
  select(age, design, total) %>%
  kbl(
    booktabs = T, align = c("llr"),
    col.names = c("Age", "Design", "N")
  ) %>%
  row_spec(c(0, 4), bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "8em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "3em") %>% 
  footnote(
    general = "RCT: randomized controlled trial.",
    # alphabet = c("Footnote a", "Footnote b", ...),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

## *List of Studies*

<br/>

<font size = 4> Table `r table_n`. Included studies, design, enrollment, centers, country, and surgery (see [References](#references) for citations). </font>

```{r studiesIncludedList, echo = FALSE, include = TRUE}
## • (updated 2021/11/16 09:06) included_studies.dat ----------------------
included_studies.dat <- study_char.dat %>%
  filter(refid %in% tech_refids) %>%
  mutate(
    design_l = as.character(design),
    design_l = factor(design_l,
      levels = c("rct", "fully_paired", "nrsi", "prospect_coh", "retrospect_coh"),
      labels = c("RCT", "Fully paired", "NRSI", "Prospective Cohort", "Retrospective Cohort")
    ),
    across(surg_various:surg_other, ~ str_replace(.x, "surg_", "")),
    across(surg_various:surg_other, ~ str_c(.x, ", ")),
    across(surg_various:surg_other, ~ firstup(.x)),
    across(surg_various:surg_other, ~ replace_na(.x, "")),
    surg_list = ifelse(grepl("abdom", surg_list), "Abdominal, ", ""),
    surgs = str_c(surg_various, surg_car, surg_cr, surg_gyn, surg_gi, surg_gen, surg_headneck, surg_hep, surg_neuro, surg_opth, surg_oralmax, surg_ortho, surg_otolar, surg_plastic, surg_thor, surg_urol, surg_list),
    surgs = str_replace(surgs, "Otolar", "ENT"),
    surgs = str_replace(surgs, "Headneck", "ENT"),
    surgs = str_sub(surgs, 1, nchar(surgs) - 2),
    country = ifelse(grepl("USA", country), "USA", country),
    country = ifelse(grepl("UK", country), "UK", country),
    country = ifelse(!is.na(non_vh_hdi), str_c(country, "^a^"), country),
    # design = case_when(
    #   design == "rct" ~ "RCT",
    #   design == "fully_paired" ~ "Fully paired"
    # ),
    # design = ifelse(study == "Claudius 2009", "Fully paired (random subset)", design)
  ) %>%
  select(refid, study_l, year, age, design, design_l, n_analyze, country, centers, non_vh_hdi, surgs) %>%
  arrange(age, design_l, year) 

## • (updated 2021/11/16 09:06) kable -------------------------------------
temp <- included_studies.dat %>%
  arrange(age, design_l, study_l) %>% 
  select(study_l, refid, age, design_l) %>% 
  group_by(age, design_l) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(end = cumsum(n),
         start = end - n + 1) %>% 
  select(age, design_l, start, end)

rm(temp)

included_studies.dat %>% 
  select(refid, study_l, n_analyze, centers, country, surgs) %>% 
  kbl(
    booktabs = T, align = c("llccll"), escape = TRUE, # format = "latex",
    col.names = c("            ID", "Study", "Analyzed (N)", "Centers", "Country^a^", "Surgery")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "6em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "6em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "10em") %>%
  column_spec(6, width = "12em") %>%
  pack_top(., "Adult", 1, 24) %>%
  pack_sub(., "RCT", 1, 5) %>% 
  pack_sub(., "Fully Paired", 6, 23) %>% 
  pack_sub(., "Prospective Cohort", 24, 24) %>% 
  footnote(
    general = "RCT: randomized controlled trial.",
    alphabet = c(
      "Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/><br/>

# **Study/Participant Detail** 

<br/>

### *Study Characteristics* 

<br>

<font size = 4> Table `r table_n`. Study characteristics. </font>

```{r createStudyCharTable, include = FALSE, echo = FALSE, eval = FALSE} 
## (updated 2021/11/10 15:31) 2021/11/10 15:31 ----------------------------
# Hmisc::latex(Hmisc::describe(study_char_diag.dat), file = "/Users/mgrant/Desktop/temp.tex")
study_char_table <- study_char_diag.dat %>%
  mutate(
    dates = str_c(date_start, "-", date_end),
    country = countrycode::countryname(country, destination = "iso3c"),
    low_r = noquote(if_else(non_vh_hdi == "yes", "\U2022", "", "")),
    n = n_enrolled,
    n_anal = n_analyze,
    pilot = noquote(if_else(pilot == "yes", "\U2022", "", "")),
    gen = noquote(if_else(!is.na(general), "\U2022", "", "")),
    reg = noquote(if_else(!is.na(regional), "\U2022", "", "")),
    registered = noquote(if_else(registered == "yes", "\U2022", "", ""))) %>% 
  mutate(
    across(surg_various:surg_other, ~ str_replace(.x, "surg_", "")),
    across(surg_various:surg_other, ~ str_c(.x, ", ")),
    across(surg_various:surg_other, ~ firstup(.x)),
    across(surg_various:surg_other, ~ replace_na(.x, "")),
    surg_list = ifelse(grepl("abdom", surg_list), "Abdominal, ", ""),
    surgs = str_c(surg_various, surg_car, surg_cr, surg_gyn, surg_gi, surg_gen, surg_headneck, surg_hep, surg_neuro, surg_opth, surg_oralmax, surg_ortho, surg_otolar, surg_plastic, surg_thor, surg_urol, surg_list),
    surgs = str_replace(surgs, "Otolar", "ENT"),
    surgs = str_replace(surgs, "Headneck", "ENT"),
    surgs = str_sub(surgs, 1, nchar(surgs) - 2)
  ) %>%
  select(refid, age, year, study, dates, country, low_r, n, centers, low_r, pilot, surgs, nct) %>% 
  arrange(age,year)



  arrange(age, desc(surg_nosurg), design, year, study) %>%
  select(refid, age, surg_nosurg, design, study, dates, country, n, pilot, setting, gen, reg, sed, surg, registered)

```

```{r studyCharKable, echo = FALSE, include = FALSE, eval = FALSE} 
## (updated 2021/01/12 19:27) ---------------------------------------------
study_char_table %>%
  select(!c(refid, age, surg_nosurg, design)) %>% 
  kbl(booktabs = T, align = c("lcccccccclc"), 
      # format = "latex",
      col.names = c("\\ \\ \\ \\ \\ \\ \\ Study", "Dates", "Country", " (N\\) ", "Pilot", 
                    "Setting", "Gen", "Reg", "Sed", "Type of Surgery", "Registered")) %>%
  add_header_above(c(" " = 3, "Enrolled" = 1, " " = 2, "Anesthetic" = 3, " " = 2), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_classic(full_width = TRUE, html_font = opt_font, position = "left", "hover") %>% 
  kable_styling(bootstrap_options = opt_boot) %>% 
  column_spec(1, width = "15em") %>% 
  # column_spec(2, width = "2em") %>% 
  pack_top(., "Adult, Surgical", 1, 99) %>% 
  pack_sub(., "RCT", 1, 84) %>% 
  pack_sub(., "Nonrandomized Studies of Interventions", 85, 92) %>% 
  pack_sub(., "Prospective Cohort", 93, 95) %>%
  pack_sub(., "Retrospective Cohort", 96, 97) %>% 
  pack_sub(., "Case-control", 98, 98) %>% 
  pack_sub(., "Before-after", 99, 99) %>% 
  pack_top(., "Adult, Non-surgical", 100, 111) %>% 
  pack_sub(., "RCT", 100, 100) %>%
  pack_sub(., "Crossover", 101, 109) %>%
  pack_sub(., "Nonrandomized Studies of Interventions", 110, 111) %>% 
  pack_top(., "Pediatric, Surgical", 112, 120) %>% 
  pack_sub(., "RCT", 112, 119) %>% 
  # pack_sub(., "Nonrandomized Studies of Interventions", 119, 119) %>% 
  pack_sub(., "Prospective Cohort", 120, 120) %>% 
  pack_top(., "Pediatric, Non-surgical", 121, 123) %>% 
  pack_sub(., "RCT", 121, 121) %>%
  pack_sub(., "Crossover", 122, 122) %>%
  pack_sub(., "Prospective Cohort", 123, 123) %>% 
  footnote(general_title = "",
    general = "Gen: general; Reg: regional; Sed: sedation; Hosp: hospital; Amb: ambulatory; TKA: total knee arthroplasty; THA: total hip arthroplasty.",
    alphabet = c("Multiple publications from the same study."),
    footnote_as_chunk = FALSE) # %>% 

table_n <- tab_inc()
```

<br/>

# **Risk of Bias** 

<br/>

### *Diagnostic Studies*

<br>

<font size = 4> Figure `r figure_n`. Summary risk of bias appraisal (QUADAS-2) for included studies. </font>

<img src="assets/kq1_quadas_summary.svg" style="width:700px;" align="left"/>

<br clear="all" />

```{r}
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Individual study risk of bias appraisal (QUADAS-2) for included diagnostic studies. </font>

<img src="assets/kq1_quadas_traffic.svg" style="width:565px;" align="left"/>
<!-- <img src="assets/kq1_quadas_traffic.svg" style="width: 75%; height: 1000px;" align="left"/> -->

```{r}
figure_n <- fig_inc()
```
<br clear="all" />

<br/>

### *RCTs Clinical Outcomes*

<br>

<font size = 4> Figure `r figure_n`. Summary risk of bias appraisal for included RCTs reporting clinical outcomes. </font>

<img src="assets/kq1_rob_clin_out.svg" style="width:750px;" align="left"/>

<br clear="all" />

```{r}
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Individual study risk of bias appraisal for included RCTs. </font>

<img src="assets/kq1_rob_clin_out_traffic.svg" style="width:650px;" align="left"/>

```{r}
figure_n <- fig_inc()
```
<br clear="all" />


<hr style="height:2px;border-width:0;color:gray;background-color:gray">

<br>

# References 
<a id="references"></a>

<br/>




