---
title: "KQ1"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
output:
  html_document:
    font: Source Sans Pro
    theme: cosmo
    anchor_sections: TRUE
    toc_float: 
      collapsed: true
      smooth_scroll: TRUE
    toc_depth: 3
    linkcolor: blue
  latex_engine: xelatex
  pdf_document:
    toc: yes
    toc_depth: '3'
bibliography: "bib/kq1.bib"
csl: jama.csl
link-citations: yes
workflowr:
  suppress_report: false
nocite: '@*'
---

```{=html}
<style type="text/css">
  body{
  font-size: 9.5pt;
  font-family: Source Sans Pro;
}

.caption {
  font-size: 15px;
}

.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  color: #090909;
  background-color: #0909093d;
}

.lightable-classic.lightable-hover tbody tr:hover {
    background-color: #c5d4e4;
}
.btn-xs, .btn-group-xs>.btn { 
display: none; 
}

.btn-default {
display: none !important; 
}

.popover-title {
      font-size: 12px;
  }

.popover-content {
      font-size: 12px;
  }
  
.popover-content {
    background-color: white;
    <!-- color: #FFFFFF; -->
    padding: 2px;
  }

<!-- .arrow { -->
<!--   border-right-color: red !important; -->
<!-- } -->

<!-- :target {  /* fix target location so caption appears */ -->
<!--     display: block;     -->
<!--     position: relative;      -->
<!--     top: 10px; -->
<!--     visibility: hidden; -->
<!-- } -->

</style>

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover({html: true, placement: top});
});
</script>
```

```{r setup, include = FALSE} 
## • (updated 2021/11/10 21:46) setup -------------------------------------
knitr::opts_chunk$set(echo = TRUE)
source("code/readfiles_nmb_102721.R")
```

```{r data, include = FALSE, eval = TRUE}
## • (updated 2021/11/16 09:02) create diag_ba.dat refids -----------------
## (updated 2022/01/07 08:54) verify correct refids -----------------------
tech_sc_refids <- study_char.dat %>% 
  filter(!is.na(tech_perf)) %>% 
  pull(refid) %>% 
  unique()

(tech_sa_refids <- study_arm.dat %>% 
  filter(!is.na(arm_tech_perf)) %>% 
# check discrepancy
  filter(!refid %in% tech_sc_refids) %>%
  pull(refid) %>%
  unique())

rm(tech_sa_refids, tech_sc_refids)

## (updated 2022/01/07 08:55) tech_perf refids verified -------------------
tech_refids <- study_arm.dat %>% 
  filter(!is.na(arm_tech_perf)) %>% 
  # TODO: remove line after fixed in distiller
  filter(refid != 3304) %>% 
  pull(refid) %>%
  unique()

# write refids to use in risk of bias
write_csv(tibble(tech_refids), "data/tech_refids.csv", na = "")

contin_tech.dat <- contin.dat %>% 
  filter(refid %in% tech_refids)

dichot_tech.dat <- dichot.dat %>% 
  filter(refid %in% tech_refids)

likert_tech.dat <- likert.dat %>% 
  filter(refid %in% tech_refids)
```

# **Included Studies** 

<br/>

<font size = 4> Table `r table_n`. Number of included studies according to age and design. </font>

```{r tablesIncluded, include = TRUE, echo = FALSE} 
## • (updated 2021/11/13 07:21) study_char_diag.dat -----------------------
# list of studies, age, surgical/non surgical, design 
study_char.dat %>% 
  filter(refid %in% tech_refids) %>% 
  group_by(age, design, .groups = "drop") %>%
  summarise(total = n()) %>%
  ungroup() %>%
  arrange(age, design) %>%
  group_by(age, .groups = "drop") %>%
  mutate(row = row_number()) %>%
  ungroup() %>%
  janitor::adorn_totals("row") %>%
  mutate(
    age = ifelse(row != 1, NA, age),
    design = case_when(
      design == "rct" ~ "RCT",
      design == "crossover" ~ "Crossover",
      design == "cluster" ~ "Cluster",
      design == "nrsi" ~ "Nonrandomized",
      design == "prospect_coh" ~ "Prospective Cohort",
      design == "retrospect_coh" ~ "Retrospective Cohort",
      design == "casecontrol" ~ "Case-Control",
      design == "other" ~ "Before-After",
      design == "fully_paired" ~ "Fully Paired"),
      age = ifelse(row_number() == n(), "Total", age)
  ) %>%
  select(age, design, total) %>%
  kbl(
    booktabs = T, align = c("llr"),
    col.names = c("Age", "Design", "N")
  ) %>%
  row_spec(c(0, 4), bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "8em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "3em") %>% 
  footnote(
    general = "RCT: randomized controlled trial.",
    # alphabet = c("Footnote a", "Footnote b", ...),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

## *List of Studies*

<br/>

<font size = 4> Table `r table_n`. Included studies, design, enrollment, centers, country, and surgery (see [References](#references) for citations). </font>

```{r studiesIncludedList, echo = FALSE, include = TRUE}
## • (updated 2021/11/16 09:06) included_studies.dat ----------------------
included_studies.dat <- study_char.dat %>%
  filter(refid %in% tech_refids) %>%
  mutate(
    design_l = as.character(design),
    design_l = factor(design_l,
      levels = c("rct", "fully_paired", "nrsi", "prospect_coh", "retrospect_coh"),
      labels = c("RCT", "Fully paired", "NRSI", "Prospective Cohort", "Retrospective Cohort")
    ),
    across(surg_various:surg_other, ~ str_replace(.x, "surg_", "")),
    across(surg_various:surg_other, ~ str_c(.x, ", ")),
    across(surg_various:surg_other, ~ firstup(.x)),
    across(surg_various:surg_other, ~ replace_na(.x, "")),
    surg_list = ifelse(grepl("abdom", surg_list), "Abdominal, ", ""),
    surgs = str_c(surg_various, surg_car, surg_cr, surg_gyn, surg_gi, surg_gen, surg_headneck, surg_hep, surg_neuro, surg_opth, surg_oralmax, surg_ortho, surg_otolar, surg_plastic, surg_thor, surg_urol, surg_list),
    surgs = str_replace(surgs, "Otolar", "ENT"),
    surgs = str_replace(surgs, "Headneck", "ENT"),
    surgs = str_sub(surgs, 1, nchar(surgs) - 2),
    country = ifelse(grepl("USA", country), "USA", country),
    country = ifelse(grepl("UK", country), "UK", country),
    country = ifelse(!is.na(non_vh_hdi), str_c(country, "^a^"), country),
    # design = case_when(
    #   design == "rct" ~ "RCT",
    #   design == "fully_paired" ~ "Fully paired"
    # ),
    # design = ifelse(study == "Claudius 2009", "Fully paired (random subset)", design)
  ) %>%
  select(refid, study_l, year, age, design, design_l, n_analyze, country, centers, non_vh_hdi, surgs) %>%
  arrange(age, design_l, year) 

## • (updated 2021/11/16 09:06) kable -------------------------------------
# included_studies.dat %>%
#   arrange(age, design_l, study_l) %>%
#   select(study_l, refid, age, design_l) %>%
#   group_by(age, design_l) %>%
#   tally() %>%
#   ungroup() %>%
#   mutate(end = cumsum(n),
#          start = end - n + 1) %>%
#   select(age, design_l, start, end)

included_studies.dat %>% 
  select(refid, study_l, n_analyze, centers, country, surgs) %>% 
  kbl(
    booktabs = T, align = c("llccll"), escape = TRUE, # format = "latex",
    col.names = c("            ID", "Study", "Analyzed (N)", "Centers", "Country^a^", "Surgery")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "6em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "6em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "10em") %>%
  column_spec(6, width = "12em") %>%
  pack_top(., "Adult", 1, 22) %>%
  pack_sub(., "RCT", 1, 4) %>% 
  pack_sub(., "Fully Paired", 5, 21) %>% 
  pack_sub(., "Prospective Cohort", 22, 22) %>% 
  footnote(
    general = "RCT: randomized controlled trial.",
    alphabet = c(
      "Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

# **Outcomes**

<br/>

## *Comparators*

```{r compareOutcomes}
## data ----------------------------------------------- (2022-03-18 07:13) @----
compare_out <- readxl::read_xlsx("data/TechPerf_DraftTables_010322.xlsx", sheet = "Comparators & Outcomes", range = "A2:N41") %>% 
  clean_names() %>% 
  remove_empty(which = "rows") %>% 
  mutate(comparators = ifelse(grepl("^[A-Z]", refid), refid, NA),
         refid = as.numeric(refid)) %>% 
  relocate(comparators, .after = refid) %>%
  fill(comparators) %>% 
  filter(!is.na(refid)) %>% 
  View()

```

<br/><br/>

# **Study/Participant Detail** 

<br/>

### *Study Characteristics* 

<br>

<font size = 4> Table `r table_n`. Study characteristics. </font>

```{r createStudyCharTable, include = FALSE}
## (updated 2021/01/12 09:30) createStudyCharTable ------------------------
study_char_table <- study_char.dat %>%
  filter(refid %in% tech_refids) %>% 
  mutate(
    dates = str_c(date_start, "-", date_end),
    country = countrycode::countryname(country, destination = "iso3c"),
    low_r = noquote(if_else(non_vh_hdi == "yes", "\U2022", "", "")),
    n = n_enrolled,
    n_anal = n_analyze,
    pilot = noquote(if_else(pilot == "yes", "\U2022", "", "")),
    setting = case_when(
      !is.na(hospital) ~ "Hosp",
      !is.na(ambulatory) ~ "Amb",
      !is.na(other_setting) ~ "Other"
    ),
    gen = noquote(if_else(!is.na(general), "\U2022", "", "")),
    reg = noquote(if_else(!is.na(regional), "\U2022", "", "")),
    sed = noquote(if_else(!is.na(sedation), "\U2022", "", "")),
    registered = noquote(if_else(registered == "yes", "\U2022", "", "")),
    across(surg_various:surg_other, ~ str_replace(.x, "surg_", "")),
    across(surg_various:surg_other, ~ str_c(.x, ", ")),
    across(surg_various:surg_other, ~ firstup(.x)),
    across(surg_various:surg_other, ~ replace_na(.x, "")),
    surg_list = ifelse(grepl("abdom", surg_list), "Abdom, ", ""),
    surgs = str_c(surg_various, surg_car, surg_cr, surg_gyn, surg_gi, surg_gen, surg_headneck, surg_hep, surg_neuro, surg_opth, surg_oralmax, surg_ortho, surg_otolar, surg_plastic, surg_thor, surg_urol, surg_list),
    surgs = str_replace(surgs, "Otolar", "ENT"),
    surgs = str_replace(surgs, "Car", "Card"),
    surgs = str_replace(surgs, "Cr", "GI"),
    surgs = str_replace(surgs, "Gi", "GI"),
    surgs = str_replace(surgs, "Headneck", "ENT"),
    surgs = str_sub(surgs, 1, nchar(surgs) - 2),
    country = ifelse(grepl("USA", country), "USA", country),
    country = ifelse(grepl("UK", country), "UK", country),
    country = ifelse(!is.na(non_vh_hdi), str_c(country, "^a^"), country)
  ) %>%
  arrange(age, design, year, study) %>%
  select(refid, age, design, study_l, dates, country, n, pilot, setting, gen, reg, -sed,  surgs, registered)

```

```{r studyCharKableAdult, echo = FALSE}
## (updated 2021/01/12 19:27) ---------------------------------------------
# temp <- study_char_table %>%
#   arrange(age, design, study) %>% 
#   filter(age == "Adult") %>% 
#   select(study, refid, age, design) %>% 
#   group_by(age, design) %>% 
#   tally() %>% 
#   ungroup() %>% 
#   mutate(end = cumsum(n),
#          start = end - n + 1) %>% 
#   select(age, design, start, end)

study_char_table %>%
  filter(age == "Adult") %>% 
  select(!c(refid, age, design)) %>% 
  kbl(booktabs = T, align = c("llllcccclc"), 
      # format = "latex",
      col.names = c("Study", "Dates", "Country", " N ", "Pilot", 
                    "Setting", "Gen", "Reg", "Type of Surgery", "Registered")) %>%
  add_header_above(c(" " = 6, "Anesthesia" = 2, " " = 2), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>% 
  column_spec(2, width = "8em") %>% 
  column_spec(3, width = "5em") %>% 
  column_spec(4, width = "4em") %>% 
  column_spec(5, width = "4em") %>% 
  column_spec(6, width = "5em") %>% 
  column_spec(7, width = "3em") %>% 
  column_spec(8, width = "3em") %>% 
  column_spec(9, width = "15em") %>% 
  column_spec(10, width = "5em") %>% 
  pack_top(., "Adult", 1, 22) %>%
  pack_sub(., "RCT", 1, 4) %>% 
  pack_sub(., "Fully Paired", 5, 21) %>% 
  pack_sub(., "Prospective Cohort", 22, 22) %>% 
  footnote(general_title = "",
    general = c("Gen: general; Reg: regional; Sed: sedation; Hosp: hospital; Amb: ambulatory; GI: gastrointestinal; Ortho: orthopedic; Abdom: abdominal; ENT: otolaryngology (ear, nose, and throat); Gyn: gynecologic; Urol: urologic; Neuro: neurological; Hep: hepatic; Thor: thoracic; Oralmax: oral maxillofacial"),
    alphabet = c("Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."),
    footnote_as_chunk = FALSE) # %>% 

table_n <- tab_inc()
```
<br/>

### *Patient Characteristics*

###   <u>Adult Studies</u>

<br>

<font size = 4> Table `r table_n`. Patient characteristics in studies including only adults. </font>

```{r ptCharTableData, include = FALSE}
## ptCharTableData (updated 2022/01/15 10:08) ----------------------------
pt_char_table <- study_arm.dat %>%
  filter(refid %in% tech_refids) %>%
  group_by(refid) %>%
  summarize(
    N = sum(arm_n),
    wgt = arm_n / N,
    asa_1_all = round(sum(asa_1 * wgt, na.rm = FALSE)),
    asa_2_all = round(sum(asa_2 * wgt, na.rm = FALSE)),
    asa_3_all = round(sum(asa_3 * wgt, na.rm = FALSE)),
    asa_12_all = round(sum(asa_12 * wgt, na.rm = FALSE)),
    asa_123_all = round(sum(asa_123 * wgt, na.rm = FALSE)),
    asa_23_all = round(sum(asa_23 * wgt, na.rm = FALSE)),
    asa_34_all = round(sum(asa_34 * wgt, na.rm = FALSE)),
    age_mn_all = round(sum(age_mean * wgt, na.rm = FALSE)),
    age_md_all = round(sum(age_med * wgt, na.rm = FALSE)),
    sex_all = round(sum(female * wgt, na.rm = FALSE)),
    white_all = round(sum(white * wgt, na.rm = FALSE)),
    black_all = round(sum(black * wgt, na.rm = FALSE)),
    asian_all = round(sum(asian * wgt, na.rm = FALSE)),
    bmi_mn_all = round(sum(bmi_mean * wgt, na.rm = FALSE)),
    bmi_md_all = round(sum(bmi_med * wgt, na.rm = FALSE)),
    cardiac_all = round(sum(cardiac * wgt, na.rm = FALSE)),
    cancer_all = round(sum(cancer * wgt, na.rm = FALSE)),
    renal_all = round(sum(renal * wgt, na.rm = FALSE)),
    gi_all = round(sum(gi * wgt, na.rm = FALSE)),
    pulm_all = round(sum(pulm * wgt, na.rm = FALSE)),
    hepatic = round(sum(hepatic * wgt, na.rm = FALSE)),
    dm_all = round(sum(dm * wgt, na.rm = FALSE)),
    neuro_all = round(sum(neuro * wgt, na.rm = FALSE))
  ) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  # remove_empty(which = "cols") %>%
  # categorize asa class
  mutate(
    asa_1 = ifelse(if_any(c(asa_1_all, asa_12_all, asa_123_all), ~ !is.na(.)), "\U00D7", NA),
    asa_2 = ifelse(if_any(c(asa_12_all, asa_2_all, asa_123_all, asa_23_all), ~ !is.na(.)), "\U00D7", NA),
    asa_3 = ifelse(if_any(c(asa_123_all, asa_3_all, asa_23_all, asa_34_all), ~ !is.na(.)), "\U00D7", NA),
    asa_4 = ifelse(if_any(c(asa_34_all), ~ !is.na(.)), "\U00D7", NA)
  ) %>%
  relocate(c(asa_1, asa_2, asa_3, asa_4), .after = asa_34_all) %>%
  mutate(across(c(cardiac_all:neuro_all), ~ bar_wn(.x, .x, color_1, 100)),
    across(c(white_all:asian_all), ~ bar_wn(.x, .x, color_2, 100)),
    sex_all = bar_wn(sex_all, sex_all, color_3, 100),
    age_sum = ifelse(is.na(age_mn_all) & !is.na(age_md_all), paste0("<u>", age_md_all, "</u>"), age_mn_all),
    bmi = ifelse(is.na(bmi_mn_all) & !is.na(bmi_md_all), paste0("<u>", bmi_md_all, "</u>"), bmi_mn_all)
  ) %>%
  relocate(bmi, .before = bmi_mn_all) %>%
  relocate(age_sum, .before = age_mn_all) %>%
  select(-c(asa_1_all:asa_34_all, wgt, bmi_mn_all, bmi_md_all, age_mn_all, age_md_all))

pt_char_table <- left_join(pt_char_table, study_char.dat[, c("refid", "age", "design", "study_l", "year")], by = "refid") %>% 
  relocate(c(age, design, study_l, year), .after = "refid") %>% 
  arrange(design, year)

```

```{r ptCharTableAdult}
## ptCharTableData (updated 2022/01/15 10:08)  ----------------------------
# pt_char_table %>%
#   arrange(age, design, study) %>%
#   filter(age == "Adult") %>%
#   select(study, refid, age, design) %>%
#   group_by(age, design) %>%
#   tally() %>%
#   ungroup() %>%
#   mutate(
#     end = cumsum(n),
#     start = end - n + 1
#   ) %>%
#   select(age, design, start, end)

pt_char_table %>% 
  filter(age == "Adult") %>% 
  select(-c(refid, year, age, design)) %>% 
  select(study_l:bmi, cardiac_all, renal_all, pulm_all, hepatic, dm_all, neuro_all) %>% 
    kbl(booktabs = T, align = c("llcccccllllcllllll"), escape = FALSE,
      col.names = c("Study", " N ", "1", "2", "3", "4", "M <u>Med</u>", "(%)", "W", "B", "A", "M <u>Med</u>", "Card", "Renal", "Pulm", "Hep", "DM", "Neur")) %>% 
  add_header_above(c(" " = 2, "ASA Class" = 4, "Age" = 1, "Female", "Race" = 3, "BMI" = 1, "Comorbidities (%)^a^" = 6), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>% 
  column_spec(2, width = "3em") %>% 
  column_spec(3:6, width = "2em", popover = "ASA class (1 to 4)") %>% 
  column_spec(7, width = "4em", popover = "Age") %>% 
  column_spec(8, width = "4em", popover = "Female %") %>% 
  column_spec(9, width = "3em", popover = "White %") %>%
  column_spec(10, width = "3em", popover = "Black %") %>%
  column_spec(11, width = "3em", popover = "Asian %") %>%
  column_spec(12, width = "4em", popover = "BMI") %>% 
  column_spec(13, width = "3em", popover = "Cardiac %") %>%
  column_spec(14, width = "3em", popover = "Renal %") %>% 
  column_spec(15, width = "3em", popover = "Pulmonary %") %>% 
  column_spec(16, width = "3em", popover = "Hepatic %") %>% 
  column_spec(17, width = "3em", popover = "Diabetes %") %>% 
  column_spec(18, width = "3em", popover = "Nuerological %") %>% 
  pack_top(., "Adult", 1, 22) %>%
  pack_sub(., "RCT", 1, 4) %>% 
  pack_sub(., "Fully Paired", 5, 21) %>% 
  pack_sub(., "Prospective Cohort", 22, 22) %>% 
  footnote(general_title = "",
    general = c("M: mean; Med: median; Card: cardiac; Pulm: pulmonary; Hep: hepatic; DM: diabetes mellitus; Neuro: neurological: RCT: randomized controlled trial."),
    alphabet = c("Empty cells indicate no information in publication."),
    footnote_as_chunk = FALSE)  

table_n <- tab_inc()
```

<br/>

# **Funding and Conflict of Interest**

<br/>

###   <u>Adult Studies</u>

<br>

<font size = 4> Table `r table_n`. Funding^a^ and reported conflict of interest in studies including only adults. </font>

```{r createFundingTable, include = FALSE}
## (updated 2021/01/12 09:28) createFundingTable --------------------------
study_fund_table <- study_char.dat %>%
  filter(refid %in% tech_refids) %>% 
  mutate(
    sponsor_desc = str_replace(sponsor_desc, "MSD", "Merck Sharp & Dohme Corp"),
    sponsor_desc = str_replace(sponsor_desc, "Merck & Co", "MSD"),
    sponsor_desc = str_replace(sponsor_desc, "Merck Sharp & Dohme Corp", "MSD"),
    sponsor_desc = str_replace(sponsor_desc, "Merck", "MSD"),
    sponsor_desc = firstup(sponsor_desc),
    # sponsor_desc = str_replace(sponsor_desc, "MSD", "Merck Sharp & Dohme"),
    auth_coi_desc = str_replace_all(auth_coi_desc, "MSD", "Merck Sharp & Dohme Corp"),
    auth_coi_desc = str_replace_all(auth_coi_desc, "Merck & Co", "Merck Sharp & Dohme Corp"),
    auth_coi_desc = str_replace_all(auth_coi_desc, "Merck Sharp & Dohme Corp", "MSD"),
    auth_coi_desc = str_replace_all(auth_coi_desc, "Merck", "MSD"),
    # auth_coi_desc = str_replace_all(auth_coi_desc, "MSD", "Merck Sharp & Dohme"),
    # sponsor_desc = str_to_title(sponsor_desc),
    auth_not_report = noquote(if_else(author_coi == "not_auth_rep", "\U00D7", "", "")),
    # auth_not_report = if_else(author_coi == "not_auth_rep", "&times", "", ""),
    auth_no_coi = noquote(if_else(author_coi == "none_auth_coi", "\U00D7", "", "")),
    auth_coi = noquote(if_else(author_coi == "author_coi", '<span style="color:red">\U00D7</span>', "", "")),
    registered = noquote(if_else(registered == "yes", "\U00D7", "", "")),
    public = noquote(if_else(funding == "public", "\U00D7", "", "")),
    pub_indus = noquote(if_else(funding == "pub_indus", '<span style="color:red">\U00D7</span>', "", "")),
    industry = noquote(if_else(funding == "industry", '<span style="color:red">\U00D7</span>', "", "")),
    none = noquote(if_else(funding == "none", "\U00D7", "", "")),
    not_reported = noquote(if_else(funding == "NR", "\U00D7", "", ""))) %>%
  arrange(age, design, year, study) %>%
  select(refid, study_l, age, design, public, pub_indus, industry, none, not_reported, sponsor_desc, auth_no_coi, auth_coi, auth_not_report, auth_coi_desc)

```

```{r fundingKable, echo = FALSE}
## (updated 2021/01/12 09:28) fundingKable --------------------------------
study_fund_table %>% 
  filter(age == "Adult") %>% 
  select(!c(refid, age, design)) %>% 
  kbl(booktabs = T, align = c("lccccclcccl"),
      col.names = c("Study", "Pub", '<span style="color:red">Pub/Ind</span>', '<span style="color:red">Ind</span>',  "None", "NR^a^", "Description", "No", '<span style="color:red">Yes</span>', "NR^a^", "Description"),
      escape = FALSE) %>%
  add_header_above(c(" " = 1, "Funding Source(s)" = 6, "Author Conflict of Interest" = 4), line = TRUE, bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "12em") %>% 
  column_spec(2:6, width = "4em") %>% 
  column_spec(7, width = "20em") %>% 
  column_spec(8:10, width = "4em") %>% 
  column_spec(11, width = "20em") %>% 
  pack_top(., "Adult", 1, 22) %>%
  pack_sub(., "RCT", 1, 4) %>% 
  pack_sub(., "Fully Paired", 5, 21) %>% 
  pack_sub(., "Prospective Cohort", 22, 22) %>% 
  footnote(general = "Pub: public, Ind: industry; NR: not reported; MSD: Merck, Sharp, and Dohme.",
          alphabet = c("Not reported meaning no mention in publication of funding source or author conflicts of interest."))
          # general_title = " ",
          # alphabet_title = " ",
          # footnote_as_chunk = T)

table_n <- tab_inc()

# merck studies
# study_fund_table %>% 
#   # filter(age == "Adult", design == "rct") %>% 
#   filter(age == "Adult") %>% 
#   mutate(
#     msd_fund = grepl("MSD|Merck", sponsor_desc)
#   ) %>% 
#   tabyl(msd_fund)
```

<br><br/>

# **Risk of Bias** 

<br/>

### *Diagnostic Studies*

<br>

<font size = 4> Figure `r figure_n`. Summary risk of bias appraisal (QUADAS-2) for included studies. </font>

<img src="assets/kq1_quadas_summary.svg" style="width:700px;" align="left"/>

<br clear="all" />

```{r}
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Individual study risk of bias appraisal (QUADAS-2) for included diagnostic studies. </font>

<img src="assets/kq1_quadas_traffic.svg" style="width:565px;" align="left"/>
<!-- <img src="assets/kq1_quadas_traffic.svg" style="width: 75%; height: 1000px;" align="left"/> -->

```{r}
figure_n <- fig_inc()
```
<br clear="all" />

<br/>

### *RCTs Clinical Outcomes*

<br>

<font size = 4> Figure `r figure_n`. Summary risk of bias appraisal for included RCTs reporting clinical outcomes. </font>

<img src="assets/kq1_rob_clin_out.svg" style="width:750px;" align="left"/>

<br clear="all" />

```{r}
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Individual study risk of bias appraisal for included RCTs. </font>

<img src="assets/kq1_rob_clin_out_traffic.svg" style="width:650px;" align="left"/>

```{r}
figure_n <- fig_inc()
```
<br clear="all" />


<hr style="height:2px;border-width:0;color:gray;background-color:gray">

<br>

# **References**
<a id="references"></a>

<br/>




