---
title: "Reversal"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
output:
  html_document:
    font: Source Sans Pro
    theme: cosmo
    anchor_sections: TRUE
    toc_float: 
      collapsed: FALSE
      smooth_scroll: TRUE
    toc_depth: 3
    linkcolor: blue
  latex_engine: xelatex
  pdf_document:
    toc: yes
    toc_depth: '3'
bibliography: "bib/kq4.bib"
csl: jama.csl
link-citations: yes
workflowr:
  suppress_report: false
nocite: '@*'
---

```{=html}
<style type="text/css">
  body{
  font-size: 9.5pt;
  font-family: Source Sans Pro;
}

.caption {
  font-size: 15px;
}

.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  color: #090909;
  background-color: #0909093d;
}

.lightable-classic.lightable-hover tbody tr:hover {
    background-color: #c5d4e4;
}
.btn-xs, .btn-group-xs>.btn { 
display: none; 
}

.btn-default {
display: none !important; 
}

.popover-title {
      font-size: 12px;
  }

.popover-content {
      font-size: 12px;
  }
  
.popover-content {
    background-color: white;
    <!-- color: #FFFFFF; -->
    padding: 2px;
  }

<!-- .arrow { -->
<!--   border-right-color: red !important; -->
<!-- } -->

<!-- :target {  /* fix target location so caption appears */ -->
<!--     display: block;     -->
<!--     position: relative;      -->
<!--     top: 10px; -->
<!--     visibility: hidden; -->
<!-- } -->

</style>

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover({html: true, placement: top});
});
</script>
```

```{r setup, include = FALSE}
## setup ---------------------------------------------- (2022-02-14 16:17) @----
knitr::opts_chunk$set(echo = TRUE)
source("code/readfiles_nmb_102721.R")
```

```{r data}
## data/refids ---------------------------------------- (2022-02-15 10:28) @
## refids --------------------------------------------- (2022-02-21 10:31) @----
# rev refids volatile study_arm.dat 
rev_refids <- study_char.dat %>% 
  filter(rev_agt == "rev_agt") %>% 
  pull(refid) %>% 
  unique()

neo_dosing_refids <- study_arm.dat %>% 
  filter(subgroup == "neo_dosing") %>% 
  pull(refid) %>% 
  unique()

sug_dosing_refids <- study_arm.dat %>% 
  filter(subgroup == "sug_dosing") %>% 
  pull(refid) %>% 
  unique()

# note that subgroup assigned by arm
subgroup_refids <- study_arm.dat %>% 
  filter(subgroup != "none") %>% 
  pull(refid) %>% 
  unique()

# from latest distiller 2022/02/21 08:13 n=26
rnmb_dist_refids <- dichot.dat %>%
  filter(refid %in% rev_refids) %>%
  filter(!is.na(rnmb), !refid %in% subgroup_refids) %>%
  # remove single arm studies; 2022/02/21 08:52 will be Yip 2304, Alenezu 3574
  group_by(refid) %>%
  filter(n() >= 2) %>%
  ungroup() %>%
  select(refid) %>%
  distinct() %>%
  pull()

## from spreadsheet ----------------------------------- (2022-02-22 14:32) @----
# rcts only from spreadsheet 2022/02/21 08:04 n=21 (checked same in excel sheet) 
rnmb_ma.dat <- suppressMessages(read_csv("data/rnmb_read_011322.csv")) %>% 
  clean_names() %>% 
  filter(!is.na(arm)) %>% 
  fill(refid, study) %>% 
  remove_empty(which = "cols") %>% 
  mutate(
    study_orig = study,
    study = str_extract(study, "\\w*.{0,1}\\w* \\d{4}"),
    mg_kg = ifelse(is.na(mg_kg) & !is.na(mg), paste0("<u>", mg, "</u>"), mg_kg),
    refid = suppressWarnings(as.numeric(refid))
  ) %>% 
  select(-mg) # milligram can delete

## data char, arm, dichot ----------------------------- (2022-02-21 10:32) @----
study_char_rev.dat <- study_char.dat %>%
  filter(refid %in% rev_refids) 

study_arm_rev.dat <- study_arm.dat %>%
  filter(refid %in% rev_refids) %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    ),
    arm = case_when(
      revagent %in% c("neo") ~ "Neo",
      revagent %in% c("sug") ~ "Sug",
      str_detect(study_arm_k, "pont") ~ "Spont",
      revagent %in% c("other_agent") ~ revother,
      TRUE ~ "Other"
    ),
    arm = ifelse(str_detect(arm, "lacebo|saline"), "Plac", arm),
    arm = ifelse(str_detect(arm, "yridostigmine"), "Pyrid", arm),
    arm = factor(arm, levels = c("Sug", "Neo", "Plac", "Spont", "Pyrid", "Other"), ordered = TRUE),
    volatile = if_any(c(an_isoflurane, an_sevoflurane, an_desf, an_hal), ~ !is.na(.))
  ) %>%
  select(refid, arm_id, study, year, design, arm_n, arm, age, study_arm_k, subgroup, depth, starts_with("depth_rev_"), anesth:anes_agent_spec, neo_dose, neo_max_dose, neo_dose_unit, sug_dose, sug_dose_max, nmbagent, gen_type, revtim, revtim_comment, mon_cat, mon_cat_f)

dichot_rev.dat <- dichot.dat %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    )
  )

# study_arm_rev.dat %>% tabyl(depth)

## comparators ---------------------------------------- (2022-02-21 10:32) @----
comparators <- study_arm_rev.dat %>% 
  # filter(design == "rct") %>% 
  arrange(year) %>% 
  select(refid, study, design, subgroup, arm_id, arm, age) %>% 
  pivot_wider(id_cols = c(refid, study, design, subgroup), names_from = arm, values_from = arm_id, values_fn = list) %>% 
  select(refid:design, subgroup, Sug, Neo, Plac, Spont, Pyrid, Other) %>% 
  mutate(across(Sug:Other, ~ as.numeric(. != "NULL"))) %>% 
  mutate(across(Sug:Other, ~ as.character(.))) %>% 
  mutate(across(Sug:Other, ~ ifelse(. == "1", cur_column(), ""))) %>% 
  mutate(compare = str_c(Sug, Neo, Plac, Spont, Pyrid, sep = ":"),
         compare = str_replace_all(compare, ":{2,3}", ":"),
         compare = str_replace(compare, "^:", ""),
         compare = str_replace_all(compare, ":{1,3}$", ""))

# subgroups with comparators
comp_subgroup <- comparators %>% 
  filter(subgroup != "none", str_detect(compare, ":")) 

rct_nosub_comp <- comparators %>% 
  filter(design == "rct", refid %notin% subgroup_refids) 

## comparators by arm --------------------------------- (2022-02-21 13:33) @----
comp_rct_arm <- study_arm_rev.dat %>% 
  mutate(study = case_when(
    study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
    study == "Wu 2014" & arm_n >= 50 ~"Wu 2014 (Chinese)",
    TRUE ~ study)) %>% 
  filter(design == "rct", refid %notin% subgroup_refids) %>% 
  arrange(year) %>% 
  select(refid, study, design, subgroup, arm_id, arm, arm_n, age) %>% 
  mutate(event_placeholder = 1)

## netmeta code --------------------------------------- (2022-02-21 14:08) @----
# library(netmeta)  
# pairs.dat <- pairwise(
#   treat = arm,
#   event = event_placeholder, 
#   n = arm_n,
#   studlab = study,
#   data = comp_rct_arm,
#   sm = "RR"
# )
# 
# # trts <- c("Clinical", "Qualitative", "Quantitative")
# 
# nmm_netmeta_nma <- netmeta(
#   pairs.dat,
#   random = TRUE,
#   # backtransf = TRUE,
#   # prediction = TRUE,
#   # seq = trts,
#   sm = "RR",
#   reference.group = "Spont"
# )
```

```{r checks, eval = FALSE}
## checkRefids TEMP ----------------------------------- (2022-02-21 09:17) @----
rnmb_ma_refids <- rnmb_ma.dat %>% 
  select(refid) %>% 
  distinct() %>% 
  pull()
  
# check in distiller pull
# refids 2834, 3491, 4997 appear to be missing
# 2304 and 3574 are single arm
# rnmb_ma_refids %in% rev_refids
# rnmb_ma_refids[!rnmb_ma_refids %in% rnmb_dist_refids]
# rnmb_dist_refids[!rnmb_dist_refids %in% rnmb_ma_refids]
## rnmb_dist_refids ----------------------------------- (2022-02-21 08:59) @----

rnmb_ma.dat %>% 
  select(refid, study, arm, deep:ns_depth)

temp_depth_rev <- study_arm_rev.dat %>% 
  filter(refid %in% rnmb_dist_refids) %>% 
  select(refid, study, arm, depth_rev_f) %>% 
  mutate(check = 1) %>% 
  pivot_wider(id_cols = c(refid, study, arm), names_from = depth_rev_f, values_from = check)
```

# **Included Studies**

<font size = 4> Table `r table_n`. Number of included studies according to age and design. </font>

```{r tablesIncluded, include = TRUE, echo = FALSE}
## tablesIncluded ------------------------------------- (2022/02/21 14:11) @----
# list of studies, age, surgical/non surgical, design 
study_char.dat %>% 
  filter(refid %in% rev_refids) %>% 
  group_by(age, design, .drop = TRUE) %>%
  summarise(total = n()) %>%
  ungroup() %>%
  arrange(age, design) %>%
  group_by(age, .drop = TRUE) %>%
  mutate(row = row_number()) %>%
  ungroup() %>%
  janitor::adorn_totals("row") %>%
  mutate(
    age = ifelse(row != 1, NA, age),
    design = case_when(
      design == "rct" ~ "RCT",
      design == "quasiexp" ~ "Before-After/Time Series",
      design == "cluster" ~ "Cluster Randomized",
      design == "nrsi" ~ "Nonrandomized Trial",
      design == "prospect_coh" ~ "Prospective Cohort",
      design == "retrospect_coh" ~ "Retrospective Cohort",
      design == "casecontrol" ~ "Case-Control",
      design == "other" ~ "Before-After",
      design == "fully_paired" ~ "Fully Paired"),
      age = ifelse(row_number() == n(), "Total", age)
  ) %>%
  select(age, design, total) %>%
  kbl(
    booktabs = T, align = c("llr"),
    col.names = c("Age", "Design", "N")
  ) %>%
  row_spec(c(0, 11), bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "8em") %>%
  column_spec(2, width = "14em") %>%
  column_spec(3, width = "3em") %>% 
  footnote(
    general = "RCT: randomized controlled trial.",
    # alphabet = c("Footnote a", "Footnote b", ...),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

<font size = 4>  Figure `r figure_n`. Comparators in randomized controlled trials in adult and pediatric populations. </font>

``` {r rctComparatorsPlots, include = TRUE, out.width="80%"}
## network plot --------------------------------------- (2022-02-21 14:07) @----
comp_rct_arm_adult<- comp_rct_arm %>% 
  filter(age == "Adult")

comp_rct_arm_peds<- comp_rct_arm %>% 
  filter(age == "Pediatric")

nmm.data <- BUGSnet::data.prep(
  arm.data = comp_rct_arm_adult,
  varname.t = "arm",
  varname.s = "study"
)

BUGSnet::net.plot(nmm.data,
  node.scale = 0.8,
  edge.scale = .5,
  # label.offset2 = 3,
  # label.offset1 = 8,
  study.counts = TRUE,
  # node.lab.cex = 1,
  # edge.lab.cex = 1.2
)

title("Adult")

nmm.data <- BUGSnet::data.prep(
  arm.data = comp_rct_arm_peds,
  varname.t = "arm",
  varname.s = "study"
)

BUGSnet::net.plot(nmm.data,
  node.scale = 0.8,
  edge.scale = .5,
  # label.offset2 = 3,
  # label.offset1 = 8,
  study.counts = TRUE,
  # node.lab.cex = 1,
  # edge.lab.cex = 1.2
)

title("Pediatric")

figure_n <- fig_inc()

```

## *Design, centers, country, surgery*

<br/>

<font size = 4> Table `r table_n`. Study design, enrollment, centers, country, and surgery (see [References](#references) for citations). </font>

```{r studiesIncludedList, echo = FALSE, include = TRUE}
## studiesIncluded ------------------------------------ (2022-02-15 10:38) @----
temp <- study_char_rev.dat %>%
  filter(rev_agt == "rev_agt") %>%
  arrange(age, design, study) %>%
  select(study, refid, age, design) %>%
  group_by(age, design) %>%
  tally() %>%
  ungroup() %>%
  mutate(
    end = cumsum(n),
    start = end - n + 1
  ) %>%
  select(age, design, start, end)

included_studies.dat <- study_char_rev.dat %>%
  mutate(
    across(surg_various:surg_other, ~ str_replace(.x, "surg_", "")),
    across(surg_various:surg_other, ~ str_c(.x, ", ")),
    across(surg_various:surg_other, ~ firstup(.x)),
    across(surg_various:surg_other, ~ replace_na(.x, "")),
    surg_list = ifelse(grepl("abdom", surg_list), "Abdominal, ", ""),
    surgs = str_c(surg_various, surg_car, surg_cr, surg_gyn, surg_gi, surg_gen, surg_headneck, surg_hep, surg_neuro, surg_opth, surg_oralmax, surg_ortho, surg_otolar, surg_plastic, surg_thor, surg_urol, surg_list),
    surgs = str_replace(surgs, "Otolar", "ENT"),
    surgs = str_replace(surgs, "Headneck", "ENT"),
    surgs = str_sub(surgs, 1, nchar(surgs) - 2),
    country = ifelse(grepl("USA", country), "USA", country),
    country = ifelse(grepl("UK", country), "UK", country),
    country = ifelse(!is.na(non_vh_hdi), str_c(country, "^a^"), country)
  ) %>%
  select(refid, study_l, year, age, design, n_analyze, country, centers, non_vh_hdi, surgs) %>%
  arrange(age, design, year)

## kable ---------------------------------------------- (2022-02-15 10:43) @----
included_studies.dat %>% 
  select(refid, study_l, n_analyze, centers, country, surgs) %>% 
  kbl(
    booktabs = T, align = c("llccll"), escape = TRUE, # format = "latex",
    col.names = c("            ID", "Study", "Analyzed (N)", "Centers", "Country^a^", "Surgery")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "6em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "6em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "10em") %>%
  column_spec(6, width = "25em") %>%
  pack_top(., "Adult", 1, 136) %>%
  pack_sub(., "RCT", 1, 105) %>% 
  pack_sub(., "Before-After/Time Series", 106, 106) %>% 
  pack_sub(., "Nonrandomized Trial", 107, 114) %>% 
  pack_sub(., "Prospective Cohort", 115, 126) %>% 
  pack_sub(., "Retrospective Cohort", 126, 136) %>% 
  pack_top(., "All ages", 137, 141) %>% 
  pack_sub(., "RCT", 137, 140) %>% 
  pack_sub(., "Retrospective Cohort", 141, 141) %>% 
  pack_top(., "Pediatric", 142, 158) %>%
  pack_sub(., "RCT", 142, 153) %>% 
  pack_sub(., "Prospective Cohort", 154, 157) %>% 
  pack_sub(., "Case-control", 158, 158) %>% 
  footnote(
    general = "RCT: randomized controlled trial.",
    alphabet = c(
      "Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
rm(temp)
```

# **Outcomes**

<br/>

## *Residual Neuromuscular Block (TOFR/Clinical)*

```{r rnmbData, echo = FALSE}
## rnmbData_ma_sheet ---------------------------------- (2022-02-15 11:25) @----
rnmb_depth <- rnmb_ma.dat %>%
  select(refid, study, study_orig, arm, n, deep:ns_depth) %>%
  mutate(across(deep:ns_depth, ~ ifelse(. == "x", cur_column(), ""))) %>%
  unite(., col = "depth_rev_ma_f", deep:ns_depth, sep = ":", remove = FALSE, na.rm = TRUE) %>%
  mutate(
    depth_rev_ma_f = factor(depth_rev_ma_f, levels = c("deep", "deep:mod", "deep:mod:shallow", "mod", "mod:shallow", "mod:shallow:min", "min", "shallow", "clincrit", "endsurg", "oth", "ns")),
    study = study_orig
  ) %>%
  rename(arm_n = n) %>%
  select(c(-study_orig))

## rnmb.dat ------------------------------------------- (2022-02-21 09:00) @----
# add subgroup studies with relevant main effects
# Martinez-Ubieto 2016; need to combine spontaneous arms
rnmb_dist_refids <- sort(unique(c(rnmb_dist_refids, 2896)))

study_arm_rnmb.dat <- study_arm_rev.dat %>% 
  filter(refid %in% rnmb_dist_refids) %>% 
  select(refid, arm_id, study, subgroup, year, arm, study_arm_k, starts_with("depth_rev"), mon_cat, mon_cat_f, neo_dose, neo_max_dose, neo_dose_unit, sug_dose, sug_dose_max, arm_n, nmbagent, gen_type, revtim, revtim_comment)

dichot_rnmb.dat <- dichot_rev.dat %>% 
  filter(refid %in% rnmb_dist_refids) %>% 
  select(refid, study, arm_id, rnmb1_dev, rnmb1_clinical, rnmb1_where, rnmb2_dev, rnmb2_clinical, rnmb2_where, rnmb, rnmb1_n, rnmb1_per, rnmb1_7, rnmb1_8, rnmb1_9, rnmb1_1, rnmb1_clinical, rnmb2_n, rnmb2_per, rnmb2_7, rnmb2_8, rnmb2_9, rnmb2_1, rnmb2_clinical)

rnmb.dat <- left_join(study_arm_rnmb.dat, dichot_rnmb.dat, by = c("refid", "study", "arm_id"))

study_char_rnmb.dat <- study_char_rev.dat %>%
  filter(refid %in% rnmb_dist_refids) %>% 
  select(refid, study_l, age, design)

rnmb.dat <- left_join(rnmb.dat, study_char_rnmb.dat, by = c("refid")) %>%
  relocate(c(study_l, age, design, year), .before = study) %>% 
  filter(refid %in% rnmb_dist_refids) 

rnmb.dat <- left_join(rnmb.dat, rnmb_depth, by = c("refid", "study", "arm", "arm_n"))
  
# depth_freq <- proc_freq(rnmb.dat, depth, depth_rev_f)
# write_csv(depth_freq, "/Users/mgrant/Desktop/depth_freq.csv", na = "")
# depth_compare <- rnmb.dat %>% 
#   select(refid, study, depth_rev_f, depth)
# write_csv(depth_compare, "/Users/mgrant/Desktop/depth_compare.csv", na = "")
# 3 refids (2834 3491 4997) to be added 2022/02/21 17:01
# rnmb_dist_refids[rnmb_dist_refids %notin% rnmb_ma.dat$refid]

rm(study_arm_rnmb.dat, dichot_rnmb.dat, study_char_rnmb.dat)

## RESUME table --------------------------------------- (2022-02-21 17:35) @----
# RESUME: rnmb table
temp <- rnmb.dat %>%
  mutate(
    # dose_comb = neo_dose,
    dose_comb = case_when(
      arm == "Neo" ~ ifelse(!is.na(neo_dose + neo_max_dose), paste0(neo_dose, "-", neo_max_dose), as.character(neo_dose)),
      arm == "Sug" ~ ifelse(!is.na(sug_dose + sug_dose_max), paste0(sug_dose, "-", sug_dose_max), as.character(sug_dose)),
    ),
    dose_comb = ifelse(neo_dose_unit %in% c("mg"), paste0("<u>", dose_comb, "</u>"), dose_comb),
    nmb_agent = ifelse(is.na(nmbagent), "NS", nmbagent),
    tiva = ifelse(str_detect(gen_type, "tiva"), "&times;", NA),
    volatile = ifelse(str_detect(gen_type, "inhal"), "&times;", NA),
    anesth_ns = ifelse(is.na(gen_type), "&times;", NA),
    rnmb_where = coalesce(rnmb1_where, rnmb2_where), # approximation, but generally correct
    rnmb_dev = coalesce(rnmb1_dev, rnmb2_dev), # approximation, but generally correct
    # depth_rev = as.character(depth_rev),
    # depth_rev = coalesce(depth_rev, depth),
    # fix Wu study for pulled from distiller
    study_l = case_when(
      study == "Wu 2014" & arm_n > 75 ~ "[Wu 2014 (Chinese)](evidence_tables.html#2710)",
      study == "Wu 2014" & arm_n < 75 ~ "[Wu 2014 (Caucasian)](evidence_tables.html#2710)",
      # study == "Nemes 2017 (nl)" ~ "[Nemes 2017 (nl)](evidence_tables.html#3058)", # used normalized 
      TRUE ~ study_l),
  ) %>%
  # select(refid, study, arm, arm_id, nmbagent, nmb_agent) %>% 
  pivot_wider(id_cols = c(refid, study, arm, arm_id, everything()), names_from = nmb_agent, values_from = nmbagent, values_fn = ~ firstup(str_extract(.x, "\\w{3}"))) %>% 
  rename_with(.fn = ~ str_extract(.x, "\\w{3}"), .cols = vecuronium:cisatracurium) %>% 
  select(refid, design, study_l, study, arm_n, arm, depth_rev_f, deep:ns_depth, dose_comb, roc, vec, cis, var, tiva, volatile, anesth_ns, rnmb_where, rnmb_dev, mon_cat_f)
  
## rnmbData_ma ---------------------------------------- (2022-02-28 08:51) @----
rnmb_ma.dat <- read_csv("data/rnmb_read_011322.csv") %>% 
  clean_names() %>% 
  filter(!is.na(arm)) %>% 
  fill(refid, study) %>% 
  remove_empty(which = "cols") %>% 
  mutate(
    study_orig = study,
    study = str_extract(study, "\\w*.{0,1}\\w* \\d{4}"),
    mg_kg = ifelse(is.na(mg_kg) & !is.na(mg), paste0("<u>", mg, "</u>"), mg_kg),
    refid = as.numeric(refid)
  ) %>% 
  select(-mg) # milligram can delete

temp <- study_char.dat %>% select(refid, study_l, age, design, year)

rnmb_ma.dat <- inner_join(rnmb_ma.dat, temp, by = "refid") %>%
  relocate(c(study_orig, study_l, age, design, year), .before = study) %>%
  # fix links
  mutate(
    study_l = case_when(
      study_orig == "Wu 2014 (Chinese)" ~ "[Wu 2014 (Chinese)](evidence_tables.html#2710)",
      study_orig == "Wu 2014 (Caucasian)" ~ "[Wu 2014 (Caucasian)](evidence_tables.html#2710)",
      study_orig == "Nemes 2017 (nl)" ~ "[Nemes 2017 (nl)](evidence_tables.html#3058)",
      TRUE ~ study_l),
    design = fct_drop(design),
    depth_f = case_when(
      !is.na(deep) ~ "Deep",
      !is.na(mod) ~ "Moderate",
      !is.na(shallow) ~ "Shallow",
      !is.na(min) ~ "Minimal",
      !is.na(ns_depth) ~ "NS",
      TRUE ~ NA_character_
    ),
  ) %>% 
    arrange(age, design, year)

# rnmb.dat %>% 
#   mutate(across(deep:ns_depth, ~ ifelse(!is.na(.x), 1, 0))) %>% 
#   summarise(across(deep:ns_depth, ~ sum(.x)/length(.x)))

# add volatile anesthestic from study arm if necessary
# temp <- study_arm_rev.dat %>% 
#   select(refid, arm, arm_n, volatile) %>% 
#   filter(refid %in% rnmb.dat$refid) %>% 
#   rename(n = arm_n)
# 
# left_join(rnmb.dat, temp, by = c("refid, arm, arm_n"))

# get n from dichot data
# temp <- dichot.dat %>% 
#   filter(refid %in% rev_refids) %>% 
#   select(refid, study, starts_with("rnmb")) %>% 
#   remove_empty(which = "cols")

rm(temp)
```

### <u>Adults</u>

###  Agents, Anesthetics, and Monitors

<br/>

<font size = 4> Table `r table_n`. Reversal and neuromuscular blocking agents, anesthetic, and monitor in studies reporting residual neuromuscular block in adults. </font>

```{r rnmbDescrKbl}
## groupings ------------------------------------------ (2022-03-02 11:24) @----
# roc <- cell_spec("Rocuromiun", angle = -60, align = "r")
# rnmb_ma.dat %>%
#   filter(age == "Adult") %>%
#   arrange(design, study_l) %>%
#   select(study_l, refid, design) %>%
#   group_by(design) %>%
#   tally() %>%
#   ungroup() %>%
#   mutate(
#     end = cumsum(n),
#     start = end - n + 1
#   ) %>%
#   select(design, start, end)
## rnmbDescrKbl (updated 2022/01/16 09:56) ------------------------------
# rnmb.dat %>% 
rnmb_ma.dat %>% 
  filter(age == "Adult") %>%
  select(study_l, arm:ns_mon) %>% 
  relocate(n, .before = arm) %>% 
  group_by(study_l) %>% 
  mutate(
    # across(c(roc:ns_mon), ~ str_replace(.x, "x", "&#x25cf;")),
    across(c(roc:ns_mon), ~ str_replace(.x, "x", "&times;")),
    study_l = ifelse(row_number() != 1, "", study_l),
    study_l = str_replace(study_l, "Nemes 2017", "Nemes 2017^a^")) %>% 
  ungroup() %>% 
  select(study_l, n, arm, mg_kg, roc:ns_mon) %>% 
  kbl(
    booktabs = T, align = c("llcccccccccccc"), escape = FALSE, # format = "latex",
    col.names = c("Study", " N", "Agent", "mg/kg; <u>mg</u>", "Roc", "Vec", "Cis", "TIVA", "Volat", "NS", "AMG", "KMG", "Clin", "NS")
  ) %>%
  add_header_above(c(" " = 2, "Reversal" = 2, "NMBA" = 3, "Anesthetic" = 3, "Monitoring" =  4), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>% 
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "3em") %>% 
  column_spec(3, width = "4em") %>% 
  column_spec(4, width = "7em") %>% 
  column_spec(c(5:14), width = "4em") %>% 
  pack_top(., "RCT", 1, 30, indent_tf = FALSE) %>% 
  pack_top(., "Nonrandomized Trials", 31, 32, indent_tf = FALSE) %>% 
  pack_top(., "Prospective Cohort", 33, 43, indent_tf = FALSE) %>% 
  pack_top(., "Retrospective Cohort", 44, 45, indent_tf = FALSE) %>% 
    footnote(
    general = "NMBA: neuromuscular blocking agent; Neo: neostigmine; Sug: sugammadex; Cis: cisatracurium; Spont: spontaneous; Roc: rocuronium; Vec: vecuronium; TIVA: total intravenous anesthesia; Volat: volatile; NS: not specified; AMG: acceleromyography; EMG: electromyography; KMG: kinemyography; nl: normalized AMG; Clin: clinical.",
    alphabet = c("Used normalized readings."),
    general_title = "",
    footnote_as_chunk = FALSE
  )  

table_n <- tab_inc()
```

<br/>

```{r rnmbKblPrimary, eval = FALSE, include = FALSE}
## rnmbKbl (updated 2022/01/11 10:16) -------------------------------------
rnmb_prim.dat <- dichot.dat %>% 
  filter(refid %in% rev_refids) %>% 
  filter(if_any(starts_with("rnmb"), ~ !is.na(.))) %>% 
  select(refid, arm_id, study, study_l, year, design, age, subgroups, subgroup, starts_with("rnmb"), notes_d) %>% 
  filter(if_any(c(rnmb1_7, rnmb1_9, rnmb2_7, rnmb2_9, rnmb1_clinical, rnmb2_clinical),  ~ !is.na(.))) %>% 
  # only rcts
  filter(design == "rct") %>% 
  remove_empty(which = "cols")

rnmb_rev_agent <- study_arm.dat %>% 
  filter(refid %in% rnmb_prim.dat$refid) %>% 
  select(refid, study, arm_id, revagent, revtim, revtim_comment, -study)

rnmb_prim.dat <- 
  left_join(rnmb_prim.dat, rnmb_rev_agent, by = c("refid", "arm_id")) %>% 
  relocate(revagent, .after = arm_id)

write_csv(rnmb_prim.dat, "/Users/mgrant/Desktop/rnmb_prim.dat.csv", na = "")
# refids
temp <- rnmb_prim.dat %>% 
  select(refid, study) %>% 
  distinct()

write_csv(temp, "data/reversal_rnmb_refids.csv", na = "")

length(unique(rnmb_prim.dat$refid))
```

<br/>

<a id="kq4Tab4"></a>

###  Incidence

<br/>

<font size = 4> Table `r table_n`. Incidence of residual neuromuscular block and depth of anesthesia according to reversal in adults.</font>

```{r rnmbKbl}
## rnmbKbl (updated 2022/01/11 15:15) ------------------------------------
# calculate odds ratios for 0.9
dichot_format <- function(x) (x)

temp <- rnmb_ma.dat %>%
# temp <- rnmb.dat %>%
  filter(age == "Adult") %>%
  group_by(study_orig) %>%
  mutate(
    rx_n = n,
    comp_n = lag(n),
    rx_event = as.numeric(str_extract(lt_9, "\\d{1,2}")),
    comp_event = lag(as.numeric(str_extract(lt_9, "\\d{1,2}")))
  ) %>%
  ungroup() %>%
  mutate(
    # fix for multiarm
    rx_event = ifelse(refid == 3058, 1, rx_event),
    rx_n = ifelse(refid == 3058, 27, rx_n),
    rx_event = ifelse(refid == 2557, 5, rx_event),
    rx_n = ifelse(refid == 2557, 117, rx_n),
    rx_event = ifelse(refid == 2560, 4, rx_event),
    rx_n = ifelse(refid == 2560, 57, rx_n),
    or_ci_calc = case_when(
      if_all(c(rx_event, rx_n, comp_event, comp_n), ~ !is.na(.)) ~ odds_ratio_y(rx_event, rx_n, comp_event, comp_n),
      TRUE ~ NA_character_
    ),
    # relocate 
    or_ci_calc = str_replace(or_ci_calc, "NA \\(NA-NA\\)", NA_character_),
    # fix percentages
    lt_1_n = as.numeric(str_extract(lt_1, "\\d{1,2}")),
    lt_9_n = as.numeric(str_extract(lt_9, "\\d{1,2}")),
    lt_7_n = as.numeric(str_extract(lt_7, "\\d{1,2}")),
    clin_n = as.numeric(str_extract(clin, "\\d{1,2}")),
    lt_1_per = lt_1_n / n,
    lt_9_per = lt_9_n / n,
    lt_7_per = lt_7_n / n,
    clin_per = clin_n / n,
    lt_1 = ifelse(!is.na(lt_1_per), paste0(lt_1_n, " (", round_0(lt_1_per * 100), ")"), lt_1),
    lt_9 = ifelse(!is.na(lt_9_per), paste0(lt_9_n, " (", round_0(lt_9_per * 100), ")"), lt_9),
    lt_7 = ifelse(!is.na(lt_7_per), paste0(lt_7_n, " (", round_0(lt_7_per * 100), ")"), lt_7),
    clin = ifelse(!is.na(clin_per), paste0(clin_n, " (", round_0(clin_per * 100), ")"), clin),
  ) %>%
  group_by(study_l) %>% 
  mutate(
    or_ci_calc = lead(or_ci_calc)
  ) %>% 
  ungroup() %>% 
  select(refid, study_l, arm, n, lt_1, lt_9, lt_7, clin, rx_n:or_ci_calc, lt_1_n:clin_per, ns_rnmb, deep:ns_depth, or_ci_calc, design, age, study_orig, year, volatiles) %>%
  mutate(
    lt_1_bar = 0, lt_9_bar = 0, lt_7_bar = 0, clin_bar = 0,
    lt_1_bar = color_bar2("#fdcccc", fun = dichot_format)(lt_1_per),
    lt_9_bar = color_bar2("#fdcccc", fun = dichot_format)(lt_9_per),
    lt_7_bar = color_bar2("#fdcccc", fun = dichot_format)(lt_7_per),
    clin_bar = color_bar2("#fdcccc", fun = dichot_format)(clin_per),
    lt_1_bar = str_replace(lt_1_bar, ">.*<", paste0(">", lt_1, "<")),
    lt_9_bar = str_replace(lt_9_bar, ">.*<", paste0(">", lt_9, "<")),
    lt_7_bar = str_replace(lt_7_bar, ">.*<", paste0(">", lt_7, "<")),
    clin_bar = str_replace(clin_bar, ">.*<", paste0(">", clin, "<")),
    across(lt_1_bar:clin_bar, ~ str_replace(., ">NA<", "><")),
    across(lt_1_bar:clin_bar, ~ case_when(
       arm == "Sug" ~ str_replace_all(., "#fdcccc", color_1),
       arm == "Neo" ~ str_replace_all(., "#fdcccc", color_2),
       arm == "Placebo" ~ str_replace_all(., "#fdcccc", color_4),
       arm == "Spont" ~ str_replace_all(., "#fdcccc", color_4)),
       ),
    arm_c = case_when(
      arm == "Sug" ~ cell_spec(arm, color = color_1),
      arm == "Placebo" ~ cell_spec(arm, color = color_4),
      arm == "Spont" ~ cell_spec(arm, color = color_4),
      arm == "Neo" ~ cell_spec(arm, color = color_2),
    )
  )

mod <- color_bar2("#d6dbdf", fun = dichot_format)(1)
lt1 <- str_replace(mod, ">.*<", paste0(">", "    <1.0", "<"))
lt9 <- str_replace(mod, ">.*<", paste0(">", "    <0.9", "<"))
lt7 <- str_replace(mod, ">.*<", paste0(">", "    <0.7", "<"))
clin <- str_replace(mod, ">.*<", paste0(">", "    Clin", "<"))
ns_rnmb <- str_replace(mod, ">.*<", paste0(">", "      ns_rnmb", "<"))

temp %>%
  select(study_l, n, arm_c, deep:ns_depth, volatiles, lt_1_bar:clin_bar, ns_rnmb, or_ci_calc) %>%
  group_by(study_l) %>%
  mutate(
    # across(c(roc:ns_mon), ~ str_replace(.x, "x", "&#x25cf;")),
    across(c(deep:ns_depth), ~ str_replace(.x, "x", "&times;")),
    study_l = ifelse(row_number() != 1, "", study_l)
  ) %>%
  ungroup() %>%
  kbl(
    booktabs = T, align = c("llcccccclllllll"), escape = FALSE, # format = "latex")
    col.names = c("Study", " N", "Agent", "Deep", "Mod", "Shal", "Min", "NS", "Volat", lt1, lt9, lt7, clin, "NS", "OR (95% CI)^c^")
  ) %>%
  add_header_above(c(" " = 2, "Reversal" = 1, "Depth of Block^a^" = 5, " " = 1,"Residual Neuromuscular Block, N (%)^b^" = 5, "  " = 1), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "2em") %>%
  column_spec(3, width = "4em") %>%
  column_spec(c(4:8), width = "3em") %>%
  column_spec(9, width = "3em", popover = "Volatiles") %>% 
  column_spec(10, width = "4em", popover = "<1.0") %>%
  column_spec(11, width = "4em", popover = "<0.9") %>%
  column_spec(12, width = "4em", popover = "<0.7") %>%
  column_spec(13, width = "4em", popover = "Clinical") %>%
  column_spec(14, width = "3em", popover = "Not specified") %>%
  column_spec(15, width = or_width, popover = "OR (95% CI)") %>%
  pack_top(., "RCT", 1, 30, indent = FALSE) %>% 
  pack_top(., "Nonrandomized Studies of Intervention", 31, 32, indent = FALSE) %>% 
  pack_top(., "Prospective Cohort", 33, 43, indent = FALSE) %>% 
  pack_top(., "Retrospective Cohort", 44, 45, indent = FALSE) %>% 
  footnote(
    general = "OR: odds ratio; Neo: neostigmine; Sug: sugammadex; Spont: spontaneous; Roc: rocuronium; Vec: vecuronium; NS: not specified; nl: normalized AMG.",
    alphabet = c(
      "Depth of block categorized according to Naguib et al., Consensus Statement on Perioperative Use of Neuromuscular Monitoring. Anesth Analg 2018;127:71-80.",
      "Bar width for reference as 100%.",
      "Comparing the 2nd or last arm with previous. If no events in one arm, continuity correction used to allow estimating OR (Schwarzer G, Carpenter JR, Rücker G: Meta-analysis with R, Springer, 2015)."
    ),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

<a id="kq4Fig1"></a>

###  Pooled TOFR \<0.9 (RCTs)

```{r rnmbMetaData}
## rnmbMetaData (updated 2022/01/21 09:41) --------------------------------
rnmb_meta.dat <- temp %>%
  filter(design == "rct", arm %in% c("Neo", "Sug"), age == "Adult") %>%
  mutate(
    depth = case_when(
      !is.na(deep) ~ "Deep",
      !is.na(mod) ~ "Moderate",
      !is.na(shallow) ~ "Shallow",
      !is.na(min) ~ "Minimal",
      TRUE ~ "Not specified",
    )
  ) %>%
  select(refid, depth, volatiles, study_orig, lt_9_n, n, arm, year) %>%
  pivot_wider(id_cols = c("refid", "study_orig", "year", "depth", "volatiles"), names_from = "arm", values_from = c("lt_9_n", "n")) %>%
  filter(if_all(c(lt_9_n_Neo:n_Sug), ~ !is.na(.))) %>% 
  mutate(volatiles = ifelse(volatiles %in% "x", "Volatile Anesthetic", "No Volatiles")) %>% 
  arrange(year)
```

<br/>

<font size = 4> Figure `r figure_n`. Pooled residual neuromuscular block (TOFR \<0.9) from randomized trials comparing sugammadex and neostigmine by depth of block. </font>

```{r rnmbMetaRctByDepth, fig.width = 10, fig.height = 6}
## rnmbMetaRctByVolatile (updated 2022/01/21 09:58) -----------------------
rnmb_meta <- metabin(lt_9_n_Sug, n_Sug, lt_9_n_Neo, n_Neo, 
  data = rnmb_meta.dat,
  studlab = study_orig,
  sm = "OR",
  method = "MH",
  method.tau = "PM",
  hakn = TRUE,
  prediction = FALSE,
  # subset = !study_orig %in% c("Wu 2014 (Chinese)", "Wu 2014 (Caucasian)"),
  subgroup = depth)

forest(rnmb_meta,
  fixed = FALSE,
  label.e = "Sugammadex",
  label.c = "Neostigmine",
  rightcols = c("effect", "ci"),
  rightlabs = c("OR", "(95% CI)"),
  digits = 2,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = FALSE,
  fs.xlab = 11,
  pooled.events = TRUE,
  subgroup = TRUE,
  print.subgroup.name = FALSE,
  text.subgroup.nohet = TRUE,
  colgap.forest.left = unit(5, "mm"),
  xlim = c(0.001, 5),
  at = c(.001, 0.01, .1, 1, 2),
  xlab = "Favors:     Sugammadex          Neostigmine")

figure_n <- fig_inc()
```

<a id="kq4Fig2"></a>Pooled RR 0.17 (95% CI: 0.06, 0.49; I^2^ = 66%)

<br/>

<font size = 4> Figure `r figure_n`. Pooled residual neuromuscular block (TOFR \<0.9) from randomized trials comparing sugammadex and neostigmine by use of volatile anesthetics. </font>

```{r rnmbMetaRctByVolatile, fig.width = 10, fig.height = 5}
## rnmbMetaRctByVolatile ----------------------------- (2022-02-14 15:16) @----
rnmb_meta <- metabin(lt_9_n_Sug, n_Sug, lt_9_n_Neo, n_Neo, 
  data = rnmb_meta.dat,
  studlab = study_orig,
  sm = "OR",
  method = "MH",
  method.tau = "PM",
  hakn = TRUE,
  prediction = TRUE,
  subgroup = volatiles)

forest(rnmb_meta,
  fixed = FALSE,
  label.e = "Sugammadex",
  label.c = "Neostigmine",
  rightcols = c("effect", "ci"),
  rightlabs = c("OR", "(95% CI)"),
  digits = 2,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = FALSE,
  prediction = FALSE,
  fs.xlab = 11,
  pooled.events = TRUE,
  subgroup = TRUE,
  print.subgroup.name = FALSE,
  # text.subgroup.nohet = TRUE,
  colgap.forest.left = unit(5, "mm"),
  xlim = c(0.001, 5),
  at = c(.001, 0.01, .1, 1, 2),
  xlab = "Favors:     Sugammadex                   Neostigmine")

figure_n <- fig_inc()
```

<br/>

```{r commentedOut, eval=FALSE, include=FALSE}
<!-- ### &ensp;Pooled TOFR <0.9 (Prospective Cohort)  -->

<!-- <br/> -->

<!-- <font size = 4> Figure `r figure_n`. Pooled residual neuromuscular block (TOFR <0.9) from prospective cohorts comparing sugammadex and neostigmine. </font> -->

<!-- ```{r rnmbMetaProspCoh, fig.width = 10, fig.height = 3.1} -->
<!-- ## rnmbMetaRct (updated 2022/01/12 14:28)  -------------------------------- -->
<!-- rnmb_meta.dat <- temp %>% -->
<!--   filter(design %in% c("prospect_coh", "rct"), arm %in% c("Neo", "Sug"), age == "Adult") %>% -->
<!--   # filter(age == "Adult", arm %in% c("Neo", "Sug")) %>% -->
<!--   mutate( -->
<!--     depth = case_when( -->
<!--       !is.na(deep) ~ "Deep", -->
<!--       !is.na(mod) ~ "Moderate", -->
<!--       !is.na(shallow) ~ "Shallow", -->
<!--       !is.na(min) ~ "Minimal", -->
<!--       TRUE ~ "Not specified", -->
<!--     ) -->
<!--   ) %>% -->
<!--   select(refid, depth, volatiles, study_orig, lt_9_n, n, arm, year) %>% -->
<!--   pivot_wider(id_cols = c("refid", "study_orig", "year", "depth", "volatiles"), names_from = "arm", values_from = c("lt_9_n", "n")) %>% -->
<!--   filter(if_all(c(lt_9_n_Neo:n_Sug), ~ !is.na(.))) %>% -->
<!--   mutate(volatiles = ifelse(volatiles %in% "x", "Volatile Anesthetic", "No Volatiles")) %>%  -->
<!--   arrange(year) -->

<!-- rnmb_meta <- metabin(lt_9_n_Sug, n_Sug, lt_9_n_Neo, n_Neo,  -->
<!--   data = rnmb_meta.dat, -->
<!--   studlab = study_orig, -->
<!--   sm = "OR", -->
<!--   method = "MH", -->
<!--   method.tau = "PM", -->
<!--   hakn = FALSE, -->
<!--   prediction = FALSE, -->
<!--   subgroup = volatiles) -->

<!-- forest(rnmb_meta, -->
<!--   fixed = FALSE, -->
<!--   lab.e = "Sugammadex", -->
<!--   lab.c = "Neostigmine", -->
<!--   rightcols = c("effect", "ci"), -->
<!--   rightlabs = c("OR", "(95% CI)"), -->
<!--   digits = 2, -->
<!--   digits.tau2 = 1, -->
<!--   overall.hetstat = TRUE, -->
<!--   print.I2.ci = FALSE, -->
<!--   prediction = FALSE, -->
<!--   fs.xlab = 11, -->
<!--   pooled.events = TRUE, -->
<!--   subgroup = TRUE, -->
<!--   print.subgroup.name = FALSE, -->
<!--   text.subgroup.nohet = TRUE, -->
<!--   xlim = c(0.001, 5), -->
<!--   at = c(.001, 0.01, .1, 1, 2), -->
<!--   xlab = "Favors:     Sugammadex                   Neostigmine") -->

<!-- figure_n <- fig_inc() -->
<!-- ``` -->

<!-- <br/> -->


<!-- ### &ensp;Pooled TOFR <0.7 (RCTs)  -->

<!-- <br/> -->

<!-- <font size = 4> Figure `r figure_n`. Pooled residual neuromuscular block (TOFR <0.7) from randomized trials comparing sugammadex and neostigmine. </font> -->

<!-- ```{r rnmbMetaRctLt7, fig.width = 10, fig.height = 3.1} -->
<!-- ## rnmbMetaRct (updated 2022/01/12 14:28) -------------------------------- -->
<!-- rnmb_meta.dat <- temp %>% -->
<!--   filter(design == "rct", arm %in% c("Neo", "Sug"), age == "Adult") %>% -->
<!--   mutate( -->
<!--     depth = case_when( -->
<!--       !is.na(deep) ~ "Deep", -->
<!--       !is.na(mod) ~ "Moderate", -->
<!--       !is.na(shallow) ~ "Shallow", -->
<!--       !is.na(min) ~ "Minimal", -->
<!--       TRUE ~ "Not specified", -->
<!--     ) -->
<!--   ) %>% -->
<!--   select(refid, study_orig, lt_7_n, n, arm, year) %>% -->
<!--   pivot_wider(id_cols = c("refid", "study_orig", "year"), names_from = "arm", values_from = c("lt_7_n", "n")) %>% -->
<!--   filter(if_all(c(lt_7_n_Neo:n_Sug), ~ !is.na(.))) %>%  -->
<!--   arrange(year) -->

<!-- rnmb_meta <- metabin(lt_7_n_Sug, n_Sug, lt_7_n_Neo, n_Neo,  -->
<!--   data = rnmb_meta.dat, -->
<!--   studlab = study_orig, -->
<!--   sm = "OR", -->
<!--   method = "MH", -->
<!--   method.tau = "PM", -->
<!--   hakn = FALSE, -->
<!--   prediction = TRUE, -->
<!--   # subgroup = depth, -->
<!--   digits = 2) -->

<!-- forest(rnmb_meta, -->
<!--   fixed = FALSE, -->
<!--   lab.e = "Sugammadex", -->
<!--   lab.c = "Neostigmine", -->
<!--   rightcols = c("effect", "ci"), -->
<!--   rightlabs = c("OR", "(95% CI)"), -->
<!--   digits = 2, -->
<!--   digits.tau2 = 1, -->
<!--   overall.hetstat = TRUE, -->
<!--   print.I2.ci = FALSE, -->
<!--   prediction = TRUE, -->
<!--   fs.xlab = 11, -->
<!--   pooled.events = TRUE, -->
<!--   subgroup = FALSE, -->
<!--   # print.subgroup.name = FALSE, -->
<!--   # text.subgroup.nohet = TRUE, -->
<!--   xlim = c(0.001, 5), -->
<!--   at = c(.001, 0.01, .1, 1, 2), -->
<!--   xlab = "Favors:     Sugammadex                   Neostigmine") -->

<!-- figure_n <- fig_inc() -->
<!-- ``` -->

<!-- <br/> -->

<!-- <a id="revFig2"></a>  -->
  
```

### <u>Pediatric</u>

###  Agents, Anesthetics, and Monitors

<br/>

<font size = 4> Table `r table_n`. Reversal and neuromuscular blocking agents, anesthetic, and monitor in studies reporting residual neuromuscular block in pediatric patients. </font>

```{r rnmbDescrPedsKbl}
## groupings ------------------------------------------ (2022-03-02 11:24) @----
# rnmb_ma.dat %>%
#   filter(age == "Pediatric") %>%
#   arrange(design, study_l) %>%
#   select(study_l, refid, design) %>%
#   group_by(design) %>%
#   tally() %>%
#   ungroup() %>%
#   mutate(
#     end = cumsum(n),
#     start = end - n + 1
#   ) %>%
#   select(design, start, end)
# roc <- cell_spec("Rocuromiun", angle = -60, align = "r")
# temp <- rnmb.dat %>%
# rnmb.dat %>% 

## rnmbDescrPedsKbl ----------------------------------- (2022-03-02 11:25) @----
# rnmb.dat %>% 
rnmb_ma.dat %>% 
  filter(age == "Pediatric") %>%
  select(study_l, arm:ns_mon) %>% 
  relocate(n, .before = arm) %>% 
  group_by(study_l) %>% 
  mutate(
    # across(c(roc:ns_mon), ~ str_replace(.x, "x", "&#x25cf;")),
    across(c(roc:ns_mon), ~ str_replace(.x, "x", "&times;")),
    study_l = ifelse(row_number() != 1, "", study_l),
    study_l = str_replace(study_l, "Nemes 2017", "Nemes 2017^a^")) %>% 
  ungroup() %>% 
  kbl(
    booktabs = T, align = c("llcccccccccccc"), escape = FALSE, # format = "latex",
    col.names = c("Study", " N", "Agent", "mg/kg", "Roc", "Vec", "Cis", "TIVA", "Inh", "NS", "AMG", "KMG", "Clin", "NS")
  ) %>%
  add_header_above(c(" " = 2, "Reversal" = 2, "NMBA" = 3, "Anesthetic" = 3, "Monitoring" =  4), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>% 
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "3em") %>% 
  column_spec(3, width = "4em") %>% 
  column_spec(4, width = "6em") %>% 
  column_spec(c(5:14), width = "4em") %>% 
  pack_top(., "RCT", 1, 2, indent_tf = FALSE) %>% 
  pack_top(., "Prospective Cohort", 3, 4, indent_tf = FALSE) %>% 
    footnote(
    general = "NMBA: neuromuscular blocking agent; Neo: neostigmine; Sug: sugammadex; Cis: cisatracurium; Spont: spontaneous; Roc: rocuronium; Vec: vecuronium; TIVA: total intravenous anesthesia; Inh: inhalation; NS: not specified; AMG: acceleromyography; EMG: electromyography; KMG: kinemyography; nl: normalized AMG; Clin: clinical.",
    # alphabet = c(""),
    general_title = "",
    footnote_as_chunk = FALSE
  )  

table_n <- tab_inc()
```

<br/>

###  Incidence

<br/>

<font size = 4> Table `r table_n`. Incidence of residual neuromuscular block and depth of anesthesia according to reversal in pediatric patients.</font>

```{r rnmbPedsKbl}
## rnmbPedsKbl (updated 2022/01/13 10:11)  --------------------------------
dichot_format <- function(x) (x)

temp <- rnmb_ma.dat %>%
  filter(age == "Pediatric") %>%
  group_by(study_orig) %>%
  mutate(
    rx_n = n,
    comp_n = lag(n),
    rx_event = as.numeric(str_extract(lt_9, "\\d{1,2}")),
    comp_event = lag(as.numeric(str_extract(lt_9, "\\d{1,2}")))
  ) %>%
  ungroup() %>%
  mutate(
    # fix for multiarm
    rx_event = ifelse(refid == 3058, 1, rx_event),
    rx_n = ifelse(refid == 3058, 27, rx_n),
    rx_event = ifelse(refid == 2557, 5, rx_event),
    rx_n = ifelse(refid == 2557, 117, rx_n),
    rx_event = ifelse(refid == 2560, 4, rx_event),
    rx_n = ifelse(refid == 2560, 57, rx_n),
    or_ci_calc = case_when(
      if_all(c(rx_event, rx_n, comp_event, comp_n), ~ !is.na(.)) ~ odds_ratio_y(rx_event, rx_n, comp_event, comp_n),
      TRUE ~ NA_character_
    ),
    # relocate 
    or_ci_calc = str_replace(or_ci_calc, "NA \\(NA-NA\\)", NA_character_),
    # fix percentages
    lt_1_n = as.numeric(str_extract(lt_1, "\\d{1,2}")),
    lt_9_n = as.numeric(str_extract(lt_9, "\\d{1,2}")),
    lt_7_n = as.numeric(str_extract(lt_7, "\\d{1,2}")),
    clin_n = as.numeric(str_extract(clin, "\\d{1,2}")),
    lt_1_per = lt_1_n / n,
    lt_9_per = lt_9_n / n,
    lt_7_per = lt_7_n / n,
    clin_per = clin_n / n,
    lt_1 = ifelse(!is.na(lt_1_per), paste0(lt_1_n, " (", round_0(lt_1_per * 100), ")"), lt_1),
    lt_9 = ifelse(!is.na(lt_9_per), paste0(lt_9_n, " (", round_0(lt_9_per * 100), ")"), lt_9),
    lt_7 = ifelse(!is.na(lt_7_per), paste0(lt_7_n, " (", round_0(lt_7_per * 100), ")"), lt_7),
    clin = ifelse(!is.na(clin_per), paste0(clin_n, " (", round_0(clin_per * 100), ")"), clin),
  ) %>%
  group_by(study_l) %>% 
  mutate(
    or_ci_calc = lead(or_ci_calc)
  ) %>% 
  ungroup() %>% 
  select(refid, study_l, arm, n, lt_1, lt_9, lt_7, clin, rx_n:or_ci_calc, lt_1_n:clin_per, ns_rnmb, deep:ns_depth, or_ci_calc, design, age, study_orig, year) %>%
  mutate(
    lt_1_bar = 0, lt_9_bar = 0, lt_7_bar = 0, clin_bar = 0,
    lt_1_bar = color_bar2("#fdcccc", fun = dichot_format)(lt_1_per),
    lt_9_bar = color_bar2("#fdcccc", fun = dichot_format)(lt_9_per),
    lt_7_bar = color_bar2("#fdcccc", fun = dichot_format)(lt_7_per),
    clin_bar = color_bar2("#fdcccc", fun = dichot_format)(clin_per),
    lt_1_bar = str_replace(lt_1_bar, ">.*<", paste0(">", lt_1, "<")),
    lt_9_bar = str_replace(lt_9_bar, ">.*<", paste0(">", lt_9, "<")),
    lt_7_bar = str_replace(lt_7_bar, ">.*<", paste0(">", lt_7, "<")),
    clin_bar = str_replace(clin_bar, ">.*<", paste0(">", clin, "<")),
    across(lt_1_bar:clin_bar, ~ str_replace(., ">NA<", "><")),
    across(lt_1_bar:clin_bar, ~ case_when(
       arm == "Sug" ~ str_replace_all(., "#fdcccc", color_1),
       arm == "Neo" ~ str_replace_all(., "#fdcccc", color_2),
       arm == "Placebo" ~ str_replace_all(., "#fdcccc", color_4),
       arm == "Spont" ~ str_replace_all(., "#fdcccc", color_4)),
       ),
    arm_c = case_when(
      arm == "Sug" ~ cell_spec(arm, color = color_1),
      arm == "Placebo" ~ cell_spec(arm, color = color_4),
      arm == "Spont" ~ cell_spec(arm, color = color_4),
      arm == "Neo" ~ cell_spec(arm, color = color_2),
    )
  )

mod <- color_bar2("#d6dbdf", fun = dichot_format)(1)
lt1 <- str_replace(mod, ">.*<", paste0(">", "    <1.0", "<"))
lt9 <- str_replace(mod, ">.*<", paste0(">", "    <0.9", "<"))
lt7 <- str_replace(mod, ">.*<", paste0(">", "    <0.7", "<"))
clin <- str_replace(mod, ">.*<", paste0(">", "    Clin", "<"))
ns_rnmb <- str_replace(mod, ">.*<", paste0(">", "      ns_rnmb", "<"))

temp %>%
  select(study_l, n, arm_c, deep:ns_depth, lt_1_bar:clin_bar, ns_rnmb, or_ci_calc) %>%
  group_by(study_l) %>%
  mutate(
    # across(c(roc:ns_mon), ~ str_replace(.x, "x", "&#x25cf;")),
    across(c(deep:ns_depth), ~ str_replace(.x, "x", "&times;")),
    study_l = ifelse(row_number() != 1, "", study_l)
  ) %>%
  ungroup() %>%
  kbl(
    booktabs = T, align = c("llccccclllllll"), escape = FALSE, # format = "latex")
    col.names = c("Study", "N", "Agent", "Deep", "Mod", "Shal", "Min", "NS", lt1, lt9, lt7, clin, "NS", "OR (95% CI)^c^")
  ) %>%
  add_header_above(c(" " = 2, "Reversal" = 1, "Depth of Block^a^" = 5, "Residual Neuromuscular Block, N (%)^b^" = 5, "  " = 1), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "2em") %>%
  column_spec(3, width = "4em") %>%
  column_spec(c(4:8), width = "3em") %>%
  column_spec(c(9:12), width = "4em") %>%
  column_spec(c(13), width = "3em") %>%
  column_spec(14, width = or_width) %>%
  pack_top(., "RCT", 1, 2, indent_tf = FALSE) %>%
  pack_top(., "Prospective Cohort", 3, 4, indent_tf = FALSE) %>%
  footnote(
    general = "OR: odds ratio; Neo: neostigmine; Sug: sugammadex; Spont: spontaneous; Roc: rocuronium; Vec: vecuronium; NS: not specified; nl: normalized AMG.",
    alphabet = c(
      "Depth of block categorized according to Naguib et al., Consensus Statement on Perioperative Use of Neuromuscular Monitoring. Anesth Analg 2018;127:71-80.",
      "Bar width for reference as 100%.",
      "Comparing the 2nd or last arm with previous. If no events in one arm, continuity correction used to allow estimating OR (Schwarzer G, Carpenter JR, Rücker G: Meta-analysis with R, Springer, 2015)."
    ),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

## *Time to Recovery*

```{r timeData}
## verify all refids not run  ------------------------- (2022/02/11 08:48) @----
# time.dat <- suppressWarnings(read_csv("data/recoveryTime_012122.csv", col_types = c("nccccncccccccccccccncccccccc"))) %>%
#   clean_names() %>%
#   remove_empty(which = c("cols", "rows")) %>% # why new names
#   fill(refid, study, arm, mg_kg, n, depth) %>% 
#   mutate(id = row_number()) %>% 
#   relocate(id, .before = refid) %>% 
#   group_by(refid) %>% 
#   fill(volatiles) %>% 
#   ungroup()
# 
# temp <- readxl::read_xlsx("data/RevAgentSummary011122_mg.xlsx", sheet = "RecoveryTimeCopy", range = "A1:A160") %>%
#     clean_names() %>%
#   remove_empty(which = c("cols", "rows")) %>% # why new names
#   mutate(refid = as.numeric(refid)) %>%
#   filter(!is.na(refid)) %>%
#   distinct(refid)
# 
# mark_refid <- unique(time.dat$refid)
# curr_sp_refid <- unique(temp$refid)
# 
# sum(!mark_refid %in% curr_sp_refid)
# sum(!curr_sp_refid %in% mark_refid)

## data ----------------------------------------------- (2022-02-10 10:41) @----
time.dat <- suppressWarnings(read_csv("data/recoveryTime_012122.csv", col_types = c("nccccncccccccccccccncccccccc"))) %>%
  clean_names() %>%
  remove_empty(which = c("cols", "rows")) %>% # why new names
  fill(refid, study, arm, mg_kg, n, depth) %>% 
  mutate(id = row_number()) %>% 
  relocate(id, .before = refid) %>% 
  group_by(refid) %>% 
  fill(volatiles) %>% 
  ungroup()

time.dat8 <- time.dat %>% 
  filter(tofr == 0.8) %>% 
  group_by(refid) %>%
  mutate(
    arm_id = paste0(row_number(), "_8")
  ) %>% 
  ungroup() %>% 
  relocate(arm_id, .before = arm)

time.dat9 <- time.dat %>% 
  filter(tofr == 0.9) %>% 
  group_by(refid) %>%
  mutate(
    arm_id = paste0(row_number(), "_9")
  ) %>% 
  ungroup() %>% 
  relocate(arm_id, .before = arm)

time.dat1 <- time.dat %>% 
  filter(tofr == 1.0) %>% 
  group_by(refid) %>%
  mutate(
    arm_id = paste0(row_number(), "_9")
  ) %>% 
  ungroup() %>% 
  relocate(arm_id, .before = arm)

time.dat <- bind_rows(time.dat9, time.dat8, time.dat1) %>% 
  arrange(id)

# time.dat %>% tabyl(tofr)

## add study_char.dat data ---------------------------- (2022-02-10 10:42) @----
temp <- study_char.dat %>% select(refid, study_l, age, design, year)
time.dat <- inner_join(time.dat, temp, by = "refid") %>%
  relocate(c(study_l, age, design, year), .before = arm_id) %>%
  # fix links
  mutate(
    study_l = case_when(
      study == "Wu 2014 (Chinese)" ~ "[Wu 2014 (Chinese)](evidence_tables.html#2710)",
      study == "Wu 2014 (Caucasian)" ~ "[Wu 2014 (Caucasian)](evidence_tables.html#2710)",
      study == "Nemes 2017 (nl)" ~ "[Nemes 2017 (nl)](evidence_tables.html#3058)",
      TRUE ~ study_l
    )
  )

## add agent and anesthetic
temp <- study_arm.dat %>% 
  filter(refid %in% time.dat$refid) %>% 
  select(refid, nmbagent, study_arm_k, gen_type) %>% 
  mutate(
    arm = str_replace(study_arm_k, "rev_agt\\|", ""),
    arm = str_replace(arm, "an$", ""),
    arm = recode(arm, "other" = "placebo"),
    arm = firstup(arm)
  ) %>% 
  select(-study_arm_k)

time.dat <- left_join(time.dat, temp, by = c("refid", "arm")) %>% 
  relocate(c(nmbagent, gen_type), .before = amg) %>% 
  group_by(id) %>% 
  slice(1) %>% 
  ungroup()

# write_csv(time.dat, "/Users/mgrant/Desktop/time_1.dat.csv", na = "")
```

### <u>Adults RCTs</u>

###  Agents, Anesthetics, and Monitors

<br/>

<font size = 4> Table `r table_n`. By depth of block, reversal and neuromuscular blocking agents, anesthetic, and monitor in RCTs reporting time to recovery from neuromuscular block in adults. </font>

```{r timeDescrKblRct}
## timeDescrKblRct ------------------------------------ (2022-02-10 10:45) @----
# select only unique arms for studies reporting 0.8 and 0.9
time_9 <- time.dat %>%
  filter(tofr == 0.9)

time_8 <- time.dat %>%
  filter(tofr == 0.8) %>% 
  # only no time to tofr 0.9
  filter(!refid %in%  time_9$refid)

time_kbl_adult <- bind_rows(time_9, time_8) %>% 
  filter(age == "Adult") %>%
  # filter(refid == 2000) %>% 
  mutate(
    mg_kg = ifelse(arm %in%  c("Placebo", "Spont"), NA, mg_kg),
    roc = ifelse(nmbagent == "rocuronium", "&times;", NA),
    vec = ifelse(nmbagent == "vecuronium", "&times;", NA),
    cis = ifelse(nmbagent == "cisatracurium", "&times;", NA),
    miv = ifelse(nmbagent == "mivacurium", "&times;", NA),
    oth = ifelse(nmbagent %in% c("atracurium", "other"), "&times;", NA),
    tiva = ifelse(str_detect(gen_type, "tiva"), "&times;", NA),
    volatiles = ifelse(!is.na(volatiles), "&times;", NA),
    inhalation = ifelse(str_detect(gen_type, "inhal"), "&times;", NA),
    mg_kg = ifelse(!is.na(mg), paste0("<u>", mg, "</u>"), mg_kg),
    tofr_arm = str_extract(arm_id, pattern = "\\d{1}$"),
    arm_n_tofr = str_extract(arm_id, pattern = "^\\d{1}"),
    tofr_arm = factor(tofr_arm, levels = c(8, 9))
  ) %>% 
  mutate(
    depth_f = factor(depth, levels = c("Deep", "Moderate", "Shallow", "Minimal", "End of surgery", "Other"))
  ) %>%
  group_by(refid) %>% 
  mutate(
     depth_lowest_f = case_when(
      any(str_detect(depth, "Deep")) ~ "Deep",
      any(str_detect(depth, "Moderate")) ~ "Moderate",
      any(str_detect(depth, "Shallow")) ~ "Shallow",
      any(str_detect(depth, "End")) ~ "End of Surgery",
      any(str_detect(depth, "Other")) ~ "Other",
    ),
    depth_lowest_f = factor(depth_lowest_f, levels = c("Deep", "Moderate", "Shallow", "End of Surgery", "Other"))) %>% 
  ungroup() %>% 
  arrange(design, depth_lowest_f, year, refid) %>% 
  select(refid, year, design, age, depth, depth_f, study_l, id, arm_id, tofr_arm, arm_n_tofr, n, arm, mg_kg, roc, vec, cis, miv, oth,  volatiles, amg, emg, kmg, mmg, ns)

# time_kbl_adult %>%
#   filter(age == "Adult") %>%
#   arrange(design, study_l, depth_f) %>%
#   select(study_l, refid, design, depth_f) %>%
#   group_by(design, depth_f) %>%
#   tally() %>%
#   ungroup() %>%
#   mutate(
#     end = cumsum(n),
#     start = end - n + 1
#   ) %>%
#   select(design, depth_f, start, end)

time_kbl_adult %>%
  filter(design == "rct") %>% 
  group_by(study_l) %>%
  mutate(
    # depth_i = lag(depth),
    # depth = ifelse(!is.na(depth_i) & depth_i == depth, NA, depth),
    # depth = ifelse(!is.na(depth) & depth == "End of surgery", "End Surg", depth),
    # depth = ifelse(!is.na(depth) & depth == "Moderate", "Mod", depth),
    # depth = ifelse(!is.na(depth) & depth == "Shallow", "Shal", depth),
    # depth = ifelse(!is.na(depth) & depth == "Deep to Shallow", "Deep→Shal", depth),
    study_l = ifelse(row_number() != 1, "", study_l),
    tofr_arm = paste0("0.", tofr_arm),
    # depth = ifelse(row_number() != 1, "", depth),
  ) %>%
  ungroup() %>%
  select(-c(refid:age, depth_f, arm_id, id, arm_n_tofr)) %>%
  relocate(depth, .after = mg_kg) %>%
  relocate(tofr_arm, .after = depth) %>%
  kbl(
    booktabs = T, align = c("lllllcccccccccccc"), escape = FALSE, # format = "latex",
    col.names = c("Study", " N", "Agent", "mg/kg; <u>mg</u>", "Depth", "TOFR", "Roc", "Vec", "Cis", "Miv", "Oth", "Anesthetic", "AMG", "EMG", "KMG", "MMG", "NS")
  ) %>%
  add_header_above(c(" " = 2, "Reversal" = 2, " " = 1, "From" = 1, "Neuromuscular Blocking Agent" = 5, "Volatile" = 1, "Monitoring" = 5), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "4em") %>%
  column_spec(3, width = "4em", popover = "Reversal Agent") %>% 
  column_spec(4, width = "6em", popover = "mg/kg or <u>mg</u>") %>%
  column_spec(5, width = "5em", popover = "Depth of Block") %>%
  column_spec(6, width = "4em", popover = "Time from TOFR of") %>%
  column_spec(7, width = "3em", popover = "Rocuronium") %>%  
  column_spec(8, width = "3em", popover = "Vecuronium") %>%  
  column_spec(9, width = "3em", popover = "Cisatracurium") %>%  
  column_spec(10, width = "3em", popover = "Mivacurium") %>%  
  column_spec(11, width = "3em", popover = "Other") %>%  
  column_spec(12, width = "3em", popover = "Volatiles") %>%  
  column_spec(13, width = "3em", popover = "AMG") %>%  
  column_spec(14, width = "3em", popover = "EMG") %>%  
  column_spec(15, width = "3em", popover = "KMG") %>%  
  column_spec(16, width = "3em", popover = "MMG") %>%  
  column_spec(17, width = "3em", popover = "Not specified") %>%  
  pack_top(., "RCT", 1, 84, indent = FALSE) %>%
  # pack_top(., "Nonrandomized Studies of Intervention", 86, 93, indent = FALSE) %>%
  # pack_top(., "Prospective Cohort", 94, 107, indent = FALSE) %>%
  # pack_top(., "Retrospective Cohort", 108, 109, indent = FALSE) %>%
  footnote(
    general = "RCT: randomized controlled trial; Neo: neostigmine; Sug: sugammadex; Spont: spontaneous; Roc: rocuronium; Vec: vecuronium; Cis: cisatracurium; Miv: mivacurium; NS: not specified; AMG: acceleromyography; EMG: electromyography; KMG: kinemyography; MMG: mechanomyography; nl: normalized AMG; Shal: shallow; Surg: surgery.",
    # alphabet = c("Used normalized readings."),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

```{r timeResultsData}
# write_csv(time.dat, "/Users/mgrant/Desktop/time.dat.csv", na = "")

## timeResultsData ------------------------------------ (2022-02-10 10:46) @----
time_result_adult <- time.dat %>%
  filter(age == "Adult") %>%
  # filter(refid == 2287) %>% 
  mutate(
    roc = ifelse(nmbagent == "rocuronium", "&times;", NA),
    vec = ifelse(nmbagent == "vecuronium", "&times;", NA),
    cis = ifelse(nmbagent == "cisatracurium", "&times;", NA),
    miv = ifelse(nmbagent == "mivacurium", "&times;", NA),
    oth = ifelse(nmbagent %in% c("atracurium", "other"), "&times;", NA),
    tiva = ifelse(str_detect(gen_type, "tiva"), "&times;", NA),
    volatiles = ifelse(!is.na(volatiles), "&times;", NA),    
    inhalation = ifelse(str_detect(gen_type, "inhal"), "&times;", NA),
    mg_kg = ifelse(!is.na(mg), paste0("<u>", mg, "</u>"), mg_kg),
    tofr_arm = str_extract(arm_id, pattern = "\\d{1}$"),
    arm_n_tofr = str_extract(arm_id, pattern = "^\\d{1}"),
    tofr_arm = factor(tofr_arm, levels = c(8, 9))
  ) %>% 
  arrange(design, year, refid, desc(tofr_arm)) %>%
  group_by(refid) %>%
  mutate(
    tofr_compare = lag(tofr_arm, 2),
    tofr_compare = as.numeric(strtoi(tofr_compare)),
    tofr_arm = as.numeric(strtoi(tofr_arm)),
    diff = tofr_arm - tofr_compare,
    diff = ifelse(is.na(diff), 1, diff),
    depth_f = case_when(
      any(str_detect(depth, "Moderate")) ~ "Moderate",
      any(str_detect(depth, "Deep")) ~ "Deep",
      any(str_detect(depth, "Shallow")) ~ "Shallow",
      any(str_detect(depth, "Minimal")) ~ "Minimal",
      any(str_detect(depth, "End")) ~ "End of Surgery",
      any(str_detect(depth, "Other")) ~ "Other",
    ),
    depth_f = factor(depth_f, levels = c("Deep", "Moderate", "Shallow", "Minimal", "End of Surgery", "Other"))
  ) %>%
  ungroup() %>%
  # select(diff, refid, study, tofr_compare, tofr_arm, design, depth_f, year) %>% 
  arrange(design, depth_f, year, refid, desc(tofr_arm)) %>% 
  # relocate(diff, .before = refid) %>% 
  filter(diff %in% c(0, 1)) %>% # TODO: unclear if needed verify 
  mutate(
    mean = as.numeric(str_extract(mean_sd, "^\\d{1,2}\\.\\d{0,1}")),
    sd = str_extract(mean_sd, "\\d{1,2}\\.?\\d{0,2}\\)"),
    sd = as.numeric(str_replace(sd, "\\)", "")),
    conf_l = as.numeric(str_extract(mean_ci, "^\\d{1,2}\\.\\d{1,2}")),
    conf_u = as.numeric(str_extract(mean_ci, "\\d{1,2}\\.\\d{1,2}$")),
    sd = ifelse(is.na(sd) & !is.na(conf_l), sd_conf_cont_t(conf_l, conf_u, n), sd),
    med = as.numeric(str_extract(med_iqr, "^\\d{1,2}\\.?\\d{0,1}")),
    iqr_l =  str_extract(med_iqr, "\\(\\d{1,2}\\.\\d{1,2}"),
    iqr_l = as.numeric(str_replace(iqr_l, "\\(", "")),
    iqr_u =  str_extract(med_iqr, "\\d{1,2}\\.\\d{1,2}\\)"),
    iqr_u = as.numeric(str_replace(iqr_u, "\\)", "")),
    range_l = as.numeric(str_extract(range, "^\\d{1,2}\\.?\\d{0,2}")),
    range_u = as.numeric(str_extract(range, "\\d{1,3}\\.\\d{1,2}$")),
    mean_ci = ifelse(!is.na(mean_ci), paste0("(", mean_ci, ")"), mean_ci),
    range = ifelse(!is.na(range), paste0("(", range, ")"), range),
  ) %>%
  select(refid, year, design, age, depth, depth_f, study_l, study, id, arm_id, arm, mg_kg, time_from_rev, time_ns, tofr, n, mean_sd, mean_ci, med_iqr, range, mean, sd, med, iqr_l, iqr_u, range_l, range_u)

# to verify
# select(refid, year, design, age, depth, depth_f, study_l, study, id, arm_id, arm, mg_kg, time_from_rev, time_ns, tofr, n, mean_sd, mean_ci, med_iqr, range, mean, sd, med, iqr_l, iqr_u, range_l, range_u, conf_l, conf_u) %>% 
# select(mean_sd, mean, sd, mean_ci, conf_l, conf_u, med_iqr, med, iqr_l, iqr_u, range, range_l, range_u)
# time_result_adult

```

<br/>

<a id="kq4Tab8"></a>

###  Minutes to Recovery

<br/>

<font size = 4> Table `r table_n`. Time to recovery of neuromuscular block (TOFR \>0.9) according to depth of block at reversal in RCTs enrolling adults. </font>

```{r timeResultsRctAdult}
## timeResultsRctAdult -------------------------------- (2022-02-10 10:47) @----
temp <- time_result_adult %>%
  filter(design == "rct") %>%
  mutate(
    mean_med = coalesce(mean, med),
    # gunes 2019 set to missing as time referent not specified
    mean_med = ifelse(refid == 3285, NA, mean_med),
    study_l = ifelse(refid == 3285, str_replace(study_l, "Gunes 2019", "Gunes 2019^d^"), study_l),
    mean_med_bar = NA_character_,
    mean_med_bar = ifelse(arm %in% c("Spont", "Placebo"), bar_wn1d(mean_med, mean_med, color_4, 100), mean_med_bar),
    mean_med_bar = ifelse(arm %in% c("Sug"), bar_wn1d(mean_med, mean_med, color_1, 100), mean_med_bar),
    mean_med_bar = ifelse(arm %in% c("Neo"), bar_wn1d(mean_med, mean_med, color_2, 100), mean_med_bar),
   arm_c = case_when(
     arm == "Sug" ~ cell_spec(arm, color = color_1),
     arm == "Placebo" ~ cell_spec(arm, color = color_4),
     arm == "Spont" ~ cell_spec(arm, color = color_4),
     arm == "Neo" ~ cell_spec(arm, color = color_2),
   )
  ) %>%
  select(study_l, n, arm_c, mg_kg, depth_f, mean_sd, mean_ci, med_iqr, range, mean_med_bar, tofr)

# temp %>%
#   filter(tofr == 0.9) %>%
#   arrange(depth_f) %>%
#   select(depth_f) %>%
#   group_by(depth_f) %>%
#   tally() %>%
#   ungroup() %>%
#   mutate(
#     end = cumsum(n),
#     start = end - n + 1
#   ) %>%
#   select(depth_f, start, end)

temp %>%
  filter(tofr == 0.9) %>% 
  group_by(study_l) %>%
  mutate(
    study_l = ifelse(row_number() != 1, "", study_l),
  ) %>%
  ungroup() %>%
  select(-c(tofr, depth_f)) %>% 
  kbl(
    booktabs = T, align 
    = c("lllllllll"), escape = FALSE, # format = "latex")
    col.names = c("Study", " N", "Agent",  "mg/kg; <u>mg</u>", "M (SD)", "(95% CI)", "Med (IQR)", "(Range)", "M or Med^c^")) %>% 
  add_header_above(c(" " = 2, "Reversal" = 2, "Minutes from Reversal to TOFR > 0.9" = 5), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "2em") %>%
  column_spec(3, width = "4em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "8em", popover = "Mean (SD)") %>%
  column_spec(6, width = "8em", popover = "95% CI" ) %>%
  column_spec(7, width = "8em", popover = "Med (IQR") %>%
  column_spec(8, width = "8em", popover = "Range") %>%
  column_spec(9, width = "10em") %>% 
  pack_top(., "Deep Block^a^", 1, 12, indent_tf = FALSE) %>% 
  pack_top(., "Moderate Block^bc^", 13, 48, indent_tf = FALSE) %>% 
  pack_top(., "Shallow Block^a^", 49, 56, indent_tf = FALSE) %>% 
  pack_top(., "Minimal^a^", 57, 67, indent_tf = FALSE) %>% 
  pack_top(., "End of Surgery^a^", 68, 77, indent_tf = FALSE) %>% 
  footnote(
    general = "Neo: neostigmine; Sug: sugammadex; Spont: spontaneous; M: mean; Med: median; CI: confidence interval",
    alphabet = c(
      "Depth of block categorized according to Naguib et al., Consensus Statement on Perioperative Use of Neuromuscular Monitoring. Anesth Analg 2018;127:71-80.",
      "Included studies with moderate depth in neostigmine arm but deep for sugammadex.",
      "Bar width 0 to 100 minutes.",
      "Starting time not specified."
    ),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

<a id="revFig3"></a>

###   Pooled Reversal to TOFR \>0.9    

```{r metaTime9, fig.width = 10}
# , fig.height = 12}
## metaTime9 data ------------------------------------- (2022-02-10 10:50) @----
meta_time.dat <- time_result_adult %>%
  filter(design == "rct", tofr == 0.9) %>% 
  filter(arm %in% c("Sug", "Neo")) %>% 
  select(refid, study, arm, depth_f, n, mean, sd, med, iqr_l, iqr_u, range_l, range_u)

# exclude studies without sug neo comparison, ie single row
compare_refids <- meta_time.dat %>% 
  group_by(refid) %>% 
  mutate(rows = row_number()) %>% 
  slice_max(rows) %>% 
  ungroup() %>% 
  filter(rows == 2) %>% 
  select(refid, rows) %>% 
  pull(refid)

meta_time.dat <- meta_time.dat %>% 
  filter(refid %in% compare_refids) %>% 
  pivot_wider(names_from = "arm", values_from = n:range_u)

## meta analysis (updated 2022/01/18 10:27) ------------------------------
temp <- metacont(
  n.e = n_Sug, 
  n.c = n_Neo,
  # fixed = TRUE,
  mean.e = mean_Sug,
  sd.e = sd_Sug,
  median.e = med_Sug,
  q1.e = iqr_l_Sug,
  q3.e = iqr_u_Sug,
  min.e = range_l_Sug,
  max.e = range_u_Sug,
  mean.c = mean_Neo,
  sd.c = sd_Neo,
  median.c = med_Neo,
  q1.c = iqr_l_Neo,
  q3.c = iqr_u_Neo,
  min.c = range_l_Neo,
  max.c = range_u_Neo,
  data = meta_time.dat,
  # subgroup = depth_f,
  # subset = depth_f == "Shallow",
  sm = "MD",
  method.tau = "REML",
  hakn = FALSE,
  prediction = TRUE,
  studlab = study
)

forest_time <- function(time_meta){
  forest(time_meta,
  weight.study = "random",
  fixed = FALSE,
  label.e = "Sugammadex",
  label.c = "Neostigmine",
  print.tau2 = FALSE,
  print.tau = TRUE,
  print.tau.ci = TRUE,
  digits = 1,
  digits.sd = 1,
  digits.mean = 1,
  digits.tau = 1,
  digits.pval.Q = 2,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  print.subgroup.name = FALSE,
  bylab = FALSE,
  # overall = FALSE,
  fs.xlab = 10,
  # sortvar = -TE,
  xlim = c(-50, 10),
  rightcols = c("effect", "ci"),
  rightlabs = c("SD", "95% CI     "),
  xlab = "Favors Sugammadex      Favors Neostigmine",
  smlab = "Mean Difference (minutes)",
)
}

deep <- update.meta(temp, subset = depth_f == "Deep", prediction = FALSE)
moderate <- update.meta(temp, subset = depth_f == "Moderate")
shallow <- update.meta(temp, subset = depth_f == "Shallow", prediction = FALSE)
minimal <- update.meta(temp, subset = depth_f == "Minimal", prediction = FALSE)
end_surg <- update.meta(temp, subset = depth_f == "End of Surgery", prediction = FALSE)



## save ----------------------------------------------- (2022-02-10 14:08) @----
# forest_time(shallow)
# forest_time(deep)
# forest_time(minimal)
# forest_time(end_surg)

# summary(temp)

# forest(temp,
#   weight.study = "random",
#   fixed = FALSE,
#   label.e = "Sugammadex",
#   label.c = "Neostigmine",
#   print.tau2 = FALSE,
#   print.tau = TRUE,
#   print.tau.ci = TRUE,
#   digits = 1,
#   digits.sd = 1,
#   digits.mean = 1,
#   digits.tau = 1,
#   digits.pval.Q = 2,
#   overall.hetstat = TRUE,
#   print.I2.ci = TRUE,
#   print.subgroup.name = FALSE,
#   bylab = FALSE,
#   # overall = FALSE,
#   fs.xlab = 10,
#   # sortvar = -TE,
#   xlim = c(-50, 10),
#   rightcols = c("effect", "ci"),
#   rightlabs = c("SD", "95% CI     "),
#   xlab = "Favors Sugammadex      Favors Neostigmine",
#   smlab = "Mean Difference (minutes)"
# )

# 
# par(bty = "n", xaxt = "l", yaxt = "l")
# funnel(temp, contour = c(0.9, 0.95, 0.99))
# figure_n <- fig_inc()
# temp_1 <- update(temp, subgroup = NULL)
# metabias(temp_1)
# metabias(temp_1, plotit = TRUE, k.min = 5, method = "Pustejovsky")

```

<br/>

<font size = 4> Figure `r figure_n`. Difference in time to recovery in minutes (TOFR \>0.9) from deep block to reversal in RCTs enrolling adults. </font>

```{r metaTimeDeep, fig.width = 10, fig.height = 3}
forest_time(deep)
grid::grid.text("Deep Block", .1, .9, gp = grid::gpar(cex = 1.2))
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Difference in time to recovery in minutes (TOFR \>0.9) from moderate block to reversal in RCTs enrolling adults. </font>

```{r metaTimeModerate, fig.width = 10}
forest_time(moderate)
grid::grid.text("Moderate Block", .1, .95, gp = grid::gpar(cex = 1.2))
figure_n <- fig_inc()
```

Hartung-Knapp adjustment not applied to allow comparability with other levels of block ; overall result yielded the same confidence interval with or without.

<br/>

<font size = 4> Figure `r figure_n`. Difference in time to recovery in minutes (TOFR \>0.9) from shallow block to reversal in RCTs enrolling adults. </font>

```{r metaTimeShallow, fig.width = 10, fig.height = 2.5}
forest_time(shallow)
grid::grid.text("Shallow Block", .1, .9, gp = grid::gpar(cex = 1.2))
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Difference in time to recovery in minutes (TOFR \>0.9) from minimal block to reversal in RCTs enrolling adults. </font>

```{r metaTimeMinimal, fig.width = 10, fig.height = 2.5}
forest_time(minimal)
grid::grid.text("Minimal Block", .1, .9, gp = grid::gpar(cex = 1.2))
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Difference in time to recovery in minutes (TOFR \>0.9) from end of surgery block to reversal in RCTs enrolling adults. </font>

```{r metaTimeEndSurg, fig.width = 10, fig.height = 3}
forest_time(end_surg)
grid::grid.text("From End of Surgery", .1, .9, gp = grid::gpar(cex = 1.2))
figure_n <- fig_inc()
```

### <u>Adults Observational</u>

###  Agents, Anesthetics, and Monitors

<br/>

<font size = 4> Table `r table_n`. Reversal and neuromuscular blocking agents, anesthetic, and monitor in observational studies reporting time to recovery from neuromuscular block in adults. </font>

```{r timeDescrKblObs}
## timeDescrKblRct (updated 2022/01/17 14:02) -----------------------------
# time_kbl_adult %>%
#   filter(design != "rct") %>% 
#   arrange(design, study_l) %>%
#   select(study_l, refid, age, design) %>%
#   group_by(age, design) %>%
#   tally() %>%
#   ungroup() %>%
#   mutate(end = cumsum(n),
#          start = end - n + 1) %>%
#   select(age, design, start, end)

time_kbl_adult %>%
  filter(design != "rct") %>%
  group_by(study_l) %>%
  mutate(
    depth_i = lag(depth),
    depth = ifelse(!is.na(depth_i) & depth_i == depth, NA, depth),
    depth = ifelse(!is.na(depth) & depth == "End of surgery", "End Surg", depth),
    # depth = ifelse(!is.na(depth) & depth == "Moderate", "Mod", depth),
    # depth = ifelse(!is.na(depth) & depth == "Shallow", "Shal", depth),
    depth = ifelse(!is.na(depth) & depth == "Deep to Shallow", "Deep→Shal", depth),
    study_l = ifelse(row_number() != 1, "", study_l),
  ) %>%
  ungroup() %>%
  select(-c(refid:age, depth_f, id:arm_n_tofr, depth_i, cis, miv, oth, emg:ns)) %>%
  relocate(depth, .after = mg_kg) %>%
  kbl(
    booktabs = T, align = c("lllllccccc"), escape = FALSE, # format = "latex",
    col.names = c("Study", " N", "Agent (subgroup)", "mg/kg; <u>mg</u>", "Depth", "Roc", "Vec", "Anesthetic", "AMG")
  ) %>%
  add_header_above(c(" " = 2, "Reversal" = 2, "Block" = 1, "NMBA" = 2, "Volatile" = 1, "Monitoring" = 1), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "4em") %>%
  column_spec(3, width = "10em", popover = "Reversal Agent") %>%
  column_spec(4, width = "6em", popover = "mg/kg or <u>mg</u>") %>%
  column_spec(5, width = "5em", popover = "Depth of Block") %>%
  column_spec(6, width = "3em", popover = "Rocuronium") %>%
  column_spec(7, width = "3em", popover = "Vecuronium") %>%
  column_spec(8, width = "3em", popover = "Volatile") %>%
  column_spec(9, width = "3em", popover = "AMG") %>%
  pack_top(., "Nonrandomized Studies of Intervention", 1, 8, indent_tf = FALSE) %>%
  pack_top(., "Prospective Cohort", 9, 22, indent_tf = FALSE) %>%
  pack_top(., "Retrospective Cohort", 23, 24, indent_tf = FALSE) %>%
  footnote(
    general = c("Neo: neostigmine; Sug: sugammadex; Roc: rocuronium; Vec: vecuronium; AMG: acceleromyography."),
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

<a id="kq4Tab8"></a>

###  Minutes to Recovery

<br/>

<font size = 4> Table `r table_n`. Time to recovery of neuromuscular block (TOFR \>0.9) according to depth of block at reversal in observational studies enrolling adults.</font>

```{r timeResultsObsAdults}
## timeResultsRctAdults (updated 2022/01/18 10:39) ------------------------
temp <- time_result_adult %>%
  filter(design != "rct") %>%
  mutate(
    mean_med = coalesce(mean, med),
    # gunes 2019 set to missing as time referent not specified
    mean_med_bar = NA_character_,
    mean_med_bar = ifelse(arm %in% c("Spont", "Placebo"), bar_wn1d(mean_med, mean_med, color_4, 30), mean_med_bar),
    mean_med_bar = ifelse(str_detect(arm, "Sug"), bar_wn1d(mean_med, mean_med, color_1, 30), mean_med_bar),
    mean_med_bar = ifelse(str_detect(arm, "Neo"), bar_wn1d(mean_med, mean_med, color_2, 30), mean_med_bar),
   arm_c = case_when(
     str_detect(arm, "Sug") ~ cell_spec(arm, color = color_1),
     str_detect(arm, "Placebo") ~ cell_spec(arm, color = color_4),
     str_detect(arm, "Spont") ~ cell_spec(arm, color = color_4),
     str_detect(arm, "Neo") ~ cell_spec(arm, color = color_2),
   )
  ) %>%
  arrange(depth_f, design, refid) %>% 
  select(study_l, n, arm_c, design, mg_kg, depth_f, mean_sd, mean_ci, med_iqr, range, mean_med_bar, tofr)

temp %>%
  filter(tofr == 0.9) %>% 
  group_by(study_l) %>%
  mutate(
    study_l = ifelse(row_number() != 1, "", study_l),
  ) %>%
  ungroup() %>%
  select(-c(design, tofr, depth_f)) %>% 
  kbl(
    booktabs = T, align = c("lllllllll"), escape = FALSE, # format = "latex")
    col.names = c("Study", " N", "Agent",  "mg/kg", "M (SD)", "(95% CI)", "Med", "(Range)", "M or Med^a^")) %>% 
  add_header_above(c(" " = 2, "Reversal" = 2, "Minutes from Reversal to TOFR > 0.9" = 5), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "2em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "4em") %>%
  column_spec(5, width = "6em", popover = "Mean (SD)") %>%
  column_spec(6, width = "7em", popover = "95% CI" ) %>%
  column_spec(7, width = "5em", popover = "Med") %>%
  column_spec(8, width = "7em", popover = "Range") %>%
  column_spec(9, width = "8em", popover = "Mean or Median") %>% 
  pack_top(., "Deep Block^b^", 1, 10, indent_tf = FALSE) %>% 
  pack_sub_bold(., "Nonrandomized Studies of Interventions", 1, 4) %>% 
  pack_sub_bold(., "Prospective Cohort", 5, 8) %>% 
  pack_sub_bold(., "Retrospective Cohort", 9, 10) %>% 
  pack_top(., "Moderate Block^b^", 11, 14, indent_tf = FALSE) %>% 
  pack_sub_bold(., "Nonrandomized Studies of Interventions", 11, 14) %>% 
  pack_top(., "Shallow Block^b^", 15, 16, indent_tf = FALSE) %>% 
  pack_sub_bold(., "Prospective Cohort", 15, 16) %>%
  pack_top(., "Time from end of surgery", 17, 24, indent_tf = FALSE) %>% 
  pack_sub_bold(., "Prospective Cohort", 17, 24) %>%
  footnote(
    general = "Neo: neostigmine; Sug: sugammadex; Spont: spontaneous; M: mean; Med: median; CI: confidence interval; NS: not specified; RBW: actual body weight; IBW: ideal body weight; ",
    alphabet = c(
      "Bar width 0 to 30 minutes.",
      "Depth of block categorized according to Naguib et al., Consensus Statement on Perioperative Use of Neuromuscular Monitoring. Anesth Analg 2018;127:71-80."
    ),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

## *Adverse Events*

```{r adverse}
## adverse -------------------------------------------- (2022-02-28 16:07) @----
adverse.dat <- suppressWarnings(readxl::read_xlsx("data/RevAgentSummary011122_mg.xlsx",
  sheet = "Adverse Events", range = "A4:N79",
  col_types = c("numeric", rep("text", 6), "numeric", rep("text", 6))
)) %>%
  rename_with(., ~ tolower(.x)) %>%
  clean_names() %>%
  remove_empty(which = "cols") %>%
  mutate(refid = as.numeric(refid)) %>%
  remove_empty(which = "rows") %>%
  fill(refid:study) %>%
  mutate(
    antichol = ifelse(arm != "Neo", NA, antichol),
    design = tolower(design),
    anaph_n = as.numeric(str_extract(anaphylaxis, "^\\d*")),
    brady_n = as.numeric(str_extract(bradycardia, "^\\d*")),
    tachy_n = as.numeric(str_extract(tachycardia, "^\\d*")),
    arrhyth_n = as.numeric(str_extract(arrhythmias, "^\\d*")),
    other_n = str_extract(other, "^\\d*"),
    # age = ifelse(refid %in% c(3280, 7030, 2976, 3628, 2177, 3381, 3384), "peds", "adult")
  ) %>%
  relocate(c(anaph_n, brady_n, tachy_n, arrhyth_n, other_n), .after = n) %>% 
  select(-c(design)) %>% # replace with from study char
  left_join(., study_ident[, c("refid", "study_l", "age", "design")], by = "refid") %>% 
  relocate(study_l:design, .before = study)

popc.dat <- suppressWarnings(readxl::read_xlsx("data/RevAgentSummary011122_mg.xlsx",
  sheet = "POPC", range = "A4:U121",
  col_types = c("numeric", rep("text", 4), "numeric", rep("text", 15))
)) %>%
  rename_with(., ~ tolower(.x)) %>%
  clean_names() %>%
  remove_empty(which = "cols") %>%
  mutate(
    # fix cells with space
    refid = as.numeric(refid),
    across(everything(), ~ na_if(., " ")),
    across(everything(), ~ na_if(., " ")),
    hypox_le_90_n = as.numeric(str_extract(le_90, "^\\d*")),
    hypox_gt_90_95_n = as.numeric(str_extract(gt_90_95, "^\\d*")),
    hypox_ns_n = as.numeric(str_extract(ns, "^\\d*")),
    composite_n = as.numeric(str_extract(composite, "^\\d*")),
    altelectasis_n = as.numeric(str_extract(atelectasis, "^\\d*")),
    pneumonia_n = as.numeric(str_extract(pneumonia, "^\\d*")),
    obstruct_n = as.numeric(str_extract(up_obstruct, "^\\d*")),
    postop_reint_n = as.numeric(str_extract(postop_reint, "^\\d*")),
  ) %>%
  remove_empty(which = "rows") %>%
  mutate(across(.fns = ~ replace(., str_detect(., "^ {1,2}"), NA))) %>%
  fill(refid:study) %>%
  # select(-age) %>%
  left_join(., study_ident[, c("refid", "study_l", "age", "design")], by = "refid") %>%
  relocate(study_l:design, .before = study) %>%
  rename(arm_n = n) %>%
  left_join(., study_arm_rev.dat[, c("refid", "arm", "arm_n", "depth_rev_f")], by = c("refid", "arm", "arm_n")) %>%
  relocate(depth_rev_f, .before = arm) %>% 
  select(-c(le_90:resp_fail))
  
# refids from spreadsheets
adverse_refid <- unique(adverse.dat$refid)
popc_refid <- unique(popc.dat$refid)

```

### <u>Adults</u>

###  Reversal Agent Dosing

<br/>

<font size = 4> Table `r table_n`. Reversal agent dosing in randomized controlled trials. </font>

```{r reversalDoseRct}
## reversalDoseRct ------------------------------------ (2022-02-13 05:36) @----
adverse_rct <- adverse.dat %>% 
  filter(design == "rct", age == "Adult")

# reversal agent doses
adverse_rct %>% 
  mutate(
    arm = str_replace(arm, " .*$", ""),
  ) %>%
  filter(!arm %in% c("Placebo", "Spont")) %>% 
  rename(Agent = arm) %>% 
  group_by(Agent) %>% 
  tabyl(Agent, mg_kg) %>% 
  kbl(
    booktabs = T, align = c("lcccccccccccc"), escape = TRUE, # format = "latex",
    # col.names = c("            ID", "Study", "Analyzed (N)", "Centers", "Country^a^", "Surgery")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>% 
  add_header_above(c(" " = 1, "Dose (mg/kg), Studies (N)" = 12), line = TRUE, bold = TRUE, align = "c") %>% 
  column_spec(1, width = "8em") %>%
  column_spec(c(2:13), width = "4em")

table_n <- tab_inc()
```

<br/>

<font size = 4> Table `r table_n`. Reversal agent dosing in adult observational studies. </font>

```{r reversalDoseObs}
## reversalDoseObs ------------------------------------ (2022-02-13 05:36) @----
adverse_obs <- adverse.dat %>% 
  filter(!design == "rct", age == "Adult")

# reversal agent doses
adverse_obs %>% 
  mutate(
    arm = str_replace(arm, " .*", ""),
  ) %>%
  filter(!arm %in% c("Placebo", "Spont")) %>% 
  rename(Agent = arm) %>% 
  group_by(Agent) %>% 
  tabyl(Agent, mg_kg) %>% 
  kbl(
    booktabs = T, align = c("lccc"), escape = TRUE, # format = "latex",
    # col.names = c("            ID", "Study", "Analyzed (N)", "Centers", "Country^a^", "Surgery")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>% 
  add_header_above(c(" " = 1, "Dose (mg/kg), Studies (N)" = 3), line = TRUE, bold = TRUE, align = "c") %>% 
  column_spec(1, width = "8em") %>%
  column_spec(c(2:4), width = "4em") %>% 
  footnote(general = "NS: not specified.",
           # number = c("● Limited, ●● Important, ●●● Critical."),
           general_title = "",
           footnote_as_chunk = FALSE)

table_n <- tab_inc()
```

<br/>

###  Anaphylaxis

<br/>

<font size = 4> Table `r table_n`. Anaphylaxis in studies enrolling adult patients.  </font>

```{r anaphylaxis}
## anaphylaxis --------------------------------------- (2022-03-01 13:52) @----
adverse.dat %>% 
  filter(age %in% c("Adult", "All ages")) %>% 
  mutate(year = str_extract(study, "\\d{4}"),
         anaph_np = n_percent_dig(anaph_n, anaph_n/n * 100, 2),
         # design = factor(design, levels = c("prospective", "retro", "case control"))
         ) %>% 
  filter(!is.na(anaph_n)) %>%
  arrange(age, design, year, refid) %>% 
  select(study, arm, n, anaph_np) %>% 
  group_by(study) %>% 
  mutate(study = ifelse(row_number() != 1, NA, study)) %>% 
 kbl(
    booktabs = T, align = c("lllc"), escape = TRUE, # format = "latex",
    col.names = c("Study", "Agent", "N", "Anaphylaxis, N (%)")
  ) %>%
  row_spec(0, bold = TRUE, align = "l") %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>% 
  # add_header_above(c(" " = 1, "Dose (mg/kg)" = 6), line = TRUE, bold = TRUE, align = "c") %>% 
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "5em") %>% 
  column_spec(3, width = "6em") %>% 
  column_spec(4, width = "10em") %>% 
  pack_rows(., "Prospective Cohort", 1, 2, indent = FALSE) %>% 
  pack_rows(., "Retrospective Cohort", 3, 8, indent = FALSE) %>% 
  pack_sub_bold(., "All ages", 7, 8) %>% 
  # pack_rows(., "Case Control", 9, 10) %>% 
  footnote(general = "IBW: ideal body weight.",
  #        number = c("● Limited, ●● Important, ●●● Critical."),
           general_title = "",
           footnote_as_chunk = FALSE)

table_n <- tab_inc()
```

<br/>

###  Bradycardia

<br/>

<font size = 4> Table `r table_n`. Bradycardia </font>

```{r bradycardia}
## bradycardia ---------------------------------------- (2022-02-13 08:07) @----
adverse.dat %>% 
  filter(age == "Adult") %>% 
  mutate(year = str_extract(study, "\\d{4}"),
         brady_p = brady_n/n * 100,
         brady_np = n_percent_dig(brady_n, brady_n/n * 100, 1),
         design = factor(design, levels = c("rct", "prospective", "retro", "case control")),
          brady_p_bar = NA_character_,
  brady_p_bar = ifelse(arm %in% c("Spont", "Placebo"), bar_wn1d(brady_p, brady_p, color_4, 100), brady_p_bar),
  brady_p_bar = ifelse(arm %in% c("Sug"), bar_wn1d(brady_p, brady_p, color_1, 100), brady_p_bar),
  brady_p_bar = ifelse(str_detect(arm, "Neo"), bar_wn1d(brady_p, brady_p, color_2, 100), brady_p_bar),
  brady_p_bar = str_replace(brady_p_bar, ">.*<", ">&nbsp;<"),
  arm_c = case_when(
    str_detect(arm, "Sug") ~ cell_spec(arm, color = color_1),
    str_detect(arm, "Placebo") ~ cell_spec(arm, color = color_4),
    str_detect(arm, "Spont") ~ cell_spec(arm, color = color_4),
    str_detect(arm, "Neo") ~ cell_spec(arm, color = color_2),
  )) %>% 
  filter(!is.na(brady_n)) %>%
  arrange(design, year, refid) %>% 
  select(study, n, arm_c, mg_kg, brady_np, brady_p_bar) %>% 
  group_by(study) %>% 
  mutate(study = ifelse(row_number() != 1, NA, study)) %>% 
 kbl(
    booktabs = T, align = c("llllll"), escape = FALSE, # format = "latex",
    col.names = c("Study", "N", "Agent", "mg/kg", "Bradycardia, N (%)", " ")
  ) %>%
  row_spec(0, bold = TRUE, align = "l") %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>% 
  # add_header_above(c(" " = 1, "Dose (mg/kg)" = 6), line = TRUE, bold = TRUE, align = "c") %>% 
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "6em") %>% 
  column_spec(c(3,4), width = "8em") %>% 
  column_spec(5, width = "11em") %>%
  column_spec(6, width = "10em") %>%
  pack_rows(., "RCT", 1, 38, indent = FALSE) %>% 
  pack_rows(., "Prospective Cohort", 39, 42, indent = FALSE) %>% 
  pack_rows(., "Retrospective Cohort", 43, 44, indent = FALSE) %>% 
  # pack_rows(., "Case Control", 9, 10) %>% 
  footnote(general = "IBW: ideal body weight.",
  #        number = c("● Limited, ●● Important, ●●● Critical."),
           general_title = "",
           footnote_as_chunk = FALSE)

table_n <- tab_inc()
```

<br/>

###     *Pooled*

<font size = 4> Figure `r figure_n`. Bradycardia pooled results from RCTs comparing sugammadex and neostigmine. </font>

```{r pooledBrady, fig.width = 10, fig.height = 4.7}
## pooledBrady --------------------------------------- (2022-02-28 16:07) @----
brady_meta.dat <- adverse.dat %>%
  filter(age == "Adult", design == "rct") %>%
  filter(arm %in% c("Neo", "Sug", "Neo LBW", "Sug TBW", "Neo (no Mg)", "Spont (no Mg)")) %>%
  filter(!is.na(brady_n)) %>%
  mutate(arm = str_replace(arm, " .*", "")) %>%
  group_by(study) %>%
  filter(n() > 1) %>%
  ungroup() %>%
  filter(refid != 2004) %>% # Suy 2007 not sug:neo comparison
  select(refid, study, arm, brady_n, n, mg_kg) %>%
  pivot_wider(names_from = arm, values_from = c(brady_n, n, mg_kg)) %>% 
  # means when range neo
  mutate(
    mg_kg_Neo = case_when(
      study == "Schaller 2010"   ~ "0.02", 
      study == "Brueckmann 2015" ~ "0.03", 
      study == "Quang 2019"      ~ "0.05", 
      TRUE ~ mg_kg_Neo
    )
  ) 
  # add reversal depth; need to use only selected arm
  # left_join(., study_arm_rev.dat %>% select(refid, depth_rev_f), by = "refid")

brady_meta <- metabin(brady_n_Neo, n_Neo, brady_n_Sug, n_Sug, 
  data = brady_meta.dat,
  studlab = study,
  sm = "RR",
  method = "MH",
  method.tau = "PM",
  # allstudies = FALSE,
  hakn = TRUE,
  prediction = TRUE)
  # subset = !study_orig %in% c("Wu 2014 (Chinese)", "Wu 2014 (Caucasian)"),
  #subgroup = depth)

forest(brady_meta,
  fixed = FALSE,
  label.c = "Sugammadex",
  label.e = "Neostigmine",
  rightcols = c("effect", "ci"),
  rightlabs = c("RR", "(95% CI)"),
  digits = 2,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = TRUE,
  fs.xlab = 11,
  pooled.events = TRUE,
  allstudies = FALSE,
  colgap.left = "4mm",
  # subgroup = FALSE,
  # print.subgroup.name = FALSE,
  # text.subgroup.nohet = TRUE,
  colgap.forest.left = unit(5, "mm"),
  xlim = c(0.1, 100),
  at = c(0.1, 1, 10, 100),
  xlab = "Favors: Neostigmine             Sugammadex")

figure_n <- fig_inc()
```
Risk difference 9.1% (95% CI: 4.0, 14.1).

<br/>

<font size = 4> Figure `r figure_n`. Bradycardia in neostigmine arms by dose. </font>

```{r neoRate, fig.width = 10, fig.height = 4.7}
## neoRate -------------------------------------------- (2022-02-28 16:09) @----
temp <- brady_meta.dat %>% 
  arrange(mg_kg_Neo)

neo_brady_meta <- metaprop(brady_n_Neo, n_Neo,
  data = temp,
  studlab = study
)

neo_brady_meta$neo_dose <- temp$mg_kg_Neo

forest(neo_brady_meta,
  rightcols = c("effect", "ci", "neo_dose"),
  rightlabs = c("Rate", "95% CI    " , "Mean Dose (mg/kg)"),
  studlab = TRUE,
  comb.fixed = FALSE,
  digits = 2,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  fs.xlab = 11,
  pooled.events = TRUE,
  allstudies = FALSE,
  colgap.left = "5mm",
  # subgroup = FALSE,
  # print.subgroup.name = FALSE,
  # text.subgroup.nohet = TRUE,
  colgap.forest.left = unit(10, "mm"),
  log = "x"
)

figure_n <- tab_inc()
```

<br/>

###  Tachycardia (adults) RCTs.

<br/>

<font size = 4> Table `r table_n`. Tachycardia. </font>

```{r tachycardia}
## tachyData ------------------------------------ (2022-02-28 16:15) @----
# temp %>%
#     filter() %>%
#     arrange(age, design, study) %>%
#     select(study, refid, age, design) %>%
#     group_by(age, design) %>%
#     tally() %>%
#     ungroup() %>%
#     mutate(
#           end = cumsum(n),
#               start = end - n + 1
#             ) %>%
#     select(age, design, start, end)

adverse.dat %>% 
  filter(age == "Adult") %>% 
  mutate(year = str_extract(study, "\\d{4}"),
         tachy_p = tachy_n/n * 100,
         tachy_np = n_percent_dig(tachy_n, tachy_n/n * 100, 1),
         design = factor(design, levels = c("rct", "prospective", "retro", "case control")),
          tachy_p_bar = NA_character_,
  tachy_p_bar = ifelse(arm %in% c("Spont", "Placebo"), bar_wn1d(tachy_p, tachy_p, color_4, 100), tachy_p_bar),
  tachy_p_bar = ifelse(arm %in% c("Sug"), bar_wn1d(tachy_p, tachy_p, color_1, 100), tachy_p_bar),
  tachy_p_bar = ifelse(str_detect(arm, "Neo"), bar_wn1d(tachy_p, tachy_p, color_2, 100), tachy_p_bar),
  tachy_p_bar = str_replace(tachy_p_bar, ">.*<", ">&nbsp;<"),
  arm_c = case_when(
    str_detect(arm, "Sug") ~ cell_spec(arm, color = color_1),
    str_detect(arm, "Placebo") ~ cell_spec(arm, color = color_4),
    str_detect(arm, "Spont") ~ cell_spec(arm, color = color_4),
    str_detect(arm, "Neo") ~ cell_spec(arm, color = color_2),
  )) %>% 
  filter(!is.na(tachy_n)) %>%
  arrange(design, year, refid) %>% 
  select(study, n, arm_c, mg_kg, tachy_np, tachy_p_bar) %>% 
  group_by(study) %>% 
  mutate(study = ifelse(row_number() != 1, NA, study)) %>% 
 kbl(
    booktabs = T, align = c("llllll"), escape = FALSE, # format = "latex",
    col.names = c("Study", "N", "Agent", "mg/kg", "Tachycardia, N (%)", " ")
  ) %>%
  row_spec(0, bold = TRUE, align = "l") %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>% 
  # add_header_above(c(" " = 1, "Dose (mg/kg)" = 6), line = TRUE, bold = TRUE, align = "c") %>% 
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "6em") %>% 
  column_spec(c(3,4), width = "8em") %>% 
  column_spec(5, width = "11em") %>%
  column_spec(6, width = "10em") %>%
  pack_rows(., "RCT", 1, 10, indent = FALSE)
  # pack_rows(., "Prospective Cohort", 39, 42, indent = FALSE) %>% 
  # pack_rows(., "Retrospective Cohort", 43, 44, indent = FALSE) %>% 
  # pack_rows(., "Case Control", 9, 10) %>% 
  # footnote(general = "IBW: ideal body weight.",
  #        number = c(""),
  #          general_title = "",
  #          footnote_as_chunk = FALSE)

table_n <- tab_inc()  
```

<br/>

###     *Pooled*

<font size = 4> Figure `r figure_n`. Tachycardia pooled results from RCTs comparing sugammadex and neostigmine. </font>

```{r pooledTachy, fig.width = 10, fig.height = 3.5}
## pooledTachy --------------------------------------- (2022-02-28 16:07) @----
tachy_meta.dat <- adverse.dat %>%
  filter(age == "Adult", design == "rct") %>%
  filter(arm %in% c("Neo", "Sug", "Neo LBW", "Sug TBW", "Neo (no Mg)", "Spont (no Mg)")) %>%
  filter(!is.na(tachy_n)) %>%
  mutate(arm = str_replace(arm, " .*", "")) %>%
  group_by(study) %>%
  filter(n() > 1) %>%
  ungroup() %>%
  filter(refid != 2004) %>% # Suy 2007 not sug:neo comparison
  select(refid, study, arm, tachy_n, n, mg_kg) %>%
  pivot_wider(names_from = arm, values_from = c(tachy_n, n, mg_kg)) %>% 
  # means when range neo
  mutate(
    mg_kg_Neo = case_when(
      study == "Schaller 2010"   ~ "0.02", 
      study == "Brueckmann 2015" ~ "0.03", 
      study == "Quang 2019"      ~ "0.05", 
      TRUE ~ mg_kg_Neo
    )
  ) 
  # add reversal depth; need to use only selected arm
  # left_join(., study_arm_rev.dat %>% select(refid, depth_rev_f), by = "refid")

tachy_meta <- metabin(tachy_n_Neo, n_Neo, tachy_n_Sug, n_Sug, 
  data = tachy_meta.dat,
  studlab = study,
  sm = "RR",
  method = "MH",
  method.tau = "PM",
  # allstudies = FALSE,
  hakn = FALSE,
  prediction = FALSE)
  # subset = !study_orig %in% c("Wu 2014 (Chinese)", "Wu 2014 (Caucasian)"),
  #subgroup = depth)

forest(tachy_meta,
  fixed = FALSE,
  label.c = "Sugammadex",
  label.e = "Neostigmine",
  rightcols = c("effect", "ci"),
  rightlabs = c("RR", "(95% CI)"),
  digits = 2,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = FALSE,
  fs.xlab = 11,
  pooled.events = TRUE,
  allstudies = FALSE,
  colgap.left = "4mm",
  # subgroup = FALSE,
  # print.subgroup.name = FALSE,
  # text.subgroup.nohet = TRUE,
  colgap.forest.left = unit(5, "mm"),
  xlim = c(0.1, 100),
  at = c(0.1, 1, 10, 100),
  xlab = "Favors: Neostigmine             Sugammadex")

figure_n <- fig_inc()
```

<br/>

###  Arrhythmias (adults) RCTs.

<br/>

<font size = 4> Table `r table_n`. Tachycardia. </font>

```{r arrythmia}
## arrhythmia ----------------------------------------- (2022-02-28 16:15) @----
# temp %>%
#     filter() %>%
#     arrange(age, design, study) %>%
#     select(study, refid, age, design) %>%
#     group_by(age, design) %>%
#     tally() %>%
#     ungroup() %>%
#     mutate(
#           end = cumsum(n),
#               start = end - n + 1
#             ) %>%
#     select(age, design, start, end)

adverse.dat %>% 
  filter(age == "Adult") %>% 
  mutate(year = str_extract(study, "\\d{4}"),
         arrhyth_p = arrhyth_n/n * 100,
         arrhyth_np = n_percent_dig(arrhyth_n, arrhyth_n/n * 100, 1),
         design = factor(design, levels = c("rct", "prospective", "retro", "case control")),
          arrhyth_p_bar = NA_character_,
  arrhyth_p_bar = ifelse(arm %in% c("Spont", "Placebo"), bar_wn1d(arrhyth_p, arrhyth_p, color_4, 100), arrhyth_p_bar),
  arrhyth_p_bar = ifelse(arm %in% c("Sug"), bar_wn1d(arrhyth_p, arrhyth_p, color_1, 100), arrhyth_p_bar),
  arrhyth_p_bar = ifelse(str_detect(arm, "Neo"), bar_wn1d(arrhyth_p, arrhyth_p, color_2, 100), arrhyth_p_bar),
  arrhyth_p_bar = str_replace(arrhyth_p_bar, ">.*<", ">&nbsp;<"),
  arm_c = case_when(
    str_detect(arm, "Sug") ~ cell_spec(arm, color = color_1),
    str_detect(arm, "Placebo") ~ cell_spec(arm, color = color_4),
    str_detect(arm, "Spont") ~ cell_spec(arm, color = color_4),
    str_detect(arm, "Neo") ~ cell_spec(arm, color = color_2),
  )) %>% 
  filter(!is.na(arrhyth_n)) %>%
  arrange(design, year, refid) %>% 
  select(study, n, arm_c, mg_kg, arrhyth_np, arrhyth_p_bar) %>% 
  group_by(study) %>% 
  mutate(study = ifelse(row_number() != 1, NA, study)) %>% 
 kbl(
    booktabs = T, align = c("llllll"), escape = FALSE, # format = "latex",
    col.names = c("Study", "N", "Agent", "mg/kg", "Arrhythmia, N (%)", " ")
  ) %>%
  row_spec(0, bold = TRUE, align = "l") %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>% 
  # add_header_above(c(" " = 1, "Dose (mg/kg)" = 6), line = TRUE, bold = TRUE, align = "c") %>% 
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "6em") %>% 
  column_spec(c(3,4), width = "8em") %>% 
  column_spec(5, width = "11em") %>%
  column_spec(6, width = "10em")
  # pack_rows(., "RCT", 1, 10, indent = FALSE)
  # pack_rows(., "Prospective Cohort", 39, 42, indent = FALSE) %>% 
  # pack_rows(., "Retrospective Cohort", 43, 44, indent = FALSE) %>% 
  # pack_rows(., "Case Control", 9, 10) %>% 
  # footnote(general = "IBW: ideal body weight.",
  #        number = c(""),
  #          general_title = "",
  #          footnote_as_chunk = FALSE)

table_n <- tab_inc()  
```

<br/>

## *Postoperative Pulmonary Complications*

###  Hypoxia (adults)

<font size = 4> Table `r table_n`. Hypoxia </font>

<br/>

```{r hypoxia} 
## groupings ------------------------------------------ (2022-03-02 08:30) @----
# temp %>%
#   filter() %>%
#   arrange(design, study) %>%
#   select(study, design) %>%
#   group_by(design) %>%
#   tally() %>%
#   ungroup() %>%
#   mutate(
#     end = cumsum(n),
#     start = end - n + 1
#   ) %>%
#   select(design, start, end)

## hypoxia -------------------------------------------- (2022-03-02 08:01) @----
hypox_dat <- popc.dat %>%
  filter(age == "Adult") %>%
  mutate(
    year = str_extract(study, "\\d{4}"),
    hypox_defn = case_when(
      !is.na(hypox_le_90_n) ~ "≤90",
      !is.na(hypox_gt_90_95_n) ~ "90-95",
      !is.na(hypox_ns_n) ~ "NS",
      TRUE ~ NA_character_
    ),
    hypox_n = case_when(
      !is.na(hypox_le_90_n) ~ hypox_le_90_n,
      !is.na(hypox_gt_90_95_n) ~ hypox_gt_90_95_n,
      !is.na(hypox_ns_n) ~ hypox_ns_n
      # TRUE ~ NA
    ),
    hypox_p = case_when(
      !is.na(hypox_le_90_n) ~ hypox_le_90_n / arm_n,
      !is.na(hypox_gt_90_95_n) ~ hypox_gt_90_95_n / arm_n,
      !is.na(hypox_ns_n) ~ hypox_ns_n / arm_n,
      # TRUE ~ NA
    ),
    hypox_np = case_when(
      !is.na(hypox_le_90_n) ~ n_percent_dig(hypox_le_90_n, hypox_le_90_n / arm_n * 100, 1),
      !is.na(hypox_gt_90_95_n) ~ n_percent_dig(hypox_gt_90_95_n, hypox_gt_90_95_n / arm_n * 100, 1),
      !is.na(hypox_ns_n) ~ n_percent_dig(hypox_ns_n, hypox_ns_n / arm_n * 100, 1),
      # TRUE ~ NA
    )
  )

hypox_dat %>%
  mutate(
    hypox_p_bar = NA_character_,
    hypox_p_bar = ifelse(arm %in% c("Spont", "Placebo"), bar_wn1d(hypox_p * 100, hypox_p * 100, color_4, 100), hypox_p_bar),
    hypox_p_bar = ifelse(arm %in% c("Sug"), bar_wn1d(hypox_p * 100, hypox_p * 100, color_1, 100), hypox_p_bar),
    hypox_p_bar = ifelse(str_detect(arm, "Neo"), bar_wn1d(hypox_p * 100, hypox_p * 100, color_2, 100), hypox_p_bar),
    hypox_p_bar = str_replace(hypox_p_bar, ">.*<", ">&nbsp;<"),
    arm_c = case_when(
      str_detect(arm, "Sug") ~ cell_spec(arm, color = color_1),
      str_detect(arm, "Placebo") ~ cell_spec(arm, color = color_4),
      str_detect(arm, "Spont") ~ cell_spec(arm, color = color_4),
      str_detect(arm, "Neo") ~ cell_spec(arm, color = color_2),
    )
  ) %>%
  filter(!is.na(hypox_np)) %>%
  arrange(hypox_defn, design, year, refid) %>%
  select(study, arm_n, arm_c, mg_kg, depth_rev_f, hypox_np, hypox_p_bar) %>%
  group_by(study) %>%
  mutate(study = ifelse(row_number() != 1, NA, study)) %>%
  kbl(
    booktabs = T, align = c("lllllll"), escape = FALSE, # format = "latex",
    col.names = c("Study", "N", "Agent", "mg/kg", "Reversal", "Hypoxia, N (%)", " ")
  ) %>%
  add_header_above(c(" " = 4, " Depth at" = 1, " " = 2), bold = TRUE, align = "l", line = FALSE) %>%
  row_spec(0, bold = TRUE, align = "l") %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "6em") %>%
  column_spec(c(3, 5), width = "8em") %>%
  column_spec(6, width = "11em") %>%
  column_spec(7, width = "10em") %>%
  pack_topnoind(., "    SaO^2^ ≤90%", 1, 20) %>%
  pack_sub_bold(., "RCT", 1, 15) %>%
  pack_sub_bold(., "Nonrandomized Trials", 16, 17) %>%
  pack_sub_bold(., "Prospective Cohort", 18, 20) %>%
  pack_topnoind(., "    SaO^2^ 90-95%", 21, 38) %>%
  pack_sub_bold(., "RCT", 21, 38) %>%
  pack_topnoind(., "SaO^2^ Not Specfified", 39, 42) %>%
  pack_sub_bold(., "    RCT", 39, 40) %>%
  pack_sub_bold(., "Retrospective Cohort", 41, 42) %>%
  footnote(
    general = "NS: not specified; mod: moderate; endsurg: end of surgery; shall: shallow; min: minimal; oth: other ",
    # number = c(""),
    general_title = "",
    footnote_as_chunk = FALSE
  )

table_n <- tab_inc()
```

<br/>

###     *Pooled*

<br/>

<font size = 4> Figure `r figure_n`. Pooled hypoxia by definition in adult RCTs. </font>

```{r hypoxiaPooled,  fig.width = 10, fig.height = 7.5}
## hypoxiaPooled -------------------------------------- (2022-03-02 10:25) @----
hypox_meta.dat <- hypox_dat %>% 
  filter(design == "rct", str_detect(arm, "Neo|Sug"), !is.na(hypox_n), refid %notin% c(7015, 4935)) %>% 
  mutate(arm = case_when(
    str_detect(arm, "Neo") ~ "Neo",
    str_detect(arm, "Sug") ~ "Sug"
  ),
  hypox_defn = case_when(
    str_detect(hypox_defn, "90-95") ~ "SaO2 90% to 95%",
    str_detect(hypox_defn, "90") ~ "SaO2 ≤90%",
    str_detect(hypox_defn, "NS") ~ "SaO2 Not Specified",
  )) %>% 
  select(refid, year, study, arm, hypox_defn, hypox_n, arm_n) %>%  
  arrange(hypox_defn, year) %>% 
  pivot_wider(id_cols = c(refid, year, study, hypox_defn), names_from = arm, values_from = c(hypox_n, arm_n))

hypox_meta <- metabin(hypox_n_Sug, arm_n_Sug, hypox_n_Neo, arm_n_Neo,
  data = hypox_meta.dat,
  studlab = study,
  sm = "RR",
  method = "MH",
  method.tau = "PM",
  hakn = TRUE,
  prediction = TRUE,
  # subset = !study_orig %in% c("Wu 2014 (Chinese)", "Wu 2014 (Caucasian)"),
  subgroup = hypox_defn)

forest(hypox_meta,
  fixed = FALSE,
  label.e = "Sugammadex",
  label.c = "Neostigmine",
  rightcols = c("effect", "ci"),
  rightlabs = c("RR", "(95% CI)"),
  digits = 2,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = TRUE,
  fs.xlab = 11,
  pooled.events = TRUE,
  subgroup = TRUE,
  print.subgroup.name = FALSE,
  text.subgroup.nohet = TRUE,
  colgap.forest.left = unit(5, "mm"),
  # xlim = c(0.001, 5),
  # at = c(.001, 0.01, .1, 1, 2),
  xlab = "Favors: Sugammadex             Neostigmine")

figure_n <- fig_inc()



```






<br/><br/>

<hr style="height:2px;border-width:0;color:gray;background-color:gray">

<br/>

# **Study/Participant Detail**

<br/>

### *Study Characteristics*

###   <u>Adult Studies</u>

<br>

<font size = 4> Table `r table_n`. Characteristics of studies including only adults. </font>

```{r createStudyCharTable, include = FALSE}
## (updated 2021/01/12 09:30) createStudyCharTable ------------------------
study_char_table <- study_char.dat %>%
  filter(refid %in% rev_refids) %>% 
  mutate(
    dates = str_c(date_start, "-", date_end),
    country = countrycode::countryname(country, destination = "iso3c"),
    low_r = noquote(if_else(non_vh_hdi == "yes", "\U2022", "", "")),
    n = n_enrolled,
    n_anal = n_analyze,
    pilot = noquote(if_else(pilot == "yes", "\U2022", "", "")),
    setting = case_when(
      !is.na(hospital) ~ "Hosp",
      !is.na(ambulatory) ~ "Amb",
      !is.na(other_setting) ~ "Other"
    ),
    gen = noquote(if_else(!is.na(general), "\U2022", "", "")),
    reg = noquote(if_else(!is.na(regional), "\U2022", "", "")),
    sed = noquote(if_else(!is.na(sedation), "\U2022", "", "")),
    registered = noquote(if_else(registered == "yes", "\U2022", "", "")),
    across(surg_various:surg_other, ~ str_replace(.x, "surg_", "")),
    across(surg_various:surg_other, ~ str_c(.x, ", ")),
    across(surg_various:surg_other, ~ firstup(.x)),
    across(surg_various:surg_other, ~ replace_na(.x, "")),
    surg_list = ifelse(grepl("abdom", surg_list), "Abdom, ", ""),
    surgs = str_c(surg_various, surg_car, surg_cr, surg_gyn, surg_gi, surg_gen, surg_headneck, surg_hep, surg_neuro, surg_opth, surg_oralmax, surg_ortho, surg_otolar, surg_plastic, surg_thor, surg_urol, surg_list),
    surgs = str_replace(surgs, "Otolar", "ENT"),
    surgs = str_replace(surgs, "Car", "Card"),
    surgs = str_replace(surgs, "Cr", "GI"),
    surgs = str_replace(surgs, "Gi", "GI"),
    surgs = str_replace(surgs, "Headneck", "ENT"),
    surgs = str_sub(surgs, 1, nchar(surgs) - 2),
    country = ifelse(grepl("USA", country), "USA", country),
    country = ifelse(grepl("UK", country), "UK", country),
    country = ifelse(!is.na(non_vh_hdi), str_c(country, "^a^"), country)
  ) %>%
  arrange(age, design, year, study) %>%
  select(refid, age, design, study, dates, country, n, pilot, setting, gen, reg, -sed,  surgs, registered)

```

```{r studyCharKableAdult, echo = FALSE}
## (updated 2021/01/12 19:27) ---------------------------------------------
temp <- study_char_table %>%
  arrange(age, design, study) %>% 
  filter(age == "Adult") %>% 
  select(study, refid, age, design) %>% 
  group_by(age, design) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(end = cumsum(n),
         start = end - n + 1) %>% 
  select(age, design, start, end)

study_char_table %>%
  filter(age == "Adult") %>% 
  select(!c(refid, age, design)) %>% 
  kbl(booktabs = T, align = c("llllcccclc"), 
      # format = "latex",
      col.names = c("Study", "Dates", "Country", " N ", "Pilot", 
                    "Setting", "Gen", "Reg", "Type of Surgery", "Registered")) %>%
  add_header_above(c(" " = 6, "Anesthesia" = 2, " " = 2), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>% 
  column_spec(2, width = "8em") %>% 
  column_spec(3, width = "5em") %>% 
  column_spec(4, width = "4em") %>% 
  column_spec(5, width = "4em") %>% 
  column_spec(6, width = "5em") %>% 
  column_spec(7, width = "3em") %>% 
  column_spec(8, width = "3em") %>% 
  column_spec(9, width = "15em") %>% 
  column_spec(10, width = "5em") %>% 
  # column_spec(2, width = "2em") %>% 
  pack_topnoind(., "RCT", 1, 105) %>% 
  pack_topnoind(., "Quasi-Experimental", 106, 106) %>% 
  pack_topnoind(., "Nonrandomized Studies of Interventions", 107, 114) %>% 
  pack_topnoind(., "Prospective Cohort", 115, 126) %>%
  pack_topnoind(., "Retrospective Cohort", 127, 136) %>% 
  # pack_sub(., "Case-control", 98, 98) %>% 
  # pack_sub(., "Before-after", 99, 99) %>% 
  # pack_sub(., "RCT", 100, 100) %>%
  # pack_sub(., "Crossover", 101, 109) %>%
  # pack_sub(., "Nonrandomized Studies of Interventions", 110, 111) %>% 
  # pack_top(., "Pediatric, Surgical", 112, 120) %>% 
  # pack_sub(., "RCT", 112, 119) %>% 
  # # pack_sub(., "Nonrandomized Studies of Interventions", 119, 119) %>% 
  # pack_sub(., "Prospective Cohort", 120, 120) %>% 
  # pack_top(., "Pediatric, Non-surgical", 121, 123) %>% 
  # pack_sub(., "RCT", 121, 121) %>%
  # pack_sub(., "Crossover", 122, 122) %>%
  # pack_sub(., "Prospective Cohort", 123, 123) %>% 
  footnote(general_title = "",
    general = c("Gen: general; Reg: regional; Sed: sedation; Hosp: hospital; Amb: ambulatory; GI: gastrointestinal; Ortho: orthopedic; Abdom: abdominal; ENT: otolaryngology (ear, nose, and throat); Gyn: gynecologic; Urol: urologic; Neuro: neurological; Hep: hepatic; Thor: thoracic; Oralmax: oral maxillofacial"),
    alphabet = c("Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."),
    footnote_as_chunk = FALSE) # %>% 

table_n <- tab_inc()
```

<br/>

###   <u>All Age Studies</u>

<br>

<font size = 4> Table `r table_n`. Characteristics of studies including patients of any age. </font>

```{r studyCharKableAllAges, echo = FALSE}
## (updated 2021/01/12 19:27) ---------------------------------------------
temp <- study_char_table %>%
  arrange(age, design, study) %>% 
  filter(age == "All ages") %>% 
  select(study, refid, age, design) %>% 
  group_by(age, design) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(end = cumsum(n),
         start = end - n + 1) %>% 
  select(age, design, start, end)

study_char_table %>%
  filter(age == "All ages") %>% 
  select(!c(refid, age, design)) %>% 
  kbl(booktabs = T, align = c("llllcccclc"), 
      # format = "latex",
      col.names = c("\\ \\ \\ \\ \\ \\ \\ Study", "Dates", "Country", " N ", "Pilot", 
                    "Setting", "Gen", "Reg", "Type of Surgery", "Registered")) %>%
  add_header_above(c(" " = 6, "Anesthesia" = 2, " " = 2), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>% 
  column_spec(2, width = "8em") %>% 
  column_spec(3, width = "5em") %>% 
  column_spec(4, width = "4em") %>% 
  column_spec(5, width = "4em") %>% 
  column_spec(6, width = "5em") %>% 
  column_spec(7, width = "3em") %>% 
  column_spec(8, width = "3em") %>% 
  column_spec(9, width = "15em") %>% 
  column_spec(10, width = "5em") %>% 
  # column_spec(2, width = "2em") %>% 
  pack_topnoind(., "RCT", 1, 4) %>% 
  pack_topnoind(., "Retrospective Cohort", 5, 5) %>% 
  footnote(general_title = "",
    general = "Gen: general; Reg: regional; Sed: sedation; Hosp: hospital; Ortho: orthopedic; ENT: otolaryngology (ear, nose, and throat).",
    alphabet = c("Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."),
    footnote_as_chunk = FALSE) # %>% 

table_n <- tab_inc()
```

<br/>

###   <u>Pediatric Studies</u>

<br>

<font size = 4> Table `r table_n`. Characteristics of studies including only pediatric patients. </font>

```{r studyCharKableAllPeds, echo = FALSE}
## (updated 2021/01/12 19:27) ---------------------------------------------
temp <- study_char_table %>%
  arrange(age, design, study) %>% 
  filter(age == "Pediatric") %>% 
  select(study, refid, age, design) %>% 
  group_by(age, design) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(end = cumsum(n),
         start = end - n + 1) %>% 
  select(age, design, start, end)

study_char_table %>%
  filter(age == "Pediatric") %>% 
  select(!c(refid, age, design)) %>% 
  kbl(booktabs = T, align = c("llllcccclc"), 
      # format = "latex",
      col.names = c("Study", "Dates", "Country", " N ", "Pilot", 
                    "Setting", "Gen", "Reg", "Type of Surgery", "Registered")) %>%
  add_header_above(c(" " = 6, "Anesthesia" = 2, " " = 2), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>% 
  column_spec(2, width = "8em") %>% 
  column_spec(3, width = "5em") %>% 
  column_spec(4, width = "4em") %>% 
  column_spec(5, width = "4em") %>% 
  column_spec(6, width = "5em") %>% 
  column_spec(7, width = "3em") %>% 
  column_spec(8, width = "3em") %>% 
  column_spec(9, width = "15em") %>% 
  column_spec(10, width = "5em") %>% 
  # column_spec(2, width = "2em") %>% 
  pack_topnoind(., "RCT", 1, 12) %>% 
  pack_topnoind(., "Prospective Cohort", 13, 16) %>% 
  pack_topnoind(., "Retrospective Cohort", 17, 17) %>% 
  footnote(general_title = "",
    general = c("Gen: general; Reg: regional; Sed: sedation; Hosp: hospital; Amb: ambulatory; Card: cardiac; GI: gastrointestinal; Ortho: orthopedic; Abdom: abdominal; ENT: otolaryngology (ear, nose, and throat); Urol: urologic; Oralmax: oral maxillofacial"),
    alphabet = c("Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."),
    footnote_as_chunk = FALSE) # %>% 

table_n <- tab_inc()
```

<br/>

### *Patient Characteristics*

###   <u>Adult Studies</u>

<br>

<font size = 4> Table `r table_n`. Patient characteristics in studies including only adults. </font>

```{r ptCharTableData, include = FALSE}
## ptCharTableData (updated 2022/01/15 10:08) ----------------------------
pt_char_table <- study_arm.dat %>%
  filter(refid %in% rev_refids) %>%
  group_by(refid) %>%
  summarize(
    N = sum(arm_n),
    wgt = arm_n / N,
    asa_1_all = round(sum(asa_1 * wgt, na.rm = FALSE)),
    asa_2_all = round(sum(asa_2 * wgt, na.rm = FALSE)),
    asa_3_all = round(sum(asa_3 * wgt, na.rm = FALSE)),
    asa_12_all = round(sum(asa_12 * wgt, na.rm = FALSE)),
    asa_123_all = round(sum(asa_123 * wgt, na.rm = FALSE)),
    asa_23_all = round(sum(asa_23 * wgt, na.rm = FALSE)),
    asa_34_all = round(sum(asa_34 * wgt, na.rm = FALSE)),
    age_mn_all = round(sum(age_mean * wgt, na.rm = FALSE)),
    age_md_all = round(sum(age_med * wgt, na.rm = FALSE)),
    sex_all = round(sum(female * wgt, na.rm = FALSE)),
    white_all = round(sum(white * wgt, na.rm = FALSE)),
    black_all = round(sum(black * wgt, na.rm = FALSE)),
    asian_all = round(sum(asian * wgt, na.rm = FALSE)),
    bmi_mn_all = round(sum(bmi_mean * wgt, na.rm = FALSE)),
    bmi_md_all = round(sum(bmi_med * wgt, na.rm = FALSE)),
    cardiac_all = round(sum(cardiac * wgt, na.rm = FALSE)),
    cancer_all = round(sum(cancer * wgt, na.rm = FALSE)),
    renal_all = round(sum(renal * wgt, na.rm = FALSE)),
    gi_all = round(sum(gi * wgt, na.rm = FALSE)),
    pulm_all = round(sum(pulm * wgt, na.rm = FALSE)),
    hepatic = round(sum(hepatic * wgt, na.rm = FALSE)),
    dm_all = round(sum(dm * wgt, na.rm = FALSE)),
    neuro_all = round(sum(neuro * wgt, na.rm = FALSE))
  ) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  remove_empty(which = "cols") %>%
  # categorize asa class
  mutate(
    asa_1 = ifelse(if_any(c(asa_1_all, asa_12_all, asa_123_all), ~ !is.na(.)), "\U00D7", NA),
    asa_2 = ifelse(if_any(c(asa_12_all, asa_2_all, asa_123_all, asa_23_all), ~ !is.na(.)), "\U00D7", NA),
    asa_3 = ifelse(if_any(c(asa_123_all, asa_3_all, asa_23_all, asa_34_all), ~ !is.na(.)), "\U00D7", NA),
    asa_4 = ifelse(if_any(c(asa_34_all), ~ !is.na(.)), "\U00D7", NA)
  ) %>%
  relocate(c(asa_1, asa_2, asa_3, asa_4), .after = asa_34_all) %>%
  mutate(across(c(cardiac_all:neuro_all), ~ bar_wn(.x, .x, color_1, 100)),
    across(c(white_all:asian_all), ~ bar_wn(.x, .x, color_2, 100)),
    sex_all = bar_wn(sex_all, sex_all, color_3, 100),
    age_sum = ifelse(is.na(age_mn_all) & !is.na(age_md_all), paste0("<u>", age_md_all, "</u>"), age_mn_all),
    bmi = ifelse(is.na(bmi_mn_all) & !is.na(bmi_md_all), paste0("<u>", bmi_md_all, "</u>"), bmi_mn_all)
  ) %>%
  relocate(bmi, .before = bmi_mn_all) %>%
  relocate(age_sum, .before = age_mn_all) %>%
  select(-c(asa_1_all:asa_34_all, wgt, bmi_mn_all, bmi_md_all, age_mn_all, age_md_all))

pt_char_table <- left_join(pt_char_table, study_char.dat[, c("refid", "age", "design", "study", "year")], by = "refid") %>% 
  relocate(c(age, design, study, year), .after = "refid") %>% 
  arrange(design, year)

```

```{r ptCharTableAdult}
## ptCharTableData (updated 2022/01/15 10:08)  ----------------------------
temp <- pt_char_table %>%
  arrange(age, design, study) %>% 
  filter(age == "Adult") %>% 
  select(study, refid, age, design) %>% 
  group_by(age, design) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(end = cumsum(n),
         start = end - n + 1) %>% 
  select(age, design, start, end)

pt_char_table %>% 
  filter(age == "Adult") %>% 
  select(-c(refid, year, age, design)) %>% 
  select(study:bmi, cardiac_all, renal_all, pulm_all, hepatic, dm_all, neuro_all) %>% 
    kbl(booktabs = T, align = c("llcccccllllcllllll"), escape = FALSE,
      col.names = c("Study", " N ", "1", "2", "3", "4", "M <u>Med</u>", "(%)", "W", "B", "A", "M <u>Med</u>", "Card", "Renal", "Pulm", "Hep", "DM", "Neur")) %>% 
  add_header_above(c(" " = 2, "ASA Class" = 4, "Age" = 1, "Female", "Race" = 3, "BMI" = 1, "Comorbidities (%)^a^" = 6), bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>% 
  column_spec(2, width = "3em") %>% 
  column_spec(3:6, width = "2em", popover = "ASA class (1 to 4)") %>% 
  column_spec(7, width = "4em", popover = "Age") %>% 
  column_spec(8, width = "4em", popover = "Female %") %>% 
  column_spec(9, width = "3em", popover = "White %") %>%
  column_spec(10, width = "3em", popover = "Black %") %>%
  column_spec(11, width = "3em", popover = "Asian %") %>%
  column_spec(12, width = "4em", popover = "BMI") %>% 
  column_spec(13, width = "3em", popover = "Cardiac %") %>%
  column_spec(14, width = "3em", popover = "Renal %") %>% 
  column_spec(15, width = "3em", popover = "Pulmonary %") %>% 
  column_spec(16, width = "3em", popover = "Hepatic %") %>% 
  column_spec(17, width = "3em", popover = "Diabetes %") %>% 
  column_spec(18, width = "3em", popover = "Nuerological %") %>% 
  pack_topnoind(., "RCT", 1, 105) %>% 
  pack_topnoind(., "Quasi-Experimental", 106, 106) %>% 
  pack_topnoind(., "Nonrandomized Studies of Interventions", 107, 114) %>% 
  pack_topnoind(., "Prospective Cohort", 115, 126) %>%
  pack_topnoind(., "Retrospective Cohort", 127, 136) %>% 
  footnote(general_title = "",
    general = c("M: mean; Med: median; Card: cardiac; Pulm: pulmonary; Hep: hepatic; DM: diabetes mellitus; Neuro: neurological: RCT: randomized controlled trial."),
    alphabet = c("Empty cells indicate no information in publication."),
    footnote_as_chunk = FALSE)  

table_n <- tab_inc()
```

<br/>

###   <u>All Age Studies</u>

<br>

<font size = 4> Table `r table_n`. Patient characteristics in studies including patients of any age. </font>

```{r ptCharTableAllAge}
## ptCharTableData (updated 2022/01/15 10:08)  ----------------------------
temp <- pt_char_table %>%
  arrange(age, design, study) %>% 
  filter(age == "All ages") %>% 
  select(study, refid, age, design) %>% 
  group_by(age, design) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(end = cumsum(n),
         start = end - n + 1) %>% 
  select(age, design, start, end)

pt_char_table %>% 
  filter(age == "All ages") %>% 
  select(-c(refid, year, age, design)) %>% 
  select(study:bmi, cardiac_all, renal_all, pulm_all, hepatic, dm_all, neuro_all) %>% 
    kbl(booktabs = T, align = c("llcccccllllcllllll"), escape = FALSE,
      col.names = c("Study", " N ", "1", "2", "3", "4", "M <u>Med</u>", "(%)", "W", "B", "A", "M <u>Med</u>", "Card", "Renal", "Pulm", "Hep", "DM", "Neur")) %>% 
  add_header_above(c(" " = 2, "ASA Class" = 4, "Age" = 1, "Female", "Race (%)" = 3, "BMI" = 1, "Comorbidities (%)^a^" = 6), bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1,   width = study_width) %>% 
  column_spec(2,   width = "3em") %>% 
  column_spec(3:6, width = "2em") %>% 
  column_spec(7,   width = "4em") %>% 
  column_spec(8,   width = "4em") %>% 
  column_spec(9,   width = "3em") %>% 
  column_spec(10,  width = "3em") %>% 
  column_spec(11,  width = "3em") %>% 
  column_spec(12,  width = "4em") %>% 
  column_spec(13,  width = "3em") %>% 
  column_spec(14,  width = "3em") %>% 
  column_spec(15,  width = "3em") %>% 
  column_spec(16,  width = "3em") %>% 
  column_spec(17,  width = "3em") %>% 
  column_spec(18,  width = "3em") %>% 
  pack_topnoind(., "RCT", 1, 4) %>% 
  pack_topnoind(., "Retrospective Cohort", 5, 5) %>% 
  footnote(general_title = "",
    general = c("M: mean; Med: median; Card: cardiac; Pulm: pulmonary; Hep: hepatic; DM: diabetes mellitus; Neuro: neurological: RCT: randomized controlled trial."),
    alphabet = c("Empty cells indicate no information in publication."),
    footnote_as_chunk = FALSE)  

table_n <- tab_inc()
```

<br/>

###   <u>Pediatric Studies</u>

<br>

<font size = 4> Table `r table_n`. Patient characteristics in studies including only pediatric patients. </font>

```{r ptCharTableAllPediatric}
## ptCharTableData (updated 2022/01/15 10:08)  ----------------------------
temp <- pt_char_table %>%
  arrange(age, design, study) %>% 
  filter(age == "Pediatric") %>% 
  select(study, refid, age, design) %>% 
  group_by(age, design) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(end = cumsum(n),
         start = end - n + 1) %>% 
  select(age, design, start, end)

pt_char_table %>%
  filter(age == "Pediatric") %>%
  select(-c(refid, year, age, design)) %>%
  select(study:bmi, cardiac_all, renal_all, pulm_all, hepatic, dm_all, neuro_all) %>%
  kbl(
    booktabs = T, align = c("llcccccllllcllllll"), escape = FALSE,
    col.names = c("Study", " N ", "1", "2", "3", "4", "M <u>Med</u>", "(%)", "W", "B", "A", "M <u>Med</u>", "Card", "Renal", "Pulm", "Hep", "DM", "Neur")
  ) %>%
  add_header_above(c(" " = 2, "ASA Class" = 4, "Age" = 1, "Female", "Race (%)" = 3, "BMI" = 1, "Comorbidities (%)^a^" = 6), bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "3em") %>%
  column_spec(3:6, width = "2em") %>%
  column_spec(7, width = "4em") %>%
  column_spec(8, width = "4em") %>%
  column_spec(9, width = "3em") %>%
  column_spec(10, width = "3em") %>%
  column_spec(11, width = "3em") %>%
  column_spec(12, width = "4em") %>%
  column_spec(13, width = "3em") %>%
  column_spec(14, width = "3em") %>%
  column_spec(15, width = "3em") %>%
  column_spec(16, width = "3em") %>%
  column_spec(17, width = "3em") %>%
  column_spec(18, width = "3em") %>%
  pack_topnoind(., "RCT", 1, 12) %>%
  pack_topnoind(., "Prospective Cohort", 13, 16) %>%
  pack_topnoind(., "Retrospective Cohort", 17, 17) %>%
  footnote(
    general_title = "",
    general = c("M: mean; Med: median; Card: cardiac; Pulm: pulmonary; Hep: hepatic; DM: diabetes mellitus; Neuro: neurological: RCT: randomized controlled trial."),
    alphabet = c("Empty cells indicate no information in publication."),
    footnote_as_chunk = FALSE
  )  

table_n <- tab_inc()
```

<br/>

# **Funding and Conflict of Interest**

<br/>

###   <u>Adult Studies</u>

<br>

<font size = 4> Table `r table_n`. Funding^a^ and reported conflict of interest in studies including only adults. </font>

```{r createFundingTable, include = FALSE}
## (updated 2021/01/12 09:28) createFundingTable --------------------------
study_fund_table <- study_char.dat %>%
  filter(refid %in% rev_refids) %>% 
  mutate(
    sponsor_desc = str_replace(sponsor_desc, "MSD", "Merck Sharp & Dohme Corp"),
    sponsor_desc = str_replace(sponsor_desc, "Merck & Co", "MSD"),
    sponsor_desc = str_replace(sponsor_desc, "Merck Sharp & Dohme Corp", "MSD"),
    sponsor_desc = str_replace(sponsor_desc, "Merck", "MSD"),
    sponsor_desc = firstup(sponsor_desc),
    # sponsor_desc = str_replace(sponsor_desc, "MSD", "Merck Sharp & Dohme"),
    auth_coi_desc = str_replace_all(auth_coi_desc, "MSD", "Merck Sharp & Dohme Corp"),
    auth_coi_desc = str_replace_all(auth_coi_desc, "Merck & Co", "Merck Sharp & Dohme Corp"),
    auth_coi_desc = str_replace_all(auth_coi_desc, "Merck Sharp & Dohme Corp", "MSD"),
    auth_coi_desc = str_replace_all(auth_coi_desc, "Merck", "MSD"),
    # auth_coi_desc = str_replace_all(auth_coi_desc, "MSD", "Merck Sharp & Dohme"),
    # sponsor_desc = str_to_title(sponsor_desc),
    auth_not_report = noquote(if_else(author_coi == "not_auth_rep", "\U00D7", "", "")),
    # auth_not_report = if_else(author_coi == "not_auth_rep", "&times", "", ""),
    auth_no_coi = noquote(if_else(author_coi == "none_auth_coi", "\U00D7", "", "")),
    auth_coi = noquote(if_else(author_coi == "author_coi", '<span style="color:red">\U00D7</span>', "", "")),
    registered = noquote(if_else(registered == "yes", "\U00D7", "", "")),
    public = noquote(if_else(funding == "public", "\U00D7", "", "")),
    pub_indus = noquote(if_else(funding == "pub_indus", '<span style="color:red">\U00D7</span>', "", "")),
    industry = noquote(if_else(funding == "industry", '<span style="color:red">\U00D7</span>', "", "")),
    none = noquote(if_else(funding == "none", "\U00D7", "", "")),
    not_reported = noquote(if_else(funding == "NR", "\U00D7", "", ""))) %>%
  arrange(age, design, year, study) %>%
  select(refid, study, age, design, public, pub_indus, industry, none, not_reported, sponsor_desc, auth_no_coi, auth_coi, auth_not_report, auth_coi_desc)

```

```{r fundingKable, echo = FALSE}
## (updated 2021/01/12 09:28) fundingKable --------------------------------
study_fund_table %>% 
  filter(age == "Adult") %>% 
  select(!c(refid, age, design)) %>% 
  kbl(booktabs = T, align = c("lccccclcccl"),
      col.names = c("Study", "Pub", '<span style="color:red">Pub/Ind</span>', '<span style="color:red">Ind</span>',  "None", "NR^a^", "Description", "No", '<span style="color:red">Yes</span>', "NR^a^", "Description"),
      escape = FALSE) %>%
  add_header_above(c(" " = 1, "Funding Source(s)" = 6, "Author Conflict of Interest" = 4), line = TRUE, bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "12em") %>% 
  column_spec(2:6, width = "4em") %>% 
  column_spec(7, width = "20em") %>% 
  column_spec(8:10, width = "4em") %>% 
  column_spec(11, width = "20em") %>% 
  pack_topnoind(., "RCT", 1, 105) %>% 
  pack_topnoind(., "Quasi-Experimental", 106, 106) %>% 
  pack_topnoind(., "Nonrandomized Studies of Interventions", 107, 114) %>% 
  pack_topnoind(., "Prospective Cohort", 115, 126) %>%
  pack_topnoind(., "Retrospective Cohort", 127, 136) %>% 
  footnote(general = "Pub: public, Ind: industry; NR: not reported; MSD: Merck, Sharp, and Dohme (funded 23 (22%) of RCTs and 26 (19%) of studies listed).",
          alphabet = c("Not reported meaning no mention in publication of funding source or author conflicts of interest."))
          # general_title = " ",
          # alphabet_title = " ",
          # footnote_as_chunk = T)

table_n <- tab_inc()

# merck studies
# study_fund_table %>% 
#   # filter(age == "Adult", design == "rct") %>% 
#   filter(age == "Adult") %>% 
#   mutate(
#     msd_fund = grepl("MSD|Merck", sponsor_desc)
#   ) %>% 
#   tabyl(msd_fund)
```

<br/>

###   <u>All Ages Studies</u>

<br>

<font size = 4> Table `r table_n`. Funding^a^ and reported conflict of interest in studies including patients of any age. </font>

```{r fundingKableAllAges, echo = FALSE}
## (updated 2021/01/12 09:28) fundingKable --------------------------------
study_fund_table %>% 
  filter(age == "All ages") %>% 
  select(!c(refid, age, design)) %>% 
  kbl(booktabs = T, align = c("lccccclcccl"),
      col.names = c("Study", "Pub", '<span style="color:red">Ind</span>',  '<span style="color:red">Pub/Ind</span>', "None", "NR^a^", "Description", "No", '<span style="color:red">Yes</span>', "NR^a^", "Description"),
      escape = FALSE) %>%
  add_header_above(c(" " = 1, "Funding Source(s)" = 6, "Author Conflict of Interest" = 4), line = TRUE, bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "12em") %>% 
  column_spec(2:6, width = "4em") %>% 
  column_spec(7, width = "20em") %>% 
  column_spec(8:10, width = "4em") %>% 
  column_spec(11, width = "20em") %>% 
  pack_topnoind(., "RCT", 1, 4) %>% 
  pack_topnoind(., "Retrospective Cohort", 5, 5) %>% 
  footnote(general = "Pub: public, Ind: industry; NR: not reported; MSD: Merck, Sharp, and Dohme.",
          alphabet = c("Not reported meaning no mention in publication of funding source or author conflicts of interest."))
          # general_title = " ",
          # alphabet_title = " ",
          # footnote_as_chunk = T)

table_n <- tab_inc()

```

<br/>

###   <u>Pediatric Studies</u>

<br>

<font size = 4> Table `r table_n`. Funding^a^ and reported conflict of interest in studies includingonly pediatric patients. </font>

<br/>

```{r fundingKablePediatric, echo = FALSE}
## (updated 2021/01/12 09:28) fundingKable --------------------------------
study_fund_table %>% 
  filter(age == "Pediatric") %>% 
  select(!c(refid, age, design)) %>% 
  kbl(booktabs = T, align = c("lccccclcccl"),
      col.names = c("Study", "Pub", '<span style="color:red">Ind</span>',  '<span style="color:red">Pub/Ind</span>', "None", "NR^a^", "Description", "No", '<span style="color:red">Yes</span>', "NR^a^", "Description"),
      escape = FALSE) %>%
  add_header_above(c(" " = 1, "Funding Source(s)" = 6, "Author Conflict of Interest" = 4), line = TRUE, bold = TRUE) %>% 
  row_spec(0, bold = TRUE) %>% 
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "12em") %>% 
  column_spec(2:6, width = "4em") %>% 
  column_spec(7, width = "20em") %>% 
  column_spec(8:10, width = "4em") %>% 
  column_spec(11, width = "20em") %>% 
  pack_topnoind(., "Prospective Cohort", 13, 16) %>% 
  pack_topnoind(., "Retrospective Cohort", 17, 17) %>% 
  footnote(general = "Pub: public, Ind: industry; NR: not reported; MSD: Merck, Sharp, and Dohme.",
          alphabet = c("Not reported meaning no mention in publication of funding source or author conflicts of interest."))
          # general_title = " ",
          # alphabet_title = " ",
          # footnote_as_chunk = T)

table_n <- tab_inc()

```

# **Risk of Bias**

<br/>

### *RCTs Clinical Outcomes*

<br>

<font size = 4> Figure `r figure_n`. Summary risk of bias appraisal for included RCTs reporting RNMB. </font>

<img src="assets/reversal_rnmb_rob_clin_out.svg" style="width:750px;" align="left"/>

<br clear="all" />

```{r}
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Individual study risk of bias appraisal for reporting RNMB. </font>

<img src="assets/reversal_rnmb_clin_out_traffic.svg" style="width:650px;" align="left"/>

```{r}
figure_n <- fig_inc()
```

<br clear="all" />

<br clear="all" />

### *Nonrandomized Studies of Interventions*

<br>

<font size = 4> Figure `r figure_n`. Summary risk of bias appraisal for included nonrandomized studies [ROBINS-I](https://www.bmj.com/content/355/bmj.i4919). </font>

<img src="assets/reversal_robins_summary.svg" style="width:750px;" align="left"/>

<br clear="all" />

```{r}
figure_n <- fig_inc()
```

<br/>

<font size = 4> Figure `r figure_n`. Individual study risk of bias appraisal for nonrandomized studies. </font>

<img src="assets/reversal_robins_traffic.svg" style="width:650px;" align="left"/>

```{r}
figure_n <- fig_inc()
```

<br clear="all" />

<hr style="height:2px;border-width:0;color:gray;background-color:gray">

<br>

# References {#references}

<a id="references"></a>


























