---
title: "Study Characteristics"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
  latex_engine: xelatex
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    font: Source Sans Pro
    theme: cosmo
    anchor_sections: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
    toc_depth: 3
    linkcolor: blue
bibliography: bib/kq4.bib
csl: jama.csl
link-citations: yes
workflowr:
  suppress_report: no
---

```{=html}
<style type="text/css">
  body{
  font-size: 9.5pt;
  font-family: Source Sans Pro;
}

.caption {
  font-size: 15px;
}

.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  color: #090909;
  background-color: #0909093d;
}

.lightable-classic.lightable-hover tbody tr:hover {
    background-color: #c5d4e4;
}
.btn-xs, .btn-group-xs>.btn { 
display: none; 
}

.btn-default {
display: none !important; 
}

.popover-title {
      font-size: 12px;
  }

.popover-content {
      font-size: 12px;
  }
  
.popover-content {
    background-color: white;
    <!-- color: #FFFFFF; -->
    padding: 2px;
  }

</style>

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover({html: true, placement: top});
});
</script>
```

```{r setup, include = FALSE}
## setup ---------------------------------------------- (2022-02-14 16:17) @----
knitr::opts_chunk$set(echo = TRUE)
source("code/readfiles_nmb_102721.R")
```
```{r data}
## data/refids ---------------------------------------- (2022-02-15 10:28) @
## refids --------------------------------------------- (2022-02-21 10:31) @----
# rev refids volatile study_arm.dat 
rev_refids <- study_char.dat %>% 
  filter(rev_agt == "rev_agt") %>% 
  pull(refid) %>% 
  unique()

neo_dosing_refids <- study_arm.dat %>% 
  filter(subgroup == "neo_dosing") %>% 
  pull(refid) %>% 
  unique()

sug_dosing_refids <- study_arm.dat %>% 
  filter(subgroup == "sug_dosing") %>% 
  pull(refid) %>% 
  unique()

# note that subgroup assigned by arm
subgroup_refids <- study_arm.dat %>% 
  filter(subgroup != "none") %>% 
  pull(refid) %>% 
  unique()

# from latest distiller 2022/02/21 08:13 n=26
rnmb_dist_refids <- dichot.dat %>%
  filter(refid %in% rev_refids) %>%
  filter(!is.na(rnmb), !refid %in% subgroup_refids) %>%
  # remove single arm studies; 2022/02/21 08:52 will be Yip 2304, Alenezu 3574
  group_by(refid) %>%
  filter(n() >= 2) %>%
  ungroup() %>%
  select(refid) %>%
  distinct() %>%
  pull()

## from spreadsheet ----------------------------------- (2022-02-22 14:32) @----
# rcts only from spreadsheet 2022/02/21 08:04 n=21 (checked same in excel sheet) 
rnmb_ma.dat <- suppressMessages(read_csv("data/rnmb_read_011322.csv")) %>% 
  clean_names() %>% 
  filter(!is.na(arm)) %>% 
  fill(refid, study) %>% 
  remove_empty(which = "cols") %>% 
  mutate(
    study_orig = study,
    study = str_extract(study, "\\w*.{0,1}\\w* \\d{4}"),
    mg_kg = ifelse(is.na(mg_kg) & !is.na(mg), paste0("<u>", mg, "</u>"), mg_kg),
    refid = suppressWarnings(as.numeric(refid))
  ) %>% 
  select(-mg) # milligram can delete

## data char, arm, dichot ----------------------------- (2022-02-21 10:32) @----
study_char_rev.dat <- study_char.dat %>%
  filter(refid %in% rev_refids) 

study_arm_rev.dat <- study_arm.dat %>%
  filter(refid %in% rev_refids) %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    ),
    arm = case_when(
      revagent %in% c("neo") ~ "Neo",
      revagent %in% c("sug") ~ "Sug",
      str_detect(study_arm_k, "pont") ~ "Spont",
      revagent %in% c("other_agent") ~ revother,
      TRUE ~ "Other"
    ),
    arm = ifelse(str_detect(arm, "lacebo|saline"), "Plac", arm),
    arm = ifelse(str_detect(arm, "yridostigmine"), "Pyrid", arm),
    arm = factor(arm, levels = c("Sug", "Neo", "Plac", "Spont", "Pyrid", "Other"), ordered = TRUE),
    volatile = if_any(c(an_isoflurane, an_sevoflurane, an_desf, an_hal), ~ !is.na(.))
  ) %>%
  select(refid, arm_id, study, year, design, arm_n, arm, age, study_arm_k, subgroup, depth, starts_with("depth_rev_"), anesth:anes_agent_spec, neo_dose, neo_max_dose, neo_dose_unit, sug_dose, sug_dose_max, nmbagent, gen_type, revtim, revtim_comment, mon_cat, mon_cat_f, asa_1:asa_123)

dichot_rev.dat <- dichot.dat %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    )
  )

# study_arm_rev.dat %>% tabyl(depth)

## comparators ---------------------------------------- (2022-02-21 10:32) @----
comparators <- study_arm_rev.dat %>% 
  # filter(design == "rct") %>% 
  arrange(year) %>% 
  select(refid, study, design, subgroup, arm_id, arm, age) %>% 
  pivot_wider(id_cols = c(refid, study, design, subgroup), names_from = arm, values_from = arm_id, values_fn = list) %>% 
  select(refid:design, subgroup, Sug, Neo, Plac, Spont, Pyrid, Other) %>% 
  mutate(across(Sug:Other, ~ as.numeric(. != "NULL"))) %>% 
  mutate(across(Sug:Other, ~ as.character(.))) %>% 
  mutate(across(Sug:Other, ~ ifelse(. == "1", cur_column(), ""))) %>% 
  mutate(compare = str_c(Sug, Neo, Plac, Spont, Pyrid, sep = ":"),
         compare = str_replace_all(compare, ":{2,3}", ":"),
         compare = str_replace(compare, "^:", ""),
         compare = str_replace_all(compare, ":{1,3}$", ""))

# subgroups with comparators
comp_subgroup <- comparators %>% 
  filter(subgroup != "none", str_detect(compare, ":")) 

rct_nosub_comp <- comparators %>% 
  filter(design == "rct", refid %notin% subgroup_refids) 

## comparators by arm --------------------------------- (2022-02-21 13:33) @----
comp_rct_arm <- study_arm_rev.dat %>% 
  mutate(study = case_when(
    study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
    study == "Wu 2014" & arm_n >= 50 ~"Wu 2014 (Chinese)",
    TRUE ~ study)) %>% 
  filter(design == "rct", refid %notin% subgroup_refids) %>% 
  arrange(year) %>% 
  select(refid, study, design, subgroup, arm_id, arm, arm_n, age) %>% 
  mutate(event_placeholder = 1)

```

\newpage 

## Randomized (adults)

### Trial Characteristics 

<br/>

<font size = 4> Table `r table_n`. Characteristics of randomized controlled trials. </font>

```{r studyCharRev}
## studyCharRev --------------------------------------- (2022-03-07 20:32) @----
study_char_table_rev <- study_char_rev.dat %>%
  filter(
    design %in% c("rct", "crossover"),
    age == "Adult",
    refid %in% rev_refids,
  ) %>%
  mutate(
    dates = str_c(date_start, "-", date_end),
    country = countrycode::countryname(country, destination = "un.name.en"),
    country = ifelse(grepl("United States", country), "United States", country),
    country = ifelse(grepl("United Kingdom", country), "United Kingdom", country),
    country = ifelse(grepl("Republic of Korea", country), "South Korea", country),
    country = ifelse(grepl("Iran", country), "Iran", country),
    eu = countrycode::countryname(country, destination = "eu28"),
    un = countrycode::countryname(country, destination = "un.region.name"),
    asia = un == "Asia",
    eu = eu == "EU",
    afr = un == "Africa",
    us = grepl("United States", country),
    ca = grepl("Canada", country),
    sa = grepl("Brazil", country),
    noneu = grepl("Bosnia|Kosovo", country),
    low_r = if_else(non_vh_hdi == "yes", 1, 0, missing = 0),
    pilot = if_else(pilot == "yes", 1, 0, missing = 0),
    ambulatory = !is.na(ambulatory),
    one_center = centers == 1,
    multi_center = centers > 1,
    general = !is.na(general),
    regional = !is.na(regional),
    sedation = !is.na(sedation),
    non_vh_hdi = ifelse(is.na(non_vh_hdi), 0, 1),
    fund_ind = funding == "industry",
    fund_pubind = funding == "pub_indus",
    fund_pub = funding == "public",
    fund_nr = funding == "NR",
    registered = if_else(registered == "yes", TRUE, FALSE, missing = FALSE),
  ) %>% 
  select(refid, study, eu, un, country, asia, eu, us, ca, sa, noneu, afr, low_r, non_vh_hdi, pilot, ambulatory, one_center, multi_center, general, regional, sedation, starts_with("fund_"), registered, n_enrolled, arms) 
  
## countries ------------------------------------------ (2022-03-09 07:23) @----
countries <- study_char_table_rev %>% 
  tabyl(country) %>% 
  arrange(desc(n)) %>% 
  mutate(
  n_per = n_percent1(n, percent * 100),
  characteristic = paste0("  ", country)
  ) %>% 
  select(characteristic, n_per)

## anesthetic ----------------------------------------- (2022-03-09 07:23) @----
anesthetic <- study_arm.dat %>% 
    filter(
    design %in% c("rct", "crossover"),
    age == "Adult",
    refid %in% rev_refids) %>% 
  group_by(refid) %>% 
  slice(1) %>% 
  ungroup() %>% 
  mutate(
    volatile = if_any(c(an_isoflurane, an_sevoflurane, an_desf, an_hal), ~ !is.na(.x)),
    tiva = ifelse(str_detect(gen_type, "tiva"), TRUE, FALSE)
  ) %>% 
  select(refid, volatile, tiva)

## table_rev ------------------------------------------ (2022-03-09 07:23) @----
table_rev <- study_char_table_rev %>% 
  left_join(., anesthetic, by = "refid") %>% 
  summarize(
    "Number of Trials" = n(),
    "Patients Enrolled (N)" = " ",
    "  Mean" = round(mean(n_enrolled), 1),
    "  Median" = median(n_enrolled),
    "  Range" = paste0("(", min(n_enrolled), "-", max(n_enrolled), ")"),
    "Arms" = " ",
    "  Two" = sum(arms == 2, na.rm = TRUE),
    "  Multi" = sum(arms > 2, na.rm = TRUE),
    "  Mean " = round(mean(arms, na.rm = TRUE), 1),
    "  Median " = round(median(arms, na.rm = TRUE), 1),
    "  Range " = paste0("(", min(arms, na.rm = TRUE), "-", max(arms, na.rm = TRUE), ")"),
    "Pilot Study" = n_per_tf(pilot),
    "Ambulatory" = n_per_tf(ambulatory),
    "Centers" = " ",
    "  Single Center" = n_per_tf(one_center),
    "  Multicenter" = n_per_tf(multi_center),
    # "Anesthesia" = " ",
    "Volatile Anestheic" = n_per_tf(volatile),
    # "  TIVA" = n_per_tf(tiva),
    # "  Sedation" = n_per_tf(sedation),
    "Country" = " ",
    "Non-very-high HDI Countryª" = n_per_tf(low_r),
    # expression(paste("Non-very-high HDI"^"a")) = n_per_tf(low_r),
    "Funding" = " ",
    "  Industry" = n_per_tf(fund_ind),
    "  Public/Industry" = n_per_tf(fund_pubind),
    "  Public" = n_per_tf(fund_pub),
    "  Not Reported" = n_per_tf(fund_nr),
    "Registered" = n_per_tf(registered),
  ) %>%
  t() %>% 
  data.frame() %>% 
  rename(n_per = ".") %>% 
  mutate(
  n = str_extract(n_per, "^\\d{1,2}"),
  per = str_extract(n_per, "\\(\\d{1,2}\\.\\d\\)")) %>% 
  rownames_to_column(var = "characteristic") %>% 
  select(characteristic, n_per) %>% 
  remove_rownames()

table_rev <- table_rev %>% 
  add_row(., countries, .after = 18)

table_rev %>%
  kbl(
    booktabs = T, align = c("lc"), escape = FALSE, # format = "latex",
    col.names = c("Characteristic", "Result")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "8em") %>%
  # row_spec(., 46, italic = TRUE) %>% 
  footnote(
    # general = "RCT: randomized controlled trial.",
    alphabet = c(
      "Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."
    ),
    general_title = "",
    footnote_as_chunk = FALSE
  )

# write_csv(study_char_table_rev, "/Users/mgrant/Desktop/study_char_table_rev.csv", na = "")
table_n <- tab_inc()
```

<br/>

### Patient Charcteristics

<br/>

<font size = 4> Table `r table_n`. Patient characteristics in randomized controlled trials. </font>

```{r ptCharRev}
## (updated 2021/07/21 08:26) surgery type --------------------------------
surg <- study_char_rev.dat %>%
  filter(
    design %in% c("rct", "crossover"),
    age == "Adult",
    refid %in% rev_refids,
  ) %>%
  mutate(
    across(surg_various:surg_other, ~ str_replace(.x, "surg_", "")),
    across(surg_various:surg_other, ~ str_c(.x, ", ")),
    across(surg_various:surg_other, ~ firstup(.x)),
    across(surg_various:surg_other, ~ replace_na(.x, "")),
    surg_list = ifelse(grepl("abdom", surg_list), "Abdominal, ", ""),
    surgs = str_c(surg_various, surg_car, surg_cr, surg_gyn, surg_gi, surg_gen, surg_headneck, surg_hep, surg_neuro, surg_opth, surg_oralmax, surg_ortho, surg_otolar, surg_plastic, surg_thor, surg_urol, surg_other, surg_list),
    surgs = str_replace(surgs, "Otolar", "ENT"),
    surgs = str_replace(surgs, "Headneck", "ENT"),
    surgs = str_sub(surgs, 1, nchar(surgs) - 2),
    surgs = ifelse(str_count(surgs, ",") > 2, "Various", surgs)
    ) %>%
  select(refid, surgs) %>% 
  tabyl(surgs) %>% 
  arrange(desc(percent)) %>% 
  rename(per = percent) %>% 
  mutate(per = paste0( "(", format(round(100*per, 1), nsmall = 1), ")"),
         per = str_replace(per, " ", ""),
         n = as.character(n),
         n_per = paste(n, per)) %>% 
  select(surgs, n_per) %>% 
  rename(result = n_per, characteristic = surgs) %>% 
  remove_rownames() %>% 
  mutate(
    characteristic = str_replace(characteristic, "Gi", "GI"),
    characteristic = str_replace(characteristic, "Cr", "CR"),
    characteristic = ifelse(characteristic == "Various", "Various (3 or more)", characteristic),
    characteristic = paste0("  ", characteristic),
  )

## (updated 2021/07/21 16:25) patients ------------------------------------
pt_char_table_rev <- study_arm.dat %>%
  filter(
    design %in% c("rct", "crossover"),
    age == "Adult",
    refid %in% rev_refids) %>% 
  group_by(refid) %>%
  summarize(
    N = sum(arm_n),
    wgt = arm_n / N,
    asa_1_all = round(sum(asa_1 * wgt, na.rm = FALSE)),
    asa_2_all = round(sum(asa_2 * wgt, na.rm = FALSE)),
    asa_3_all = round(sum(asa_3 * wgt, na.rm = FALSE)),
    asa_12_all = round(sum(asa_12 * wgt, na.rm = FALSE)),
    asa_123_all = round(sum(asa_123 * wgt, na.rm = FALSE)),
    asa_23_all = round(sum(asa_23 * wgt, na.rm = FALSE)),
    asa_34_all = round(sum(asa_34 * wgt, na.rm = FALSE)),
    age_mn_all = round(sum(age_mean * wgt, na.rm = FALSE)),
    age_md_all = round(sum(age_med * wgt, na.rm = FALSE)),
    sex_all = round(sum(female * wgt, na.rm = FALSE)),
    white_all = round(sum(white * wgt, na.rm = FALSE)),
    black_all = round(sum(black * wgt, na.rm = FALSE)),
    asian_all = round(sum(asian * wgt, na.rm = FALSE)),
    bmi_mn_all = round(sum(bmi_mean * wgt, na.rm = FALSE)),
    bmi_md_all = round(sum(bmi_med * wgt, na.rm = FALSE)),
    dm_mn_all = round(sum(dm * wgt, na.rm = FALSE)),
    neuro_all = round(sum(neuro * wgt, na.rm = FALSE))) %>%
  filter(row_number() == 1) %>%
  ungroup() %>% 
  rename_with(~ str_replace(., "_all", "")) %>% 
  mutate(across(asa_1:asa_34, ~ replace(., !is.na(.), "Y")),
         across(asa_1:asa_34, ~ replace(., is.na(.),  "-")),
         ) %>% 
  unite(., col = "asa", asa_1:asa_34, sep = "", remove = FALSE) %>% 
  mutate(
    age = case_when(
      !is.na(age_mn) ~ age_mn,
      !is.na(age_md) ~ age_md,
    ),
    bmi = case_when(
      !is.na(bmi_mn) ~ bmi_mn,
      !is.na(bmi_md) ~ bmi_md,
    ),
  ) %>%
  summarise(
    "Age (average of mean or med, range)" = paste0(round(sum(age/(n() - sum(is.na(age_mn) & is.na(age_md))), na.rm = TRUE), 1), " (", min(age, na.rm = TRUE), "-", max(age, na.rm = TRUE), ")"),
    "Female (%, range)" = paste0(round(sum(sex, na.rm = TRUE)/(n() - sum(is.na(sex))), 1), " (", min(sex, na.rm = TRUE), "-", max(sex, na.rm = TRUE), ")"),
    "ASA Class (%)" = " ",
    "  I-II" =   round(100 * mean(str_count(asa, "Y------|YY-----|---Y---")), 1),
    "  I-III" =  round(100 * mean(str_count(asa, "----Y--|--Y----|-YY----|Y----Y-|--YY---|YYY----")), 1),
    "  NR"     = round(100*mean(asa == "-------"), 1),
    "BMI (average of mean or med, range)" = paste0(round(sum(bmi/(n() - sum(is.na(bmi_mn) & is.na(bmi_md))), na.rm = TRUE), 1), " (", min(bmi, na.rm = TRUE), "-", max(bmi, na.rm = TRUE), ")"),
    "BMI (mean or med ≥ 30), (%)" = paste0("(", round(sum(bmi >= 30, na.rm = TRUE) / n() * 100, 1), ")"),
    # "DM" = " ",
    # "  Any (studies)" = sum(dm_mn > 0, na.rm = TRUE),
    # "    % pts, (range)" = paste0("(", min(dm_mn[dm_mn != 0], na.rm = TRUE), "-", max(dm_mn, na.rm = TRUE), ")")
  ) %>% 
t() %>% 
  data.frame() %>% 
  rownames_to_column(var = "characteristic") %>% 
  rename(result = ".") %>% 
  remove_rownames() %>% 
  add_row(characteristic = "Surgery, N (%)", result = "") %>% 
  # add surgery type
  bind_rows(surg)

pt_char_table_rev %>% 
  kbl(
    booktabs = T, align = c("lc"), escape = FALSE, # format = "latex",
    col.names = c("Characteristic", "Result")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "8em") 
  # row_spec(., 46, italic = TRUE) %>% 
  # footnote(
  #   general = "RCT: randomized controlled trial.",
  #   alphabet = c(" "),
  #   general_title = "",
  #   footnote_as_chunk = FALSE
  # )

# write_csv(pt_char_table_rev, "/Users/mgrant/Desktop/pt_char_table_rev.csv", na = "")

table_n <- tab_inc()

```

<br/><br/>

## Nonrandomized (adults)

### Study Characteristics 

<br/>

<font size = 4> Table `r table_n`. Characteristics of nonrandomized studies. </font>

```{r studyCharRevNrsi}
## studyCharRev --------------------------------------- (2022-03-07 20:32) @----
study_char_table_rev <- study_char_rev.dat %>%
  filter(
    !design %in% c("rct", "crossover"),
    age == "Adult",
    refid %in% rev_refids,
  ) %>%
  mutate(
    dates = str_c(date_start, "-", date_end),
    country = countrycode::countryname(country, destination = "un.name.en"),
    country = ifelse(grepl("United States", country), "United States", country),
    country = ifelse(grepl("United Kingdom", country), "United Kingdom", country),
    country = ifelse(grepl("Republic of Korea", country), "South Korea", country),
    country = ifelse(grepl("Iran", country), "Iran", country),
    eu = countrycode::countryname(country, destination = "eu28"),
    un = countrycode::countryname(country, destination = "un.region.name"),
    asia = un == "Asia",
    eu = eu == "EU",
    afr = un == "Africa",
    us = grepl("United States", country),
    ca = grepl("Canada", country),
    sa = grepl("Brazil", country),
    noneu = grepl("Bosnia|Kosovo", country),
    low_r = if_else(non_vh_hdi == "yes", 1, 0, missing = 0),
    pilot = if_else(pilot == "yes", 1, 0, missing = 0),
    ambulatory = !is.na(ambulatory),
    one_center = centers == 1,
    multi_center = centers > 1,
    general = !is.na(general),
    regional = !is.na(regional),
    sedation = !is.na(sedation),
    non_vh_hdi = ifelse(is.na(non_vh_hdi), 0, 1),
    fund_ind = funding == "industry",
    fund_pubind = funding == "pub_indus",
    fund_pub = funding == "public",
    fund_nr = funding == "NR",
    registered = if_else(registered == "yes", TRUE, FALSE, missing = FALSE),
  ) %>% 
  select(refid, study, eu, un, country, asia, eu, us, ca, sa, noneu, afr, low_r, non_vh_hdi, pilot, ambulatory, one_center, multi_center, general, regional, sedation, starts_with("fund_"), registered, n_enrolled, arms) 
  
## countries ------------------------------------------ (2022-03-09 07:23) @----
countries <- study_char_table_rev %>% 
  tabyl(country) %>% 
  arrange(desc(n)) %>% 
  mutate(
  n_per = n_percent1(n, percent * 100),
  characteristic = paste0("  ", country)
  ) %>% 
  select(characteristic, n_per)

## anesthetic ----------------------------------------- (2022-03-09 07:23) @----
anesthetic <- study_arm.dat %>% 
    filter(
    !design %in% c("rct", "crossover"),
    age == "Adult",
    refid %in% rev_refids) %>% 
  group_by(refid) %>% 
  slice(1) %>% 
  ungroup() %>% 
  mutate(
    volatile = if_any(c(an_isoflurane, an_sevoflurane, an_desf, an_hal), ~ !is.na(.x)),
    tiva = ifelse(str_detect(gen_type, "tiva"), TRUE, FALSE)
  ) %>% 
  select(refid, volatile, tiva)

## table_rev ------------------------------------------ (2022-03-09 07:23) @----
table_rev <- study_char_table_rev %>% 
  left_join(., anesthetic, by = "refid") %>% 
  summarize(
    "Number of Studies" = n(),
    "Patients Enrolled (N)" = " ",
    "  Mean" = round(mean(n_enrolled), 1),
    "  Median" = median(n_enrolled),
    "  Range" = paste0("(", min(n_enrolled), "-", max(n_enrolled), ")"),
    "Arms" = " ",
    "  Two" = sum(arms == 2, na.rm = TRUE),
    "  Multi" = sum(arms > 2, na.rm = TRUE),
    "  Mean " = round(mean(arms, na.rm = TRUE), 1),
    "  Median " = round(median(arms, na.rm = TRUE), 1),
    "  Range " = paste0("(", min(arms, na.rm = TRUE), "-", max(arms, na.rm = TRUE), ")"),
    "Pilot Study" = n_per_tf(pilot),
    "Ambulatory" = n_per_tf(ambulatory),
    "Centers" = " ",
    "  Single Center" = n_per_tfna(one_center),
    "  Multicenter" = n_per_tfna(multi_center),
    # "Anesthesia" = " ",
    "Volatile Anestheic" = n_per_tf(volatile),
    # "  TIVA" = n_per_tf(tiva),
    # "  Sedation" = n_per_tf(sedation),
    "Country" = " ",
    "Non-very-high HDI Countryª" = n_per_tf(low_r),
    # expression(paste("Non-very-high HDI"^"a")) = n_per_tf(low_r),
    "Funding" = " ",
    "  Industry" = n_per_tf(fund_ind),
    "  Public/Industry" = n_per_tf(fund_pubind),
    "  Public" = n_per_tf(fund_pub),
    "  Not Reported" = n_per_tf(fund_nr),
    "Registered" = n_per_tf(registered),
  ) %>%
  t() %>% 
  data.frame() %>% 
  rename(n_per = ".") %>% 
  mutate(
  n = str_extract(n_per, "^\\d{1,2}"),
  per = str_extract(n_per, "\\(\\d{1,2}\\.\\d\\)")) %>% 
  rownames_to_column(var = "characteristic") %>% 
  select(characteristic, n_per) %>% 
  remove_rownames()

table_rev <- table_rev %>% 
  add_row(., countries, .after = 18)

table_rev %>%
  kbl(
    booktabs = T, align = c("lc"), escape = FALSE, # format = "latex",
    col.names = c("Characteristic", "Result")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "8em") %>%
  # row_spec(., 46, italic = TRUE) %>% 
  footnote(
    # general = "RCT: randomized controlled trial.",
    alphabet = c(
      "Non very high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."
    ),
    general_title = "",
    footnote_as_chunk = FALSE
  )

# write_csv(study_char_table_rev, "/Users/mgrant/Desktop/study_char_table_rev.csv", na = "")
table_n <- tab_inc()
```

<br/>

### Patient Charcteristics

<br/>

<font size = 4> Table `r table_n`. Patient characteristics in randomized studies. </font>

```{r ptCharRevNrsi}
## (updated 2021/07/21 08:26) surgery type --------------------------------
surg <- study_char_rev.dat %>%
  filter(
    !design %in% c("rct", "crossover"),
    age == "Adult",
    refid %in% rev_refids,
  ) %>%
  mutate(
    across(surg_various:surg_other, ~ str_replace(.x, "surg_", "")),
    across(surg_various:surg_other, ~ str_c(.x, ", ")),
    across(surg_various:surg_other, ~ firstup(.x)),
    across(surg_various:surg_other, ~ replace_na(.x, "")),
    surg_list = ifelse(grepl("abdom", surg_list), "Abdominal, ", ""),
    surgs = str_c(surg_various, surg_car, surg_cr, surg_gyn, surg_gi, surg_gen, surg_headneck, surg_hep, surg_neuro, surg_opth, surg_oralmax, surg_ortho, surg_otolar, surg_plastic, surg_thor, surg_urol, surg_other, surg_list),
    surgs = str_replace(surgs, "Otolar", "ENT"),
    surgs = str_replace(surgs, "Headneck", "ENT"),
    surgs = str_sub(surgs, 1, nchar(surgs) - 2),
    surgs = ifelse(str_count(surgs, ",") > 2, "Various", surgs)
    ) %>%
  select(refid, surgs) %>% 
  tabyl(surgs) %>% 
  arrange(desc(percent)) %>% 
  rename(per = percent) %>% 
  mutate(per = paste0( "(", format(round(100*per, 1), nsmall = 1), ")"),
         per = str_replace(per, " ", ""),
         n = as.character(n),
         n_per = paste(n, per)) %>% 
  select(surgs, n_per) %>% 
  rename(result = n_per, characteristic = surgs) %>% 
  remove_rownames() %>% 
  mutate(
    characteristic = str_replace(characteristic, "Gi", "GI"),
    characteristic = str_replace(characteristic, "Cr", "CR"),
    characteristic = ifelse(characteristic == "Various", "Various (3 or more)", characteristic),
    characteristic = paste0("  ", characteristic),
  )

## (updated 2021/07/21 16:25) patients ------------------------------------
pt_char_table_rev <- study_arm.dat %>%
  filter(
    !design %in% c("rct", "crossover"),
    age == "Adult",
    refid %in% rev_refids) %>% 
  group_by(refid) %>%
  summarize(
    N = sum(arm_n),
    wgt = arm_n / N,
    asa_1_all = round(sum(asa_1 * wgt, na.rm = FALSE)),
    asa_2_all = round(sum(asa_2 * wgt, na.rm = FALSE)),
    asa_3_all = round(sum(asa_3 * wgt, na.rm = FALSE)),
    asa_12_all = round(sum(asa_12 * wgt, na.rm = FALSE)),
    asa_123_all = round(sum(asa_123 * wgt, na.rm = FALSE)),
    asa_23_all = round(sum(asa_23 * wgt, na.rm = FALSE)),
    asa_34_all = round(sum(asa_34 * wgt, na.rm = FALSE)),
    age_mn_all = round(sum(age_mean * wgt, na.rm = FALSE)),
    age_md_all = round(sum(age_med * wgt, na.rm = FALSE)),
    sex_all = round(sum(female * wgt, na.rm = FALSE)),
    white_all = round(sum(white * wgt, na.rm = FALSE)),
    black_all = round(sum(black * wgt, na.rm = FALSE)),
    asian_all = round(sum(asian * wgt, na.rm = FALSE)),
    bmi_mn_all = round(sum(bmi_mean * wgt, na.rm = FALSE)),
    bmi_md_all = round(sum(bmi_med * wgt, na.rm = FALSE)),
    dm_mn_all = round(sum(dm * wgt, na.rm = FALSE)),
    neuro_all = round(sum(neuro * wgt, na.rm = FALSE))) %>%
  filter(row_number() == 1) %>%
  ungroup() %>% 
  rename_with(~ str_replace(., "_all", "")) %>% 
  mutate(across(asa_1:asa_34, ~ replace(., !is.na(.), "Y")),
         across(asa_1:asa_34, ~ replace(., is.na(.),  "-")),
         ) %>% 
  unite(., col = "asa", asa_1:asa_34, sep = "", remove = FALSE) %>% 
  mutate(
    age = case_when(
      !is.na(age_mn) ~ age_mn,
      !is.na(age_md) ~ age_md,
    ),
    bmi = case_when(
      !is.na(bmi_mn) ~ bmi_mn,
      !is.na(bmi_md) ~ bmi_md,
    ),
  ) %>%
  summarise(
    "Age (average of mean or med, range)" = paste0(round(sum(age/(n() - sum(is.na(age_mn) & is.na(age_md))), na.rm = TRUE), 1), " (", min(age, na.rm = TRUE), "-", max(age, na.rm = TRUE), ")"),
    "Female (%, range)" = paste0(round(sum(sex, na.rm = TRUE)/(n() - sum(is.na(sex))), 1), " (", min(sex, na.rm = TRUE), "-", max(sex, na.rm = TRUE), ")"),
    "ASA Class (%)" = " ",
    "  I-II" =   round(100 * mean(str_count(asa, "Y------|YY-----|---Y---")), 1),
    "  I-III" =  round(100 * mean(str_count(asa, "----Y--|--Y----|-YY----|Y----Y-|--YY---|YYY----")), 1),
    "  NR"     = round(100*mean(asa == "-------"), 1),
    "BMI (average of mean or med, range)" = paste0(round(sum(bmi/(n() - sum(is.na(bmi_mn) & is.na(bmi_md))), na.rm = TRUE), 1), " (", min(bmi, na.rm = TRUE), "-", max(bmi, na.rm = TRUE), ")"),
    "BMI (mean or med ≥ 30), (%)" = paste0("(", round(sum(bmi >= 30, na.rm = TRUE) / n() * 100, 1), ")"),
    # "DM" = " ",
    # "  Any (studies)" = sum(dm_mn > 0, na.rm = TRUE),
    # "    % pts, (range)" = paste0("(", min(dm_mn[dm_mn != 0], na.rm = TRUE), "-", max(dm_mn, na.rm = TRUE), ")")
  ) %>% 
t() %>% 
  data.frame() %>% 
  rownames_to_column(var = "characteristic") %>% 
  rename(result = ".") %>% 
  remove_rownames() %>% 
  add_row(characteristic = "Surgery, N (%)", result = "") %>% 
  # add surgery type
  bind_rows(surg)

pt_char_table_rev %>% 
  kbl(
    booktabs = T, align = c("lc"), escape = FALSE, # format = "latex",
    col.names = c("Characteristic", "Result")
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "20em") %>%
  column_spec(2, width = "8em") %>% 
  footnote(
    general = "NR: not reported.",
    # alphabet = c(" "),
    general_title = "",
    footnote_as_chunk = FALSE
  )

# write_csv(pt_char_table_rev, "/Users/mgrant/Desktop/pt_char_table_rev.csv", na = "")

table_n <- tab_inc()

```

