---
title: "TOFR Confirmation (draft/preliminary)"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
output:
  html_document:
    font: Source Sans Pro
    theme: cosmo
    anchor_sections: TRUE
    toc_float: 
      collapsed: FALSE
      smooth_scroll: TRUE
    toc_depth: 3
    linkcolor: blue
  latex_engine: xelatex
  pdf_document:
    toc: yes
    toc_depth: '3'
# bibliography: "bib/kq4.bib"
# csl: jama.csl
# link-citations: yes
workflowr:
  suppress_report: false
nocite: '@*'
---

```{=html}
<style type="text/css">
  body{
  font-size: 9.5pt;
  font-family: Source Sans Pro;
}

.caption {
  font-size: 15px;
}

.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  color: #090909;
  background-color: #0909093d;
}

.lightable-classic.lightable-hover tbody tr:hover {
    background-color: #c5d4e4;
}
.btn-xs, .btn-group-xs>.btn { 
display: none; 
}

.btn-default {
display: none !important; 
}

.popover-title {
      font-size: 12px;
  }

.popover-content {
      font-size: 12px;
  }
  
.popover-content {
    background-color: white;
    <!-- color: #FFFFFF; -->
    padding: 2px;
  }

<!-- .arrow { -->
<!--   border-right-color: red !important; -->
<!-- } -->

<!-- :target {  /* fix target location so caption appears */ -->
<!--     display: block;     -->
<!--     position: relative;      -->
<!--     top: 10px; -->
<!--     visibility: hidden; -->
<!-- } -->

</style>

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover({html: true, placement: top});
});
</script>
```
```{r setup, include = FALSE}
## setup ---------------------------------------------- (2022-02-14 16:17) @----
knitr::opts_chunk$set(echo = TRUE)
source("code/readfiles_nmb_102721.R")
# index of tibbles
```

```{r dataBaseRev}
## data/refids ---------------------------------------- (2022-02-15 10:28) @
## refids --------------------------------------------- (2022-02-21 10:31) @----
# rev refids volatile study_arm.dat 
rev_refids <- study_char.dat %>% 
  filter(rev_agt == "rev_agt") %>% 
  pull(refid) %>% 
  unique()

neo_dosing_refids <- study_arm.dat %>% 
  filter(subgroup == "neo_dosing") %>% 
  pull(refid) %>% 
  unique()

sug_dosing_refids <- study_arm.dat %>% 
  filter(subgroup == "sug_dosing") %>% 
  pull(refid) %>% 
  unique()

# note that subgroup assigned by arm
subgroup_refids <- study_arm.dat %>% 
  filter(subgroup != "none") %>% 
  pull(refid) %>% 
  unique()

# from latest distiller 2022/02/21 08:13 n=26
rnmb_dist_refids <- dichot.dat %>%
  filter(refid %in% rev_refids) %>%
  # filter(!is.na(rnmb), !refid %in% subgroup_refids) %>% # TODO: check if correct
  filter(!is.na(rnmb), age == "Adult") %>% # TODO: check if correct
  # remove single arm studies; 2022/02/21 08:52 will be Yip 2304, Alenezu 3574
  group_by(refid) %>%
  filter(n() >= 2) %>%
  ungroup() %>%
  select(refid) %>%
  distinct() %>%
  pull()

# temp <- study_arm_rev.dat %>% 
#   filter(refid %in% rnmb_dist_refids_wsub) %>% 
#   mutate(subgroup = ifelse(refid %notin% rnmb_dist_refids, "subgroup", NA)) %>% 
#   relocate(subgroup, .after = refid)
# 
# write_csv(temp, "/Users/mgrant/Desktop/temp.csv", na = "")

## data char, arm, dichot ----------------------------- (2022-02-21 10:32) @----
study_char_rev.dat <- study_char.dat %>%
  filter(refid %in% rev_refids) 

study_arm_rev.dat <- study_arm.dat %>%
  filter(refid %in% rev_refids) %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    ),
    arm = case_when(
      revagent %in% c("neo") ~ "Neo",
      revagent %in% c("sug") ~ "Sug",
      str_detect(study_arm_k, "pont") ~ "Spont",
      revagent %in% c("other_agent") ~ revother,
      TRUE ~ "Other"
    ),
    arm = ifelse(str_detect(arm, "lacebo|saline"), "Plac", arm),
    arm = ifelse(str_detect(arm, "yridostigmine"), "Pyrid", arm),
    arm = factor(arm, levels = c("Sug", "Neo", "Plac", "Spont", "Pyrid", "Other"), ordered = TRUE),
    volatile = if_any(c(an_isoflurane, an_sevoflurane, an_desf, an_hal), ~ !is.na(.))
  ) %>%
  select(refid, arm_id, study, year, design, arm_n, arm, age, study_arm_k, subgroup, depth, depth_rev_f, starts_with("depth_rev_"), anesth:anes_agent_spec, neo_dose, neo_max_dose, neo_dose_unit, sug_dose, sug_dose_max, nmbagent, gen_type, revtim, revtim_comment, mon_type, mon_cat, mon_cat_f)

dichot_rev.dat <- dichot.dat %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    )
  )

# study_arm_rev.dat %>% tabyl(depth_rev_f)
```

```{r rnmbData, echo = FALSE}
## rnmb data distiller -------------------------------- (2022-02-21 09:00) @----
# add subgroup studies with relevant main effects
# Martinez-Ubieto 2016; need to combine spontaneous arms
rnmb_dist_refids <- sort(unique(c(rnmb_dist_refids)))

study_arm_rnmb.dat <- study_arm_rev.dat %>% 
  filter(refid %in% rnmb_dist_refids) %>% 
  select(refid, arm_id, study, subgroup, year, arm, study_arm_k, starts_with("depth_rev"), mon_type, mon_cat, mon_cat_f, neo_dose, neo_max_dose, neo_dose_unit, sug_dose, sug_dose_max, arm_n, nmbagent, gen_type, revtim, revtim_comment)

dichot_rnmb.dat <- dichot_rev.dat %>% 
  filter(refid %in% rnmb_dist_refids) %>% 
  select(refid, study, arm_id, rnmb1_dev, rnmb1_clinical, rnmb1_where, rnmb2_dev, rnmb2_clinical, rnmb2_where, rnmb, rnmb1_n, rnmb1_per, rnmb1_7, rnmb1_8, rnmb1_9, rnmb1_1, rnmb1_clinical, rnmb2_n, rnmb2_per, rnmb2_7, rnmb2_8, rnmb2_9, rnmb2_1, rnmb2_clinical)

rnmb.dat <- left_join(study_arm_rnmb.dat, dichot_rnmb.dat, by = c("refid", "study", "arm_id"))

study_char_rnmb.dat <- study_char_rev.dat %>%
  filter(refid %in% rnmb_dist_refids) %>% 
  select(refid, study_l, age, design)

rnmb.dat <- left_join(rnmb.dat, study_char_rnmb.dat, by = c("refid")) %>%
  relocate(c(study_l, age, design, year), .before = study) %>% 
  filter(refid %in% rnmb_dist_refids) 

tofr_confirm <- study_arm.dat %>% 
group_by(refid) %>%
  slice(1) %>%
  select(refid, extbconf, tofrext) %>%
  mutate(extbconf = case_when(
    extbconf == "yes" ~ "TOFR confirmed",
    extbconf == "no" ~ "TOFR not confirmed",
    extbconf == "ns" ~ "Not stated"
  ),
  tofr = case_when(
    str_detect(tofrext, "1") ~ '1.0',
    str_detect(tofrext, "9") ~ "0.9",
    str_detect(tofrext, "8") ~ "0.8",
    str_detect(tofrext, "7") ~ "0.7",
    str_detect(tofrext, "ns") ~ "NS",
  ))

rnmb.dat <- left_join(rnmb.dat, tofr_confirm, by = "refid")

rnmb_meta_distiller.dat <- rnmb.dat %>%
  filter(!is.na(extbconf), !is.na(rnmb1_9) | !is.na(rnmb2_9) | !is.na(rnmb1_1) | !is.na(rnmb2_1)) %>%
  filter(arm %in% c("Sug", "Neo", "Spont", "Plac")) %>%
  mutate(rnmb_n = case_when(
    !is.na(rnmb1_9) ~ rnmb1_n,
    !is.na(rnmb2_9) ~ rnmb2_n,
    !is.na(rnmb1_1) ~ rnmb1_n,
    !is.na(rnmb2_1) ~ rnmb2_n,
    ),
    extbconf = factor(extbconf, levels = c("TOFR confirmed", "TOFR not confirmed", "Not stated"))
  ) %>% 
  select(refid, study, design, arm, arm_n, rnmb_n, extbconf, tofr, depth_rev_f, mon_type, mon_cat_f) %>% 
  arrange(extbconf, depth_rev_f)

# rnmb_meta_distiller.dat %>% tabyl(mon_cat_f)
```

```{r rnmbDataExternal, echo = FALSE}
## rnmb extubation external data ---------------------- (2022-03-19 17:44) @----
# study & design to add
study_add <- study_char.dat %>% 
  select(refid, study, year, design) 

# read excel file
ext_confirm_temp <- readxl::read_xlsx("data/Extubationconfirm_031722_mg.xlsx", sheet = "TOFR Confirm", range = "A1:Q98") %>%
  clean_names() %>%
  left_join(., study_add, by = "refid") %>%
  mutate(
    study = ifelse(is.na(study), str_extract(authors, "^\\w*"), study), # TODO: delete when distiller complete
    rnmb_n = as.numeric(str_extract(rnmb_np, "^\\d{1,3}")),
    tofr_conf = factor(tofr_confirm, levels = c("Yes", "No", "NS", "PNS"), labels = c("Yes", "No", "Not stated", "PNS")),
    tofr_conf_comb = fct_collapse(tofr_conf, No = c("No", "PNS")),
    volatile = case_when(
      str_detect(anesth, "Vol") ~ "Volatile",
      str_detect(anesth, "NS") ~ "NS/Missing",
      anesth == "TIVA" ~ "TIVA alone",
      is.na(anesth) ~ "NS/Missing",
    ),
    rnmb_def_comb = case_when(
      str_detect(rnmb_def, "0.9") ~ "0.9",
      str_detect(rnmb_def, "0.8") ~ "0.8",
      str_detect(rnmb_def, "0.7") ~ "0.7",
      str_detect(rnmb_def, "NS") ~ "NS",
    )
  ) %>%
  group_by(refid) %>%
  fill(study) %>%
  ungroup() %>% # TODO: delete when distiller complete
  select(refid, design, study, year, rev_agent, rnmb_n, arm_n, volatile, monitor, tofr_conf, tofr_conf_comb, tofr_ext, rnmb_def, rnmb_def_comb, rnmb_monitor, depth) %>%
  rename(arm = rev_agent)

# write_csv(ext_confirm_temp, "/Users/mgrant/Desktop/ext_confirm_temp.csv", na = "")
# ext_confirm_temp %>% tabyl(depth)
# ext_confirm_temp %>% tabyl(tofr_conf_comb, tofr_ext)
```

## TOFR ≥0.9 Before Extubation

```{r rnmbMetaTofrData}
## rnmbMetaConfirm 0.9 -------------------------------- (2022-03-20 09:36) @----
#  select 0.9 at extubation or no and not stated; includes qualitative and quantitative monitoring
conf_meta_9 <- ext_confirm_temp %>% 
  filter(tofr_ext == "0.9" | tofr_conf_comb %in% c("No", "Not stated")) %>% # verified 
  filter(rnmb_def_comb == 0.9) %>% 
  mutate(extb_conf_r = case_when(
    tofr_conf_comb == "Yes" ~ "TOFR ≥0.9 confirmed",
    tofr_conf_comb == "No" ~ "TOFR not confirmed",
    tofr_conf_comb == "Not stated" ~ "Not stated"
  ),
  mon_cat_f = factor(monitor),
  mon_cat_f = fct_collapse(mon_cat_f, Quant = c("AMG", "EMG", "KMG", "Quant NS", "MMG"), Qual = c("PNS"), Clin = c("Clinical"), "None/NS" = c("No monitoring", "NS")),
  mon_cat_f = fct_relevel(mon_cat_f, c("Quant",  "Qual", "Clin", "None/NS"))
  ) %>% 
  select(refid, design, study, arm, arm_n, rnmb_n, extb_conf_r, depth, volatile, mon_cat_f)

# Hmisc::describe(conf_meta_9)

# from distiller 0.9 rnmb defn and confirm level
temp <- rnmb_meta_distiller.dat %>%
  filter(refid %notin% ext_confirm_temp$refid) %>%
  # select(-design) %>%
  mutate(
    arm_n = case_when(
      study == "Della Rocca 2013" & arm == "Sug" ~ 207,
      study == "Della Rocca 2013" & arm == "Neo" ~ 150,
      TRUE ~ arm_n
    ),
    rnmb_n = case_when(
      study == "Della Rocca 2013" & arm == "Sug" ~ 4,
      study == "Della Rocca 2013" & arm == "Neo" ~ 47,
      TRUE ~ rnmb_n
    ),
    extb_conf_r = ifelse(extbconf == "TOFR confirmed", "TOFR ≥0.9 confirmed", extbconf),
    depth = firstup(as.character(depth_rev_f)),
    volatile = ifelse(study == "Della Rocca 2013", "Volatile", "TIVA alone")
  ) %>% 
  group_by(study, arm) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-c(extbconf, tofr, depth_rev_f)) %>% 
  relocate(extb_conf_r, .before = depth) %>% 
  select(names(conf_meta_9))

conf_meta_9 <- conf_meta_9 %>% 
  bind_rows(., temp) %>% 
  mutate(year = as.numeric(str_extract(study, "\\d{4}")),
         extb_conf_r = factor(extb_conf_r, levels = c("TOFR ≥0.9 confirmed", "TOFR not confirmed", "Not stated")),
         study = ifelse(study == "Wu 2014" & arm_n > 100, "Wu 2014 (Chinese)", study),
         study = ifelse(study == "Wu 2014" & arm_n < 100, "Wu 2014 (Caucasian)", study),
         ) %>% 
  arrange(depth, year) %>% 
  distinct() # 2022/03/23 11:11

```

```{r metaBaseCode, fig.align = 'left', fig.width = 11, fig.height = 9.5}
## metaSug -------------------------------------------- (2022-03-23 07:42) @----
## forest function and base meta ---------------------- (2022-03-23 14:30) @----
forest_conf <- function(meta_result) {
  forest(meta_result,
    fixed = FALSE,
    rightcols = c("effect", "ci", "depth"),
    rightlabs = c("Incidence", "(95% CI)", "Depth @ Reversal"),
    digits = 2,
    digits.tau2 = 1,
    overall.hetstat = TRUE,
    print.I2.ci = TRUE,
    prediction = FALSE,
    prediction.subroup = TRUE,
    fs.xlab = 11,
    pooled.events = TRUE,
    subgroup = TRUE,
    print.subgroup.name = FALSE,
    text.subgroup.nohet = TRUE,
    colgap.forest.left = "30mm",
    just.addcols.right = "left",
    xlim = c(0, 0.8),
    xlab = "Incidence TOFR <0.9"
  )
}

rnmb_meta <- metaprop(rnmb_n, arm_n,
  data = conf_meta_9,
  studlab = study,
  sm = "PAS",
  hakn = TRUE,
  prediction.subgroup = FALSE,
  prediction = FALSE,
  subgroup = extb_conf_r,
)

## rrCalc --------------------------------------------- (2022-03-23 07:43) @----
# use arcsin est and sd; backtransform simulated 
compare_ci <- function(data_meta) {
  rnmb_pas <- update(data_meta, backtransf = FALSE)[c("TE.random.w", "seTE.random.w")] %>% unlist()
  set.seed(12345)
  rr <- (sin(rnorm(1000000, rnmb_pas[1], rnmb_pas[3])))^2 / (sin(rnorm(1000000, rnmb_pas[2], rnmb_pas[4])))^2
  rr <- quantile(rr, probs = c(0.025, 0.5, 0.975))
  paste0(round_2(rr[2]), " (95% CI: ", round_2(rr[1]), ", ", round_2(rr[3]), ")")
}
```

### Sugammadex

<a id="kq4Fig1"></a>

<br/>

<font size = 4> Figure `r figure_n`. Incidence of residual neuromuscular block (TOFR \<0.9) in arms of randomized and nonrandomized studies using quantitative monitoring among patients reversed with sugammadex according to whether TOFR ≥0.9 was reported as confirmed prior to extubation. </font>

```{r metaSug, fig.align = "left", fig.width = 11, fig.height = 9.5}
## metaSug -------------------------------------------- (2022-03-24 10:18) @----
rnmb_sug <- update(rnmb_meta,
  subset = arm == "Sug" & mon_cat_f == "Quant",
  # remove Alday 2019 outlier
  # subset = arm == "Sug" & mon_cat_f == "Quant" & study != "Alday 2019",
  # compare confirm vs not confirmed
  # subset = arm == "Sug" & mon_cat_f == "Quant" & str_detect(extb_conf_r, "confirm"), 
  # compare confirm vs not confirmed removing Alday 2019
  # subset = arm == "Sug" & mon_cat_f == "Quant" & str_detect(extb_conf_r, "confirm")  & study != "Alday 2019",
)

forest_conf(rnmb_sug)
figure_n <- fig_inc()

## risk ratio ----------------------------------------- (2022-03-23 17:08) @----
# rnmb_sug <- update(rnmb_meta,
#   # subset = arm == "Sug" & mon_cat_f == "Quant" & str_detect(extb_conf_r, "confirm"),
#   subset = arm == "Sug" & str_detect(extb_conf_r, "confirm"),
#   backtransf = FALSE,
# )
# compare_ci(rnmb_sug)

## exclude Alday 2019 --------------------------------- (2022-03-24 08:23) @----
# rnmb_sug <- update(rnmb_meta,
#   subset = arm == "Sug" & mon_cat_f == "Quant" & study != "Alday 2019" & str_detect(extb_conf_r, "confirm"),
#   backtransf = FALSE,
# )
# compare_ci(rnmb_sug)

# ## assume all not stated confirmed or not ----------- (2022-03-24 09:57) @----
# conf_meta_sens <- conf_meta_9 %>%
#   mutate(
#     extb_conf_r = fct_recode(extb_conf_r, "TOFR ≥0.9 confirmed" = "Not stated")
#     # extb_conf_r = fct_recode(extb_conf_r, "TOFR not confirmed" = "Not stated")
#   )
# 
# rnmb_meta <- metaprop(rnmb_n, arm_n,
#   data = conf_meta_sens,
#   studlab = study,
#   sm = "PAS",
#   hakn = TRUE,
#   subset = arm == "Sug" & mon_cat_f == "Quant",
#   subgroup = extb_conf_r,
#   backtransf = FALSE
# )
# 
# compare_ci(rnmb_meta)

```
Mod: moderate; Min: minimal; Oth: other; NS: not stated.<br/> 
Difference between confirmed and not confirmed p = 0.11 (removing Alday 2019 p = 0.19) — risk ratio 0.27 (95% CI: 0.03, 1.43). <br/>
Removing Alday 2019, risk ratio 0.38 (95% CI: 0.04, 1.72). <br/>
Adding arms from studies not using quantitative monitoring — risk ratio 0.27 (95% CI: 0.03, 1.30).<br/>
Assuming all not stated were confirmed — risk ratio 0.21 (95% CI: 0.02, 1.11). <br/>
Assuming all not stated were not confirmed — risk ratio 0.42 (95% CI: 0.05, 2.16). <br/>

<br/><br/>

<a id="kq4Fig1"></a>

### Neostigmine

<br/>

<font size = 4> Figure `r figure_n`. Incidence of residual neuromuscular block (TOFR \<0.9) in arms of randomized and nonrandomized studies among patients reversed with neostigmine according to whether TOFR ≥0.9 was reported confirmed prior to extubation. </font>

```{r metaNeo, fig.align = "left", fig.width = 11, fig.height = 9.5}
## metaNeo -------------------------------------------- (2022-03-24 10:18) @----
rnmb_neo <- update(rnmb_meta,
  subset = arm == "Neo" & mon_cat_f == "Quant",
  # subset = arm == "Neo" & mon_cat_f == "Quant" & str_detect(extb_conf_r, "confirm"), 
)

forest_conf(rnmb_neo)
figure_n <- fig_inc()

## risk ratio ----------------------------------------- (2022-03-23 17:08) @----
# rnmb_neo <- update(rnmb_meta,
#   # subset = arm == "Neo" & str_detect(extb_conf_r, "confirm") & mon_cat_f == "Quant",
#   subset = arm == "Neo" & str_detect(extb_conf_r, "confirm"),
#   backtransf = FALSE,
# )
# compare_ci(rnmb_neo)

## assume all not stated confirmed or not ------------- (2022-03-24 09:57) @----
# conf_meta_sens <- conf_meta_9 %>% 
#   mutate(
#     # extb_conf_r = fct_recode(extb_conf_r, "TOFR ≥0.9 confirmed" = "Not stated")
#     extb_conf_r = fct_recode(extb_conf_r, "TOFR not confirmed" = "Not stated")
#   )
# 
# rnmb_meta <- metaprop(rnmb_n, arm_n,
#   data = conf_meta_sens,
#   studlab = study,
#   sm = "PAS",
#   hakn = TRUE,
#   subset = arm == "Neo" & mon_cat_f == "Quant",
#   subgroup = extb_conf_r,
#   backtransf = FALSE
# )
# 
# compare_ci(rnmb_meta)
```
Mod: moderate; Min: minimal; Oth: other; NS: not stated.<br/> 
Difference between confirmed and not confirmed p < 0.0002 — risk ratio 0.21 (95% CI: 0.06, 0.49). <br/>
Adding arms from studies not using quantitative monitoring — risk ratio 0.20 (95% CI: 0.06, 0.44). <br/>
Assuming all not stated were confirmed — risk ratio 0.25 (95% CI: 0.09, 0.52). <br/>
Assuming all not stated were not confirmed — risk ratio 0.30 (95% CI: 0.09, 0.73). <br/>


<br/><br/>

### Summary of included studies  

```{r}
## summarize studies----------------------------------- (2022-03-22 12:56) @----
conf_meta_9_tab <- conf_meta_9 %>% 
  group_by(refid) %>% 
  slice(1) 

tabyl_row <- function(data, arm_tx, var, name_cat){
    data %>% 
    filter(arm %in% c({{arm_tx}})) %>% 
    tabyl({{var}}, show_na = FALSE) %>% 
    adorn_pct_formatting(rounding = "half up", digits = 0) %>% 
    rename("char" = var) %>% 
    add_row(.before = 1, char = name_cat)
}

bind_rows(
  tabyl_row(conf_meta_9, "Sug", "mon_cat_f", "Monitoring"),
  tabyl_row(conf_meta_9, "Sug", "volatile", "Anesthetic"),
  tabyl_row(conf_meta_9, "Sug", "arm", "Arms"),
  tabyl_row(conf_meta_9, "Sug", "design", "Design")
) %>%
  kbl(
    booktabs = T, align = c("lrr"), escape = FALSE, padding = 10, col.names = c("Characteristic", "N", "%"),
    caption = "Summary of all sugammadex studies."
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover")

bind_rows(
  tabyl_row(conf_meta_9, "Neo", "mon_cat_f", "Monitoring"),
  tabyl_row(conf_meta_9, "Neo", "volatile", "Anesthetic"),
  tabyl_row(conf_meta_9, "Neo", "arm", "Arms"),
  tabyl_row(conf_meta_9, "Neo", "design", "Design")
) %>%
  kbl(
    booktabs = T, align = c("lrr"), escape = FALSE, padding = 10, col.names = c("Characteristic", "N", "%"),
    caption = "Summary of all neostigmine studies."
  ) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover")

# conf_meta_9 %>% tabyl(tofr_conf_comb, tofr_ext)
```


