---
title: "TOFR Confirmation Before Extubation"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
output:
  html_document:
    font: Source Sans Pro
    theme: cosmo
    anchor_sections: TRUE
    toc_float: 
      collapsed: FALSE
      smooth_scroll: TRUE
    toc_depth: 3
    linkcolor: blue
  latex_engine: xelatex
  pdf_document:
    toc: yes
    toc_depth: '3'
bibliography: "bib/kq3_confirm.bib"
csl: jama.csl
link-citations: yes
workflowr:
  suppress_report: false
nocite: '@*'
---

```{=html}
<style type="text/css">
  body{
  font-size: 9.5pt;
  font-family: Source Sans Pro;
}

.caption {
  font-size: 15px;
}

.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  color: #090909;
  background-color: #0909093d;
}

.lightable-classic.lightable-hover tbody tr:hover {
    background-color: #c5d4e4;
}
.btn-xs, .btn-group-xs>.btn { 
display: none; 
}

.btn-default {
display: none !important; 
}

.popover-title {
      font-size: 12px;
  }

.popover-content {
      font-size: 12px;
  }
  
.popover-content {
    background-color: white;
    <!-- color: #FFFFFF; -->
    padding: 2px;
  }

<!-- .arrow { -->
<!--   border-right-color: red !important; -->
<!-- } -->

:target {  /* fix target location so caption appears */
    display: block;
    position: relative;
    top: -25px;
    visibility: hidden;
}

</style>

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover({html: true, placement: top});
});
</script>
```
```{r setup, include = FALSE}
## setup ---------------------------------------------- (2022-02-14 16:17) @----
knitr::opts_chunk$set(echo = TRUE)
source("code/readfiles_nmb_102721.R")
library(gtsummary, quietly = TRUE)
```

```{r dataBaseRev}
## confirm extubation refids [extb_refids] ------------ (2022-06-27 12:42) @----
# confirmation; n = 134 2022-06-27; 283 arms
extb_refids <- study_arm.dat |> 
  filter(!is.na(extbconf), age == "Adult") |> 
  pull(refid) |> 
  unique()

## studies/arms tables (not run) ---------------------- (2022-03-25 19:00) @----
# study_arm.dat %>%
#   filter(refid %in% extb_refids) %>%
#   filter(age == "Adult", !is.na(extbconf)) %>% # !is.na(extbconf) because arms not relevant fully paired or historical controls
#   # select(refid, study, extbconf) # debug
#   group_by(refid) %>%
#   slice(1) %>%
#   # tabyl(extbconf) %>%
#   # tabyl(tofrext) %>%
#   # summarize(total = sum(arm_n))
#   tabyl(design) %>%
#   adorn_totals()

## rnmb extubation refids extb_rnmb_refids ------------ (2022-06-27 19:01) @----
# confirmation and rnmb data at any tofr
extb_rnmb_refids <- dichot.dat %>%
  filter(age == "Adult") %>% 
  filter(refid %in% extb_refids) %>% # comment out if checking refids below
  filter(if_any(c(rnmb1_n, rnmb2_n), ~ !is.na(.))) %>%
  select(refid) %>%
  distinct() %>%
  pull()

# check refids confirmation w/wo extubation data; 98 with extubation confirm; 81 with rnmb 
# length(unique(extb_rnmb_refids))
# extb_refids |> tibble(refid = _) |> filter(refid %in% extb_rnmb_refids) |> tally()    # n = 98 2022-06-27
# extb_refids |> tibble(refid = _) |> filter(refid %notin% extb_rnmb_refids) |> tally() # no rnmb data n = 36 2022-06-27

## study char arm dichot ------------------------------ (2022-06-27 19:14) @----
study_char_conf.dat <- study_char.dat %>%
  filter(refid %in% extb_rnmb_refids) 

study_arm_conf.dat <- study_arm.dat %>%
  filter(refid %in% extb_rnmb_refids) %>%
  filter(!is.na(extbconf)) %>% # verify for each arm
  remove_empty(which = "cols") %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    ),
    arm = case_when(
      revagent %in% c("neo") ~ "Neo",
      revagent %in% c("sug") ~ "Sug",
      str_detect(study_arm_k, "pont") ~ "Spont",
      revagent %in% c("other_agent") ~ revother,
      TRUE ~ "Other"
    ),
    arm = ifelse(str_detect(arm, "lacebo|saline"), "Plac", arm),
    arm = ifelse(str_detect(arm, "yridostigmine"), "Pyrid", arm),
    arm = factor(arm, levels = c("Sug", "Neo", "Plac", "Spont", "Pyrid", "Other"), ordered = TRUE),
    volatile = if_any(c(an_isoflurane, an_sevoflurane, an_desf, an_hal), ~ !is.na(.))
  ) %>%
  select(refid, extbconf, tofrext, arm_id, year, design, arm_n, arm, age, depth_rev_f, nmbagent, volatile, mon_type, mon_cat, mon_cat_f, sug_dose, neo_dose)

dichot_conf.dat <- dichot.dat %>%
filter(refid %in% extb_rnmb_refids) %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    ),
  ) %>%
  select(refid, arm_id, study, study_l, rnmb_location, rnmb1_where, rnmb2_where, matches("rnmb[1-2]_n"), matches("[rnmb][1-2]_9"), tofr_normalized) %>% 
  select(-contains("pval"), -contains("clin"), -contains("per")) %>% 
  left_join(., study_arm_conf.dat, by = c("refid", "arm_id")) %>% 
  relocate(c(year, design, arm, arm_n, age, extbconf, tofrext), .after = study_l)

## create meta-analysis data -------------------------- (2022-07-05 10:42) @----
conf_meta_temp <- dichot_conf.dat |> 
  filter(!is.na(mon_cat_f)) |> 
  mutate(
    # to have 3 categories of monitoring: Quant, Qual, Clin/None/NS (not stated)
    mon_cat_f = fct_collapse(mon_cat_f, "Clin/None/NS" = c("Clin", "None/NS")), 
    rnmb9_n = case_when(
      rnmb1_9 == "rnmb1_9" ~ rnmb1_n,
      rnmb2_9 == "rnmb2_9" ~ rnmb2_n,
    ),
    rnmb_where = case_when(
      rnmb1_9 == "rnmb1_9" ~ rnmb1_where,
      rnmb2_9 == "rnmb2_9" ~ rnmb2_where,
    ),
    rnmb_where = ifelse(is.na(rnmb_where), rnmb_location, rnmb_where),
    rnmb_where = ifelse(rnmb_where == "post_ext", "post_extub", rnmb_where),
    confirm = case_when(
      extbconf == "yes" & tofrext %in%  c("tofrext9", "tofrext1") ~ "Confirmed ≥0.9",
      extbconf == "yes" & grepl("7|8|ns", tofrext) ~ "Confirmed ≥0.8/NS", # confirmed at 0.7, 0.8, or level not stated
      extbconf == "no" ~ "Not confirmed",
      extbconf == "ns" ~ "Not stated"
    ),
    # if No quantitative monitoring, set to unconfirmed 
    confirm = ifelse(mon_cat_f == "Qual", "Qualitative assessment", confirm), 
    confirm = ifelse(str_detect(mon_cat_f, "Clin"), "Clinical/None/NS", confirm), 
  ) %>%
  # only neostigmine and sugammadex arms
  filter(!is.na(rnmb9_n), arm %in% c("Neo", "Sug")) %>% 
  select(refid, study, year, design, age, arm, arm_n, rnmb9_n, rnmb_where, rnmb_location, extbconf, tofrext, confirm, nmbagent, volatile, mon_cat_f, depth_rev_f)

## multiarm using same agent -------------------------- (2022-07-05 20:27) @----
multiarm_refid <- conf_meta_temp |> 
  group_by(study, arm, confirm) |> 
  filter(n() > 1) |> 
  ungroup() |> 
  select(refid) |> 
  distinct() |> 
  pull(refid)

# get combined depths for arms, 2022-06-30 8 arms from 7 studies
temp_1 <- conf_meta_temp %>%
  filter(refid %in% multiarm_refid) %>%
  group_by(study, arm) %>%
  summarise(arm_n = sum(arm_n), rnmb9_n = sum(rnmb9_n), depth_rev_f = str_c(depth_rev_f, collapse = ":")) %>%
  ungroup %>%
  select(-arm)

# get characteristics for combined arms
temp_2 <- conf_meta_temp %>%
  filter(refid %in% multiarm_refid) %>%
  group_by(study, arm) %>%
  slice(1) %>%
  ungroup() %>%
  select(-c(study, arm_n, rnmb9_n, depth_rev_f))

# new data from multiarm
add <- bind_cols(temp_2, temp_1) %>%
  select(names(conf_meta_temp))

conf_meta_temp <- conf_meta_temp %>%
  filter(!refid %in% multiarm_refid) %>%
  bind_rows(., add) %>%
  mutate(
    depth = as.character(depth_rev_f),
    depth = str_replace(depth, "mod:mod", "mod"),
    depth = str_replace(depth, "ns", "NS"),
    depth = str_replace(depth, "mod", "Mod"),
    depth = str_replace(depth, "deep", "Deep"),
    depth = str_replace(depth, "shall", "Shallow"),
    depth = str_replace(depth, "oth", "Other"),
    depth = str_replace(depth, "endsurg", "End surgery"),
    depth = str_replace(depth, "min", "Min"),
    depth = str_replace(depth, "Mod:Deep", "Deep:Mod")
  ) |> 
  select(-design) # add after adding domenech

# add Domenech 2019; entered as comparison of monitoring vs none in kq3
domenech2019 <- tribble(
  ~mon_cat_f, ~refid, ~study, ~year, ~age, ~arm, ~arm_n, ~rnmb9_n, ~rnmb_where, ~rnmb_location, ~extbconf, ~tofrext, ~confirm, ~nmbagent, ~volatile, ~depth_rev_f, ~depth, ~study_l, 
  "Quant",3270,"Domenech 2019",2019,"Adult","Sug",42,0,"pacu","pacu","ns",NA,"Not stated","various",NA,"ns","NS",NA,
  "Quant",3270,"Domenech 2019",2019,"Adult","Neo",9,0,"pacu","pacu","ns",NA,"Not stated","various",NA,"ns","NS",NA, 
  "Clin",3270,"Domenech 2019",2019,"Adult","Sug",19,3,"pacu","pacu","ns",NA,"Clinical/None/NS","various",NA,"ns","NS",NA, 
  "Clin",3270,"Domenech 2019",2019,"Adult","Neo",5,2,"pacu","pacu","ns",NA,"Clinical/None/NS","various",NA,"ns","NS",NA,  
) |> 
  select(names(conf_meta_temp)) # will be the same for binding rows

## conf_meta 0.9/0.8/NS/qual/clin---------------------- (2022-04-01 08:37) @----
conf_meta <- bind_rows(conf_meta_temp, domenech2019) %>% 
  mutate(
    confirm = factor(confirm, levels = c("Confirmed ≥0.9", "Confirmed ≥0.8/NS", "Not confirmed", "Not stated", "Qualitative assessment", "Clinical/None/NS")),
    rnmb_where = case_when(
    rnmb_where == "ns" ~ "NS",
    rnmb_where %in% c("post_extub", "or") ~ "Extubation",
    rnmb_where == "pacu" ~ "PACU",
    rnmb_where == "recover" ~ "Recovery"
  ),
  rnmb_where = factor(rnmb_where, levels = c("Extubation", "PACU", "Recovery", "NS"))) %>% 
  arrange(confirm, rnmb_where, year) %>%
  left_join(., study_ident[, c("refid", "study_l", "design_f")], by = "refid") |> 
  # rename(design_f = design) %>%
  mutate(
    design_f = fct_recode(design_f,
      "Before-After" = "Before-After/Time Series",
      "NR Trial" = "Nonrandomized Trial",
      "Prosp Cohort" = "Prospective Cohort",
      "Retro Cohort" = "Retrospective Cohort",
    ),
    design_f = fct_drop(design_f)
  )

rm(add, multiarm_refid, temp_1, temp_2, conf_meta_temp)

## descriptive for results (not run) ------------------ (2022-07-05 12:24) @----
# conf_meta |> 
#   tabyl(confirm) |> 
#   adorn_totals()
# 
# conf_meta |> 
#   group_by(refid) |> 
#   slice(1) |> 
#   tabyl(design_f, show_missing_levels = FALSE) |> 
#   adorn_totals()
# 
# tbl_temp <- conf_meta |> 
#   tbl_cross(row = mon_cat_f, col = confirm, percent = "row")
# 
# tbl_temp <- as_tibble(tbl_temp)
# 
# write_csv(tbl_temp, "/Users/mgrant/Desktop/tbl_temp.csv", na = "")
# can save a prn to add to text file

```

# **Summary**

<font size = 4> Figure `r figure_n`. Residual neuromuscular blockade (TOFR < 0.9, pooled incidence proportion) in arms of randomized and nonrandomized studies according to type of monitoring and confirmation of TOFR prior to extubation. From random effects meta-analyses of proportions fitted with generalized linear mixed models. </font>
 
`r figure_n <- fig_inc()`

<br/>

```{r, fig.align = "left", fig.width = 9.5, fig.height = 4, eval = FALSE}
library(forester)
library(extrafont)
loadfonts(device = "pdf")

table <- readxl::read_excel(
  "data/confirm_data.xlsx",
  sheet = "data",
  range = "A1:G20"
) |> 
  mutate(
    Group = ifelse(str_detect(Group, "Yes|No"), paste0("    ", Group), Group)
  )

forester(left_side_data = table[,1:4],
         estimate = table$`per 100`,
         estimate_col_name = "RNMB per 100 (95% CI)",
         ci_low = table$`CI low`,
         ci_high = table$`CI high`,
         display = TRUE,
         nudge_y = -.3, 
         justify = 0,
         file_path = "docs/assets/confirm_summary.png",
         font_family = "Fira Sans")

```

<img src = "assets/confirm_summary.png" style="width:800px;" align = "left"/>

<br clear="all" />

RNMB: residual neuromuscular blockade (TOFR < 0.9); NS: not stated.

<br/>

# **Sugammadex**

<a id="confTab1"></a>

<br/>

<font size = 4> Table `r table_n`. Residual neuromuscular blockade in study arms according to TOFR confirmation prior to extubation when quantitative monitoring was used and in studies where quantitative monitoring was not used. Sugammadex given for reversal.</font>

```{r sugammadexKbl}
## descriptive table ---------------------------------- (2022-03-26 15:30) @----
conf_kbl <- conf_meta |>
  # arrange(confirm, year, study, arm) %>%
  mutate(
    rnmb9_np = n_percent1(rnmb9_n, rnmb9_n / arm_n * 100),
    rnmb9_per = rnmb9_n / arm_n,
  ) |>
  select(refid, year, design_f, study, study_l, arm, arm_n, rnmb9_n, nmbagent, volatile, mon_cat_f, depth, rnmb_where, rnmb9_np, extbconf, confirm, rnmb9_per) |>
  # select only to go in meta
  filter(arm %in% c("Neo", "Sug"))

temp <- conf_kbl |> 
  filter(confirm %in% c("Confirmed ≥0.9", "Not confirmed", "Not stated", "Confirmed ≥0.8/NS")) |> 
  # filter(confirm %in% c("Confirmed ≥0.9", "Not confirmed", "Not stated")) |> 
  pull(refid) |> 
  unique()

# save confirm studies for summary
confirm_studies <- conf_kbl |> 
  filter(confirm %in% c("Confirmed ≥0.9", "Not confirmed", "Not stated", "Confirmed ≥0.8/NS")) |> 
  select(refid, study) |> 
  distinct() |> 
  group_by(refid) |> 
  slice(1) |> 
  ungroup() |> 
  mutate(study = str_remove(study, " (Caucasian)"))

# write_csv(confirm_studies, "data/confirm_studies.csv", na = "")
rm(confirm_studies)

dichot_format <- function(x) (x/100)

conf_kbl %>%
  # temp <- conf_kbl %>%
  # table_tally_2(temp, confirm, design_f)
  # filter(mon_cat_f == "Quant") |> 
  filter(arm == "Sug") %>% 
  select(confirm, study, design_f, arm_n, nmbagent, volatile, depth, rnmb_where, rnmb9_np, rnmb9_per) %>% 
  mutate(
  rnmb_bar = case_when(
    confirm == "Confirmed ≥0.9" ~ bar_wn(rnmb9_per, rnmb9_per, color_1, 1),
    confirm == "Not confirmed" ~ bar_wn(rnmb9_per, rnmb9_per, color_4, 1),
    confirm == "Not stated"  ~ bar_wn(rnmb9_per, rnmb9_per, color_2, 1),
    confirm == "Confirmed ≥0.8/NS"  ~ bar_wn(rnmb9_per, rnmb9_per, color_3, 1),
    confirm == "Qualitative assessment"  ~ bar_wn(rnmb9_per, rnmb9_per, "#e74343", 1),
    confirm == "Clinical/None/NS"  ~ bar_wn(rnmb9_per, rnmb9_per, "#dc0c22", 1),
    ),
  # rnmb_bar = str_replace(rnmb_bar, ">\\d+\\.?\\d?", ",>&nbsp;"),
  rnmb_bar = str_replace(rnmb_bar, ">0\\.?\\d*", ",>&nbsp;"),
  nmbagent = firstup(str_extract(nmbagent, "^\\w{3}")),
  volatile = ifelse(volatile, "\U00D7", " "),
  ) %>% 
  select(-c(confirm, rnmb9_per)) %>% 
kbl(
    booktabs = T, align = c("llrccllll"), escape = FALSE, # format = "latex",
    col.names = c("Study", "Design", "N", "Agent", "Volatile", "Depth", "Place^a^", "N (%)", bar_ref),
  ) %>%
  add_header_above(c(" " = 5, "Reversal" = 1, "Residual Neuromuscular Blockade" = 3), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "4em") %>%
  column_spec(4, width = "4em") %>%
  column_spec(5, width = "5em") %>%
  column_spec(6, width = "7em") %>%
  column_spec(7, width = "6em") %>%
  column_spec(8, width = "6em") %>%
  column_spec(9, width = bar_width) %>% 
  pack_topnoind(., "Quantitative monitoring", 1, 30) %>% 
  pack_sub_bold_ind(., "Confirmed ≥ 0.9", 1, 10) %>%
  pack_sub_bold_ind(., "Confirmed ≥ 0.8/NS", 11, 12) %>%
  pack_sub_bold_ind(., "Not confirmed", 13, 23) %>%
  pack_sub_bold_ind(., "Not stated", 24, 30) %>%
  pack_top(., "Qualitative assessment", 31, 31) %>%
  pack_top(., "Clinical/None/NS", 32, 35) %>%
  footnote(
    general = "RCT: randomized controlled trial; NR Trial: nonrandomized trial; Prosp Cohort: prospective cohort; Retro Cohort: retrospective cohort; ROC: rocuronium; Vec: vecuronium; Var: various; Min: minimal; Mod: moderate; NS: not stated; PACU: post-anesthesia care unit; NS: not stated.",
    alphabet = c("Extubation includes designated in OR."),
    general_title = "",
    footnote_as_chunk = FALSE,
  )

table_n <- tab_inc()
```

```{r metaBaseCode, eval = FALSE}
## meta data ------------------------------------------ (2022-07-06 11:25) @----
# consider only confirmed vs not 
# only quantitative monitoring includes 0.8/NS
conf_meta_collapsed <- conf_meta |> 
  # filter(!confirm %in% c("Qualitative assessment", "Clinical/None/NS")) |> 
  mutate(
    confirm = fct_collapse(confirm, Confirmed = c("Confirmed ≥0.9", "Confirmed ≥0.8/NS")),
  )

# only quantitative monitoring 0.9
conf_meta_9 <- conf_meta 
  # filter(!confirm %in% c("Qualitative assessment", "Clinical/None/NS")) |> 
  # filter(!confirm %in% c("Confirmed ≥0.8/NS"))

## forest function ------------------------------------ (2022-03-23 14:30) @----
forest_conf <- function(meta_result) {
  forest(meta_result,
    overall = FALSE,
    common = TRUE,
    rightcols = c("effect", "ci"),
    rightlabs = c(" ", "(95% CI)"),
    smlab = "Residual Neuromuscular Blockade\n per 100 patients",
    digits = 2,
    pscale = 100,
    digits.tau2 = 1,
    overall.hetstat = FALSE,
    print.I2.ci = TRUE,
    prediction = FALSE,
    prediction.subroup = TRUE,
    fs.xlab = 11,
    pooled.events = TRUE,
    subgroup = TRUE,
    print.subgroup.name = FALSE,
    text.subgroup.nohet = TRUE,
    colgap.forest.left = "30mm",
    just.addcols.right = "left",
    xlim = c(0, 100),
    ref = 0
    # xlab = "Incidence/100 TOFR <0.9"
  )
}

## meta-anlayses -------------------------------------- (2022-07-25 09:04) @----
# base meta with all studies
# rnmb_meta_glmm_9          ≥0.9        sm = PLOGIT
# rnmb_meta_collapsed_glmm  ≥0.9/0.8/NS sm = PLOGIT
# rnmb_meta_9               ≥0.9        sm = PAS
# rnmb_meta_collapsed       ≥0.9/0.8/NS sm = PAS

# rnmb_meta_collapsed <- metaprop(rnmb9_n, arm_n,
#   data = conf_meta_collapsed,
#   studlab = study,
#   sm = "PAS",
#   method.tau = "PM",
#   hakn = TRUE,
#   prediction.subgroup = FALSE,
#   prediction = FALSE,
#   subgroup = confirm
# )
# 
# rnmb_meta_9 <- metaprop(rnmb9_n, arm_n,
#   data = conf_meta_9,
#   studlab = study,
#   sm = "PAS",
#   method.tau = "PM",
#   hakn = TRUE,
#   prediction.subgroup = FALSE,
#   prediction = FALSE,
#   subgroup = confirm
# )

# GLMM
library(GLMMadaptive)
rnmb_meta_collapsed_glmm <- metaprop(rnmb9_n, arm_n,
  data = conf_meta_collapsed,
  studlab = study,
  method = "GLMM",
  sm = "PLOGIT",
  method.tau = "ML",
  incr = 0,
  hakn = TRUE,
  prediction.subgroup = FALSE,
  prediction = FALSE,
  # subgroup = confirm,
  # control = list(package = "GLMMadaptive")
)

rnmb_meta_glmm_9 <- metaprop(rnmb9_n, arm_n,
  data = conf_meta_9,
  studlab = study,
  method = "GLMM",
  sm = "PLOGIT",
  method.tau = "ML",
  hakn = FALSE,
  # incr = 0,
  # prediction.subgroup = FALSE,
  prediction = FALSE,
  # subgroup = confirm,  
  # control = list(package = "GLMMadaptive")
)

## rrCalc arc sin ------------------------------------- (2022-03-23 07:43) @----
# use arcsin est and sd; backtransform simulated 
compare_ci_pas <- function(data_meta) {
  rnmb_pas <- update(data_meta, backtransf = FALSE)[c("TE.random.w", "seTE.random.w")] %>% unlist()
  set.seed(12345)
  rr <- (sin(rnorm(1000000, rnmb_pas[1], rnmb_pas[3])))^2 / (sin(rnorm(1000000, rnmb_pas[2], rnmb_pas[4])))^2
  rr <- quantile(rr, probs = c(0.025, 0.5, 0.975))
  paste0(round_2(rr[2]), " (95% CI: ", round_2(rr[1]), ", ", round_2(rr[3]), ")")
  # paste0(round_2(rr[2]), " (95% CI: ", rr[1], ", ", rr[3], ")")
}

## rrCalc logit --------------------------------------- (2022-07-25 09:06) @----
# use logit est and sd; backtransform simulated 
compare_ci_logit <- function(data_meta) {
  rnmb_logit <- update(data_meta, backtransf = FALSE)[c("TE.random.w", "seTE.random.w")] %>% unlist()
  set.seed(12345)
  rr <- (boot::inv.logit(rnorm(1000000, rnmb_logit[1], rnmb_logit[3])))^2 / (boot::inv.logit(rnorm(1000000, rnmb_logit[2], rnmb_logit[4])))^2
  rr <- quantile(rr, probs = c(0.025, 0.5, 0.975))
  paste0(round_2(rr[2]), " (95% CI: ", round_2(rr[1]), ", ", round_2(rr[3]), ")")
  # paste0(round_2(rr[2]), " (95% CI: ", rr[1], ", ", rr[3], ")")
}

rnmb_sug

  rnmb_logit <- update(data_meta, backtransf = FALSE)[c("TE.random.w", "seTE.random.w")] %>% unlist()
  set.seed(12345)
  rr <- 
    
    boot::inv.logit(
    rnorm(10, rnmb_sug[1], rnmb_sug[3]) 
  
  (boot::inv.logit(rnorm(1000000, rnmb_logit[2], rnmb_logit[4])))^2
  
  
  rr <- (boot::inv.logit(rnorm(1000000, rnmb_logit[1], rnmb_logit[3])))^2 / (boot::inv.logit(rnorm(1000000, rnmb_logit[2], rnmb_logit[4])))^2
  rr <- quantile(rr, probs = c(0.025, 0.5, 0.975))
  paste0(round_2(rr[2]), " (95% CI: ", round_2(rr[1]), ", ", round_2(rr[3]), ")")




```

<!-- <br/> -->

<!-- #   Pooled -->

<!-- <a id="confFig1"></a> -->

<!-- <br/> -->

<!-- <font size = 4> Figure `r figure_n`. Incidence of residual neuromuscular blockade (TOFR <0.9) in arms of randomized and nonrandomized studies using quantitative monitoring according to whether TOFR ≥0.9 was reported as confirmed prior to extubation (reversal with sugammadex). </font> -->

```{r metaSug, eval = FALSE, fig.align = "left", fig.width = 9.5, fig.height = 12}

## metaSug -------------------------------------------- (2022-03-24 10:18) @----
# rnmb_sug <- update(rnmb_meta_collapsed_glmm,
#   subset = arm == "Sug" & confirm == "Confirmed",
rnmb_sug <- update(rnmb_meta_glmm_9,
  # incr = 0,
  # subset = arm == "Sug" & confirm == "Confirmed ≥0.9",
  subgroup = confirm,
  # subset = arm == "Sug" & confirm %in% c("Confirmed ≥0.9", "Not confirmed"),
  subset = arm == "Neo" & confirm %in% c("Confirmed ≥0.9", "Not confirmed"),
  # subset = arm == "Sug" & confirm == "Not confirmed"
  # subset = arm == "Sug" & confirm == "Not stated"
  # subset = arm == "Sug" & confirm == "Qualitative assessment"
  # subset = arm == "Sug" & confirm == "Clinical/None/NS"
  # subset = arm == "Neo" & confirm == "Confirmed ≥0.9",
  # subset = arm == "Neo" & confirm == "Confirmed",
  # subset = arm == "Neo" & confirm == "Not confirmed"
  # subset = arm == "Neo" & confirm == "Not stated"
  # subset = arm == "Neo" & confirm == "Qualitative assessment"
  # subset = arm == "Neo" & confirm == "Clinical/None/NS"
  # remove Alday 2019 outlier
  # subset = arm == "Sug" & study != "Alday 2019",
  # compare confirm vs not confirmed
  # subset = arm == "Sug" & str_detect(confirm, "confirm"),
  # compare confirm vs not confirmed removing Alday 2019
  # subset = arm == "Sug" & str_detect(confirm, "confirm")  & study != "Alday 2019",
)

rnmb_sug

forest_conf(rnmb_sug)

rnmb_sug <- update(rnmb_meta_collapsed_glmm , 
  # subset = arm == "Sug",
  subgroup = confirm,
  subset = arm == "Sug" & confirm %in% c("Confirmed", "Not confirmed"),
  subset = arm == "Sug" & confirm %in% c("Confirmed", "Not confirmed") & study != "Alday 2019",
  # remove Alday 2019 outlier
  # subset = arm == "Sug" & study != "Alday 2019",
  # compare confirm vs not confirmed
  # subset = arm == "Sug" & str_detect(confirm, "confirm"),
  # compare confirm vs not confirmed removing Alday 2019
  # subset = arm == "Sug" & str_detect(confirm, "confirm")  & study != "Alday 2019",
)

forest_conf(rnmb_sug)
figure_n <- fig_inc()
```
<!-- <font size = 4>  -->

```{r riskratiosPas, eval = FALSE}
## quant monitoring all categories confirmed ---------- (2022-07-06 08:47) @----
rnmb_meta_ci <- metaprop(
  rnmb9_n, 
  arm_n,
  data = conf_meta_9,
  studlab = study,
  sm = "PAS",
  hakn = TRUE,
  prediction.subgroup = FALSE,
  prediction = FALSE,
  subgroup = confirm,
  backtransf = FALSE
)

## risk ratio ----------------------------------------- (2022-03-23 17:08) @----
rnmb_sug_meta_ci <- update(rnmb_meta_ci,
  # subset = arm == "Sug" & mon_cat_f == "Quant" & str_detect(confirm, "confirm"),
  subset = arm == "Sug" & str_detect(confirm, "onfirmed"),
  backtransf = FALSE,
)

compare_ci(rnmb_sug_meta_ci)

## exclude Alday 2019 --------------------------------- (2022-03-24 08:23) @----
rnmb_sug <- update(rnmb_sug_meta_9,
  subset = study != "Alday 2019",
  backtransf = FALSE,
)

compare_ci_pas(rnmb_sug)
compare_ci_glmm(rnmb_sug)

## assume all not stated confirmed or not ----------- (2022-03-24 09:57) @----
conf_meta_sens <- conf_meta_quant %>%
  mutate(
    # confirm = fct_recode(confirm, "Confirmed" = "Not stated")
    confirm = fct_recode(confirm, "Not confirmed" = "Not stated")
  )

rnmb_meta <- metaprop(rnmb9_n, arm_n,
  data = conf_meta_sens,
  studlab = study,
  sm = "PAS",
  hakn = TRUE,
  subset = arm == "Sug",
  subgroup = confirm,
  backtransf = FALSE
)

compare_ci(rnmb_meta)

```

<!-- <font size = 4> Risk Ratios  -->

<!-- arcsine -->
<!-- | Comparison                                  | RR (95% CI)       | -->
<!-- |:--------------------------------------------|:------------------| -->
<!-- | Confirmed vs. not confirmed                 | 0.11 (0.00, 0.99) | # -->
<!-- |    Removing Alday 2019                      | 0.21 (0.00, 1.81) | -->
<!-- | Assuming all not stated were confirmed      | 0.09 (0.00, 0.77) | -->
<!-- | Assuming all not stated were not confirmed  | 0.12 (0.00, 1.09) | -->

<!-- </font> -->

<!-- <font size = 3> Risk ratios obtained as the ratio (median, lower and upper 0.025 quantiles) sampled from the means and standard deviations of the respective comparator incidence proportions (1E^6^ samples). Arms from von Quillfeldt 2013 and Pecek 2015 confirmed at TOFR ≥ 0.8.  E-value point estimate of 28.1 (upper limit 2.4) for the main result. </font> -->

<!-- <br/> -->


# **Neostigmine**

<a id="confTab1"></a>

<br/>

<font size = 4> Table `r table_n`. Residual neuromuscular blockade in study arms according to TOFR confirmation prior to extubation when quantitative monitoring was used and in studies where quantitative monitoring was not used. Neostigmine given for reversal.</font>

```{r NeostigmineKbl}
## descriptive table ---------------------------------- (2022-03-26 15:30) @----
conf_kbl <- conf_meta |>
  # arrange(confirm, year, study, arm) %>%
  mutate(
    rnmb9_np = n_percent1(rnmb9_n, rnmb9_n / arm_n * 100),
    rnmb9_per = rnmb9_n / arm_n,
  ) |>
  select(refid, year, design_f, study, study_l, arm, arm_n, rnmb9_n, nmbagent, volatile, mon_cat_f, depth, rnmb_where, rnmb9_np, extbconf, confirm, rnmb9_per) |>
  # select only to go in meta
  filter(arm %in% c("Neo", "Neo"))

dichot_format <- function(x) (x/100)

conf_kbl %>%
  # temp <- conf_kbl %>%
  # temp <- table_tally_2(temp, confirm, design_f)
  # filter(mon_cat_f == "Quant") |> 
  filter(arm == "Neo") %>% 
  select(confirm, study, design_f, arm_n, nmbagent, volatile, depth, rnmb_where, rnmb9_np, rnmb9_per) %>% 
  mutate(
  rnmb_bar = case_when(
    confirm == "Confirmed ≥0.9" ~ bar_wn(rnmb9_per, rnmb9_per, color_1, 1),
    confirm == "Not confirmed" ~ bar_wn(rnmb9_per, rnmb9_per, color_4, 1),
    confirm == "Not stated"  ~ bar_wn(rnmb9_per, rnmb9_per, color_2, 1),
    confirm == "Confirmed ≥0.8/NS"  ~ bar_wn(rnmb9_per, rnmb9_per, color_3, 1),
    confirm == "Qualitative assessment"  ~ bar_wn(rnmb9_per, rnmb9_per, "#e74343", 1),
    confirm == "Clinical/None/NS"  ~ bar_wn(rnmb9_per, rnmb9_per, "#dc0c22", 1),
    ),
  # rnmb_bar = str_replace(rnmb_bar, ">\\d+\\.?\\d?", ",>&nbsp;"),
  rnmb_bar = str_replace(rnmb_bar, ">0\\.?\\d*", ",>&nbsp;"),
  nmbagent = firstup(str_extract(nmbagent, "^\\w{3}")),
  volatile = ifelse(volatile, "\U00D7", " "),
  ) %>% 
  select(-c(confirm, rnmb9_per)) %>% 
kbl(
    booktabs = T, align = c("llrccllll"), escape = FALSE, # format = "latex",
    col.names = c("Study", "Design", "N", "Agent", "Volatile", "Depth", "Place^a^", "N (%)", bar_ref),
  ) %>%
  add_header_above(c(" " = 5, "Reversal" = 1, "Residual Neuromuscular Blockade" = 3), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "4em") %>%
  column_spec(4, width = "4em") %>%
  column_spec(5, width = "5em") %>%
  column_spec(6, width = "7em") %>%
  column_spec(7, width = "6em") %>%
  column_spec(8, width = "6em") %>%
  column_spec(9, width = bar_width) %>% 
  pack_topnoind(., "Quantitative monitoring", 1, 41) %>% 
  pack_sub_bold_ind(., "Confirmed ≥ 0.9", 1, 10) %>%
  pack_sub_bold_ind(., "Confirmed ≥ 0.8/NS", 11, 15) %>%
  pack_sub_bold_ind(., "Not confirmed", 16, 31) %>%
  pack_sub_bold_ind(., "Not stated", 32, 41) %>%
  pack_top(., "Qualitative assessment", 42, 50) %>%
  pack_top(., "Clinical/None/NS", 51, 60) %>%
  footnote(
    general = "RCT: randomized controlled trial; NR Trial: nonrandomized trial; Prosp Cohort: prospective cohort; Retro Cohort: retrospective cohort; ROC: rocuronium; Vec: vecuronium; Var: various; Min: minimal; Mod: moderate; NS: not stated; PACU: post-anesthesia care unit; NS: not stated.",
    alphabet = c("Extubation includes designated in OR."),
    general_title = "",
    footnote_as_chunk = FALSE,
  )

table_n <- tab_inc()
```


<!-- <br/> -->

<!-- #   Pooled -->

<!-- <a id="confFig1"></a> -->

<!-- <br/> -->

<!-- <font size = 4> Figure `r figure_n`. Incidence of residual neuromuscular blockade (TOFR <0.9) in arms of randomized and nonrandomized studies using quantitative monitoring according to whether TOFR ≥0.9 was reported as confirmed prior to extubation (reversal with Neostigmine). </font> -->

```{r metaNeo, eval = FALSE, fig.align = "left", fig.width = 9.5, fig.height = 17}
## metaNeo -------------------------------------------- (2022-03-24 10:18) @----
rnmb_neo <- update(rnmb_meta, 
  subset = arm == "Neo"
  # remove Alday 2019 outlier
  # subset = arm == "Neo" & study != "Alday 2019",
  # compare confirm vs not confirmed
  # subset = arm == "Neo" & str_detect(confirm, "confirm"),
  # compare confirm vs not confirmed removing Alday 2019
  # subset = arm == "Neo" & str_detect(confirm, "confirm")  & study != "Alday 2019",
)

forest_conf(rnmb_neo)
figure_n <- fig_inc()
```


```{r riskratiosNeo, eval = FALSE}
## quant monitoring all categories confirmed ---------- (2022-07-06 08:47) @----
rnmb_meta_any <- metaprop(
  rnmb9_n, 
  arm_n,
  data = conf_meta_quant,
  studlab = study,
  sm = "PAS",
  hakn = TRUE,
  prediction.subgroup = FALSE,
  prediction = FALSE,
  subgroup = confirm
)

## risk ratio ----------------------------------------- (2022-03-23 17:08) @----
rnmb_neo_meta_any <- update(rnmb_meta_any,
  # subset = arm == "Neo" & mon_cat_f == "Quant" & str_detect(confirm, "confirm"),
  subset = arm == "Neo" & str_detect(confirm, "onfirmed"),
  backtransf = FALSE,
)

compare_ci(rnmb_neo_meta_any)

## assume all not stated confirmed or not ----------- (2022-03-24 09:57) @----
conf_meta_sens <- conf_meta_quant %>%
  mutate(
    confirm = fct_recode(confirm, "Confirmed" = "Not stated")
    # confirm = fct_recode(confirm, "Not confirmed" = "Not stated")
  )

rnmb_meta <- metaprop(rnmb9_n, arm_n,
  data = conf_meta_sens,
  studlab = study,
  sm = "PAS",
  hakn = TRUE,
  subset = arm == "Neo",
  subgroup = confirm,
  backtransf = FALSE
)

compare_ci(rnmb_meta)
```

<!-- <font size = 4> Risk Ratios   -->

<!-- | Comparison                                  | RR (95% CI)       | -->
<!-- |:--------------------------------------------|:------------------| -->
<!-- | Confirmed vs. not confirmed                 | 0.22 (0.09, 0.44) | -->
<!-- | Assuming all not stated were confirmed      | 0.24 (0.10, 0.48) | -->
<!-- | Assuming all not stated were not confirmed  | 0.31 (0.12, 0.68) | -->

<!-- </font> -->

<!-- <font size = 3> Risk ratios obtained as the ratio (median, lower and upper 0.025 quantiles) sampled from the means and standard deviations of the respective comparator incidence proportions (1E^6^ samples). Arms from Murphy 2008, Murphy 2011, Norton 2013, Thilen 2018, and Pecek 2015  confirmed at TOFR ≥ 0.8 or was not stated.  E-value point estimate of 8.6 (upper limit 4.0) for the main result. </font> -->

# **References**

<br/>

<a id="references"></a>
