---
title: "TOFR Confirmation (draft/preliminary)"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
output:
  html_document:
    font: Source Sans Pro
    theme: cosmo
    anchor_sections: TRUE
    toc_float: 
      collapsed: FALSE
      smooth_scroll: TRUE
    toc_depth: 3
    linkcolor: blue
  latex_engine: xelatex
  pdf_document:
    toc: yes
    toc_depth: '3'
# bibliography: "bib/kq4.bib"
# csl: jama.csl
# link-citations: yes
workflowr:
  suppress_report: false
nocite: '@*'
---

```{=html}
<style type="text/css">
  body{
  font-size: 9.5pt;
  font-family: Source Sans Pro;
}

.caption {
  font-size: 15px;
}

.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  color: #090909;
  background-color: #0909093d;
}

.lightable-classic.lightable-hover tbody tr:hover {
    background-color: #c5d4e4;
}
.btn-xs, .btn-group-xs>.btn { 
display: none; 
}

.btn-default {
display: none !important; 
}

.popover-title {
      font-size: 12px;
  }

.popover-content {
      font-size: 12px;
  }
  
.popover-content {
    background-color: white;
    <!-- color: #FFFFFF; -->
    padding: 2px;
  }

<!-- .arrow { -->
<!--   border-right-color: red !important; -->
<!-- } -->

<!-- :target {  /* fix target location so caption appears */ -->
<!--     display: block;     -->
<!--     position: relative;      -->
<!--     top: 10px; -->
<!--     visibility: hidden; -->
<!-- } -->

</style>

<script>
$(document).ready(function(){
    $('[data-toggle="popover"]').popover({html: true, placement: top});
});
</script>
```

```{r setup, include = FALSE}
## setup ---------------------------------------------- (2022-02-14 16:17) @----
knitr::opts_chunk$set(echo = TRUE)
source("code/readfiles_nmb_102721.R")
# index of tibbles
```

```{r rnmbDataExternal, eval = FALSE, echo = FALSE}
## rnmb extubation external data not included --------- (2022-03-19 17:44) @----
# study & design to add
study_add <- study_char.dat %>% 
  select(refid, study, year, design) 

# read excel file
ext_confirm_temp <- readxl::read_xlsx("data/Extubationconfirm_031722_mg.xlsx", sheet = "TOFR Confirm", range = "A1:Q104") %>%
  clean_names() %>%
  left_join(., study_add, by = "refid") %>%
  mutate(
    study = ifelse(is.na(study), str_extract(authors, "^\\w*"), study), # TODO: delete when distiller complete
    rnmb_n = as.numeric(str_extract(rnmb_np, "^\\d{1,3}")),
    tofr_conf = factor(tofr_confirm, levels = c("Yes", "No", "NS", "PNS"), labels = c("Yes", "No", "Not stated", "PNS")),
    tofr_conf_comb = fct_collapse(tofr_conf, No = c("No", "PNS")),
    volatile = case_when(
      str_detect(anesth, "Vol") ~ "Volatile",
      str_detect(anesth, "NS") ~ "NS/Missing",
      anesth == "TIVA" ~ "TIVA alone",
      is.na(anesth) ~ "NS/Missing",
    ),
    rnmb_def_comb = case_when(
      str_detect(rnmb_def, "0.9") ~ "0.9",
      str_detect(rnmb_def, "0.8") ~ "0.8",
      str_detect(rnmb_def, "0.7") ~ "0.7",
      str_detect(rnmb_def, "NS") ~ "NS",
    )
  ) %>%
  group_by(refid) %>%
  fill(study) %>%
  ungroup() %>% # TODO: delete when distiller complete
  select(refid, design_f, study, year, rev_agent, rnmb_n, arm_n, volatile, monitor, tofr_conf, tofr_conf_comb, tofr_ext, rnmb_def, rnmb_def_comb, rnmb_monitor, depth) %>%
  rename(arm = rev_agent)

# unique refids # NOTE: 65 studies in excel file
ext_conf_refid <- sort(unique(ext_confirm_temp$refid))

temp <- ext_confirm_temp %>% 
  select(refid, study) %>% 
  arrange(refid) %>% 
  distinct()

# write_csv(temp, "/Users/mgrant/Desktop/excel_refid_study.csv", na = "")

# in excel file not distiller non missing extbconf
# study_char.dat %>% 
#   filter(refid %in% ext_conf_refid[!ext_conf_refid %in% extb_refids]) %>% 
#   select(refid, study, age)

# in distiller not in excel
# temp <- study_char.dat %>%
#   filter(refid %in% extb_refids[extb_refids %notin% ext_conf_refid]) %>% 
#   select(refid, study, age)
# 
# write_csv(temp, "/Users/mgrant/Desktop/distiller_not_excel.csv", na = "")

```

```{r dataBaseRev}
## data/refids ---------------------------------------- (2022-02-15 10:28) @----
# NOTE analysis flow
# - studies with confirmation data (yes/no/not stated) extb_refids
# - studies with rnmb data
# - studies rnmb + confirmation
# - study_char_conf.dat, study_arm_conf.dat, dichot_conf.dat
# - studies 0.9 confirm and 0.9 rnmb
# - combine arms, 6 studies (avoid dependencies/hlm); limitations 
# - conf_meta data set
# - descriptive table
# - pooled
# - sensitivity
# - forest plots
# - risk of bias

## confirm extubation refids [extb_refids] ------------ (2022-03-25 12:42) @----
# TEXT: confirmation 
extb_refids <- study_arm.dat %>% 
  filter(!is.na(extbconf), age == "Adult") %>%
  pull(refid) %>% 
  unique()

## studies/arms tables (not run) ---------------------- (2022-03-25 19:00) @----
# study_arm.dat %>%
#   filter(refid %in% extb_refids) %>%
#   filter(age == "Adult") %>%
#   group_by(refid) %>%
#   slice(1) %>%
#   # tabyl(extbconf) %>%
#   # tabyl(tofrext) %>%
#   # summarize(total = sum(arm_n))
#   tabyl(design) %>%
#   adorn_totals()

# # number of studies
#        extbconf  n   percent
#              no 38 0.3838384
#              ns 26 0.2626263
#             yes 35 0.3535354
#           Total 99 1.0000000

# number of arms
#        extbconf  n   percent
#             no  78 0.3750000
#             ns  62 0.2980769
#            yes  68 0.3269231
#          Total 208 1.0000000

#         design  n    percent
#            rct 60 0.60606061
#      crossover  0 0.00000000
#        cluster  0 0.00000000
#   fully_paired  4 0.04040404
#       quasiexp  3 0.03030303
#           nrsi  9 0.09090909
#   prospect_coh 18 0.18181818
# retrospect_coh  5 0.05050505
#    casecontrol  0 0.00000000
#    case_series  0 0.00000000
#          other  0 0.00000000
#          Total 99 1.00000000

## rnmb extubation refids [extb_rnmb_refids] ---------- (2022-03-25 19:01) @----
# confirmation and rnmb data at any tofr
extb_rnmb_refids <- dichot.dat %>%
  filter(age == "Adult") %>% 
  filter(refid %in% extb_refids) %>% # comment out if checking refids below
  filter(if_any(c(rnmb1_n, rnmb2_n), ~ !is.na(.))) %>% 
  select(refid) %>%
  distinct() %>%
  pull()

# check refids confirmation w/wo extubation data; 99 with extubation confirm; 81 with rnmb 
# extb_refids %>% tibble(refid = .) %>% filter(refid %in% extb_rnmb_refids) %>% tally() # n = 86
# extb_refids %>% tibble(refid = .) %>% filter(refid %notin% extb_rnmb_refids) %>% tally() #  no rnmb data n = 13

## study char arm dichot ------------------------------ (2022-03-25 19:14) @----
study_char_conf.dat <- study_char.dat %>%
  filter(refid %in% extb_rnmb_refids) 

study_arm_conf.dat <- study_arm.dat %>%
  filter(refid %in% extb_rnmb_refids) %>%
  remove_empty(which = "cols") %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    ),
    arm = case_when(
      revagent %in% c("neo") ~ "Neo",
      revagent %in% c("sug") ~ "Sug",
      str_detect(study_arm_k, "pont") ~ "Spont",
      revagent %in% c("other_agent") ~ revother,
      TRUE ~ "Other"
    ),
    arm = ifelse(str_detect(arm, "lacebo|saline"), "Plac", arm),
    arm = ifelse(str_detect(arm, "yridostigmine"), "Pyrid", arm),
    arm = factor(arm, levels = c("Sug", "Neo", "Plac", "Spont", "Pyrid", "Other"), ordered = TRUE),
    volatile = if_any(c(an_isoflurane, an_sevoflurane, an_desf, an_hal), ~ !is.na(.))
  ) %>%
  select(refid, extbconf, tofrext, arm_id, year, design, arm_n, arm, age, depth_rev_f, nmbagent, volatile, mon_type, mon_cat, mon_cat_f)

# describe
# tab_lst(study_arm_conf.dat, c(tofrext, volatile, depth_rev_f:mon_cat_f))

dichot_conf.dat <- dichot.dat %>%
filter(refid %in% extb_rnmb_refids) %>%
  mutate(
    study = case_when(
      study == "Wu 2014" & arm_n < 50 ~ "Wu 2014 (Caucasian)",
      study == "Wu 2014" & arm_n >= 50 ~ "Wu 2014 (Chinese)",
      TRUE ~ study
    )
  ) %>%
  select(refid, arm_id, study, study_l, rnmb_location, rnmb1_where, rnmb2_where, matches("rnmb[1-2]_n"), matches("[rnmb][1-2]_9")) %>% 
  select(-contains("pval"), -contains("clin"), -contains("per")) %>% 
  left_join(., study_arm_conf.dat, by = c("refid", "arm_id")) %>% 
  relocate(c(year, design, arm, arm_n, age, extbconf, tofrext), .after = study_l)

# qinu(dichot_conf.dat, refid) n = 86 correct 2022/03/26 11:35

# select confirmed 0.9 and rnmb 0.9
conf_meta <- dichot_conf.dat %>%
  mutate(
    rnmb9_n = case_when(
      rnmb1_9 == "rnmb1_9" ~ rnmb1_n,
      rnmb2_9 == "rnmb2_9" ~ rnmb2_n,
    ),
    rnmb_where = case_when(
      rnmb1_9 == "rnmb1_9" ~ rnmb1_where,
      rnmb2_9 == "rnmb2_9" ~ rnmb2_where,
    ),
    rnmb_where = ifelse(is.na(rnmb_where), rnmb_location, rnmb_where),
    rnmb_where = ifelse(rnmb_where == "post_ext", "post_extub", rnmb_where),
    confirm = case_when(
      extbconf == "yes" & tofrext == "tofrext9" ~ "≥0.9 confirmed",
      extbconf == "yes" & str_detect(tofrext, "tofrext") ~ "≥0.7,0.8/NS confirmed",
      extbconf == "no" ~ "Not confirmed",
      extbconf == "ns" ~ "Not stated"
    ),
  ) %>%
  # filter(!is.na(rnmb9_n), mon_cat_f == "Quant", arm %in% c("Neo", "Sug")) %>%
  filter(!is.na(rnmb9_n), confirm %notin% "≥0.7,0.8/NS confirmed", mon_cat_f == "Quant", arm %in% c("Neo", "Sug")) %>%
  # NOTE: all studies used quantitive monitoring.
  mutate(confirm = ordered(confirm, levels = c("≥0.9 confirmed", "Not confirmed", "Not stated"))) %>%
  select(mon_cat_f, refid, study, year, design, age, arm, arm_n, rnmb9_n, rnmb_where, rnmb_location, extbconf, tofrext, confirm, nmbagent, volatile, mon_cat_f, depth_rev_f)

# collapse multiarm
remove <- c(1511, 2088, 3305, 2523, 2961, 2197)
temp_1 <- conf_meta %>%
  filter(refid %in% remove) %>%
  group_by(study, arm) %>%
  summarise(arm_n = sum(arm_n), rnmb9_n = sum(rnmb9_n), depth_rev_f = str_c(depth_rev_f, collapse = ":")) %>% 
  ungroup %>% 
  select(-arm)

temp_2 <- conf_meta %>% 
  filter(refid %in% remove) %>%
  group_by(study, arm) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-c(study, arm_n, rnmb9_n, depth_rev_f)) 

add <- bind_cols(temp_2, temp_1) %>% 
  select(names(conf_meta))

conf_meta <- conf_meta %>%
  filter(!refid %in% remove) %>%
  bind_rows(., add) %>%
  mutate(
    depth = as.character(depth_rev_f),
    depth = str_replace(depth, "mod:mod", "mod"),
    depth = str_replace(depth, "ns", "NS"),
    depth = str_replace(depth, "mod", "Mod"),
    depth = str_replace(depth, "deep", "Deep"),
    depth = str_replace(depth, "shall", "Shallow"),
    depth = str_replace(depth, "oth", "Other"),
    depth = str_replace(depth, "endsurg", "End surgery"),
    depth = str_replace(depth, "min", "Min"),
    depth = str_replace(depth, "Mod:Deep", "Deep:Mod")
  ) %>%
  left_join(., study_ident[, c("refid", "study_l", "design_f")], by = "refid") %>%
  select(-design) %>%
  mutate(
    design_f = fct_recode(design_f,
      "Before-After" = "Before-After/Time Series",
      "NR Trial" = "Nonrandomized Trial",
      "Prosp Coh" = "Prospective Cohort",
      "Retro Coh" = "Retrospective Cohort",
    )
  )

rm(add, remove, temp_1, temp_2)
```


## TOFR ≥0.9 Before Extubation

<br/>

### Sugammadex

<br/>

<font size = 4> Table `r table_n`. Study arms included in analyses of extubation confirmation with sugammadex. All studies utilized quantitative monitoring.</font>

```{r sugammadexKbl}
## descriptive table ---------------------------------- (2022-03-26 15:30) @----
conf_kbl <- conf_meta %>%
  arrange(confirm, year, study, arm) %>%
  mutate(rnmb9_np = n_percent1(rnmb9_n, rnmb9_n/arm_n * 100),
         rnmb9_per = rnmb9_n/arm_n) %>% 
  select(refid, year, design_f, study, arm, arm_n, rnmb9_n, nmbagent, volatile, mon_cat_f, depth, rnmb_where, rnmb9_np, extbconf, confirm, rnmb9_per) %>% 
  # select only to go in meta
  filter(arm %in% c("Neo", "Sug"))

# table_tally_2(temp, confirm, design)

#  1 ≥0.9 confirmed rct                1     6
#  2 ≥0.9 confirmed nrsi               7     7
#  3 Not confirmed  rct                8    13
#  4 Not confirmed  nrsi              14    14
#  5 Not confirmed  prospect_coh      15    17
#  6 Not confirmed  retrospect_coh    18    18
#  7 Not stated     rct               19    21
#  8 Not stated     nrsi              22    22
#  9 Not stated     prospect_coh      23    23
# 10 Not stated     retrospect_coh    24    24

dichot_format <- function(x) (x/100)

conf_kbl %>% 
  filter(arm == "Sug") %>% 
  select(confirm, study, design_f, arm_n, nmbagent, volatile, depth, rnmb_where, rnmb9_np, rnmb9_per) %>% 
  mutate(
  rnmb_bar = case_when(
    confirm == "≥0.9 confirmed" ~ bar_wn(rnmb9_per, rnmb9_per, color_4, 1),
    confirm == "Not confirmed" ~ bar_wn(rnmb9_per, rnmb9_per, color_3, 1),
    confirm == "Not stated"  ~ bar_wn(rnmb9_per, rnmb9_per, color_2, 1),
    ),
  # rnmb_bar = str_replace(rnmb_bar, ">\\d+\\.?\\d?", ",>&nbsp;"),
  rnmb_bar = str_replace(rnmb_bar, ">0\\.?\\d*", ",>&nbsp;"),
  nmbagent = firstup(str_extract(nmbagent, "^\\w{3}")),
  rnmb_where = case_when(
    rnmb_where == "ns" ~ "NS",
    rnmb_where %in% c("post_extub", "or") ~ "Extubation",
    rnmb_where == "pacu" ~ "PACU",
    rnmb_where == "recover" ~ "Recovery",
  ),
  volatile = ifelse(volatile, "\U00D7", " "),
  ) %>% 
  select(-c(confirm, rnmb9_per)) %>% 
kbl(
    booktabs = T, align = c("llrccllll"), escape = FALSE, # format = "latex",
    col.names = c("Study", "Design", "N", "Agent", "Volatile", "Depth", "Location^a^", "N (%)", bar_ref),
  ) %>%
  add_header_above(c(" " = 5, "Reversal" = 1, "Residual Neuromuscular Blockade" = 3), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "8em") %>%
  column_spec(3, width = "4em") %>%
  column_spec(4, width = "4em") %>%
  column_spec(5, width = "5em") %>%
  column_spec(6, width = "7em") %>%
  column_spec(7, width = "6em") %>%
  column_spec(8, width = "6em") %>%
  column_spec(9, width = bar_width) %>% 
  pack_topnoind(., "≥0.9 confirmed", 1, 7) %>%
  pack_topnoind(., "Not confirmed", 8, 18) %>%
  pack_topnoind(., "Not stated", 19, 24) %>%
  footnote(
    general = "RCT: randomized controlled trial; NR Trial: nonrandomized trial; Prosp Coh: prospective cohort; Retro Coh: retrospective cohort; ROC: rocuronium; Vec: vecuronium; Var: various; Min: minimal; Mod: moderate; NS: not stated; PACU: post-anesthesia care unit.",
    alphabet = c("Extubation includes designated in OR."),
    general_title = "",
    footnote_as_chunk = FALSE,
  )

table_n <- tab_inc()
```

```{r metaBaseCode}
## metaSug -------------------------------------------- (2022-03-23 07:42) @----
## forest function and base meta ---------------------- (2022-03-23 14:30) @----
forest_conf <- function(meta_result) {
  forest(meta_result,
    fixed = FALSE,
    rightcols = c("effect", "ci"),
    rightlabs = c("Incidence", "(95% CI)"),
    digits = 2,
    digits.tau2 = 1,
    overall.hetstat = TRUE,
    print.I2.ci = TRUE,
    prediction = FALSE,
    prediction.subroup = TRUE,
    fs.xlab = 11,
    pooled.events = TRUE,
    subgroup = TRUE,
    print.subgroup.name = FALSE,
    text.subgroup.nohet = TRUE,
    colgap.forest.left = "30mm",
    just.addcols.right = "left",
    xlim = c(0, 0.8),
    xlab = "Incidence TOFR <0.9"
  )
}

rnmb_meta <- metaprop(rnmb9_n, arm_n,
  data = conf_meta,
  studlab = study,
  sm = "PAS",
  hakn = TRUE,
  prediction.subgroup = FALSE,
  prediction = FALSE,
  subgroup = confirm
)

## rrCalc --------------------------------------------- (2022-03-23 07:43) @----
# use arcsin est and sd; backtransform simulated 
compare_ci <- function(data_meta) {
  rnmb_pas <- update(data_meta, backtransf = FALSE)[c("TE.random.w", "seTE.random.w")] %>% unlist()
  set.seed(12345)
  rr <- (sin(rnorm(1000000, rnmb_pas[1], rnmb_pas[3])))^2 / (sin(rnorm(1000000, rnmb_pas[2], rnmb_pas[4])))^2
  rr <- quantile(rr, probs = c(0.025, 0.5, 0.975))
  paste0(round_2(rr[2]), " (95% CI: ", round_2(rr[1]), ", ", round_2(rr[3]), ")")
}
```

<br/>

###   Pooled

<a id="kq4Fig1"></a>

<br/>

<font size = 4> Figure `r figure_n`. Incidence of residual neuromuscular block (TOFR \<0.9) in arms of randomized and nonrandomized studies using quantitative monitoring among patients reversed with sugammadex according to whether TOFR ≥0.9 was reported as confirmed prior to extubation. </font>

```{r metaSug, fig.align = "left", fig.width = 9.5, fig.height = 9}
## metaSug -------------------------------------------- (2022-03-24 10:18) @----
rnmb_sug <- update(rnmb_meta, 
  subset = arm == "Sug"
  # remove Alday 2019 outlier
  # subset = arm == "Sug" & study != "Alday 2019",
  # compare confirm vs not confirmed
  # subset = arm == "Sug" & str_detect(confirm, "confirm"),
  # compare confirm vs not confirmed removing Alday 2019
  # subset = arm == "Sug" & str_detect(confirm, "confirm")  & study != "Alday 2019",
)

forest_conf(rnmb_sug)

figure_n <- fig_inc()

## risk ratio ----------------------------------------- (2022-03-23 17:08) @----
# rnmb_sug <- update(rnmb_meta,
#   # subset = arm == "Sug" & mon_cat_f == "Quant" & str_detect(confirm, "confirm"),
#   subset = arm == "Sug" & str_detect(confirm, "confirm"),
#   backtransf = FALSE,
# )
# compare_ci(rnmb_sug)

## exclude Alday 2019 --------------------------------- (2022-03-24 08:23) @----
# rnmb_sug <- update(rnmb_meta,
#   subset = arm == "Sug" & study != "Alday 2019" & str_detect(confirm, "confirm"),
#   backtransf = FALSE,
# )
# compare_ci(rnmb_sug)

# # ## assume all not stated confirmed or not ----------- (2022-03-24 09:57) @----
# conf_meta_sens <- conf_meta %>%
#   mutate(
#     # confirm = fct_recode(confirm, "≥0.9 confirmed" = "Not stated")
#     confirm = fct_recode(confirm, "Not confirmed" = "Not stated")
#   )
# 
# rnmb_meta <- metaprop(rnmb9_n, arm_n,
#   data = conf_meta_sens,
#   studlab = study,
#   sm = "PAS",
#   hakn = TRUE,
#   subset = arm == "Sug",
#   subgroup = confirm,
#   backtransf = FALSE
# )
# 
# compare_ci(rnmb_meta)

```
Mod: moderate; Min: minimal; Oth: other; NS: not stated.<br/> 
Difference between confirmed and not confirmed --- risk ratio 0.09 (95% CI: 0.00, 0.72). <br/>
Removing Alday 2019 — Risk Ratio 0.14 (95% CI: 0.00, 1.03)<br/>
Assuming all not stated were confirmed --- risk ratio 0.15 (95% CI: 0.01, 1.09). <br/>
Assuming all not stated were not confirmed --- risk ratio 0.14 (95% CI: 0.00, 1.05).

<br/><br/>

<a id="kq4Fig1"></a>

### Neostigmine

<br/>

<font size = 4> Table `r table_n`. Study arms included in analyses of extubation confirmation with neostigmine. All studies utilized quantitative monitoring.</font>

```{r neostigmineKbl}
## descriptive table ---------------------------------- (2022-03-26 15:30) @----
# table_tally_2(temp, confirm, design)

# 1 ≥0.9 confirmed rct                1     7
# 2 Not confirmed  rct                8    13
# 3 Not confirmed  nrsi              14    15
# 4 Not confirmed  prospect_coh      16    18
# 5 Not confirmed  retrospect_coh    19    19
# 6 Not stated     rct               20    24
# 7 Not stated     quasiexp          25    25
# 8 Not stated     nrsi              26    26
# 9 Not stated     prospect_coh      27    27

dichot_format <- function(x) (x/100)

conf_kbl %>% 
  filter(arm == "Neo") %>% 
  select(confirm, study, design_f, arm_n, nmbagent, volatile, depth, rnmb_where, rnmb9_np, rnmb9_per) %>% 
  mutate(
  rnmb_bar = case_when(
    confirm == "≥0.9 confirmed" ~ bar_wn(rnmb9_per, rnmb9_per, color_4, 1),
    confirm == "Not confirmed" ~ bar_wn(rnmb9_per, rnmb9_per, color_3, 1),
    confirm == "Not stated"  ~ bar_wn(rnmb9_per, rnmb9_per, color_2, 1),
    ),
  # rnmb_bar = str_replace(rnmb_bar, ">\\d+\\.?\\d?", ",>&nbsp;"),
  rnmb_bar = str_replace(rnmb_bar, ">0\\.?\\d*", ",>&nbsp;"),
  nmbagent = firstup(str_extract(nmbagent, "^\\w{3}")),
  rnmb_where = case_when(
    rnmb_where == "ns" ~ "NS",
    rnmb_where %in% c("post_extub", "or") ~ "Extubation",
    rnmb_where == "pacu" ~ "PACU",
    rnmb_where == "recover" ~ "Recovery",
  ),
  volatile = ifelse(volatile, "\U00D7", " "),
  ) %>% 
  select(-c(confirm, rnmb9_per)) %>% 
kbl(
    booktabs = T, align = c("llrccllll"), escape = FALSE, # format = "latex",
    col.names = c("Study", "Design", "N", "Agent", "Volatile", "Depth", "Location^a^", "N (%)", bar_ref),
  ) %>%
  add_header_above(c(" " = 5, "Reversal" = 1, "Residual Neuromuscular Blockade" = 3), line = TRUE, bold = TRUE) %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(full_width = FALSE, bootstrap_options = opt_boot, position = "left") %>%
  kable_classic(full_width = FALSE, html_font = opt_font, position = "left", "hover") %>%
  column_spec(1, width = study_width) %>%
  column_spec(2, width = "8em") %>%
  column_spec(3, width = "4em") %>%
  column_spec(4, width = "4em") %>%
  column_spec(5, width = "5em") %>%
  column_spec(6, width = "7em") %>%
  column_spec(7, width = "6em") %>%
  column_spec(8, width = "6em") %>%
  column_spec(9, width = bar_width) %>% 
  pack_topnoind(., "≥0.9 confirmed", 1, 7) %>%
  # pack_sub_bold(., "RCT", 1, 6) %>% 
  # pack_sub_bold(., "Nonrandomized Trial", 7, 7) %>% 
  pack_topnoind(., "Not confirmed", 8, 19) %>%
  # pack_sub_bold(., "RCT", 8, 13) %>% 
  # pack_sub_bold(., "Nonrandomized Trial", 14, 14) %>%
  # pack_sub_bold(., "Prospective Cohort", 15, 17) %>% 
  # pack_sub_bold(., "Retrospective Cohort", 18, 18) %>% 
  pack_topnoind(., "Not stated", 20, 27) %>%
  # pack_sub_bold(., "RCT", 19, 21) %>% 
  # pack_sub_bold(., "Nonrandomized Trial", 22, 22) %>%
  # pack_sub_bold(., "Prospective Cohort", 23, 23) %>% 
  # pack_sub_bold(., "Retrospective Cohort", 24, 24) %>% 
  footnote(
    general = "RCT: randomized controlled trial; Quasi-exp: quasi-experimental; Prosp Coh: prospective cohort; Retro Coh: retrospective cohort; ROC: rocuronium; Vec: vecuronium; Var: various; Min: minimal; Mod: moderate; NS: not stated; PACU: post-anesthesia care unit.",
    alphabet = c("Extubation includes designated in OR."),
    general_title = "",
    footnote_as_chunk = FALSE,
  )

table_n <- tab_inc()
```

<br/>

###   Pooled

<br/>

<font size = 4> Figure `r figure_n`. Incidence of residual neuromuscular block (TOFR \<0.9) in arms of randomized and nonrandomized studies among patients reversed with neostigmine according to whether TOFR ≥0.9 was reported confirmed prior to extubation. </font>

```{r metaNeo, fig.align = "left", fig.width = 9.5, fig.height = 9.2}
## metaNeo -------------------------------------------- (2022-03-24 10:18) @----
rnmb_neo <- update(rnmb_meta,
  subset = arm == "Neo"
  # subset = arm == "Neo" & str_detect(confirm, "confirm"), 
)

forest_conf(rnmb_neo)
figure_n <- fig_inc()

## risk ratio ----------------------------------------- (2022-03-23 17:08) @----
# rnmb_neo <- update(rnmb_meta,
#   # subset = arm == "Neo" & str_detect(confirm, "confirm"),
#   subset = arm == "Neo" & str_detect(confirm, "confirm"),
#   backtransf = FALSE,
# )
# compare_ci(rnmb_neo)

## assume all not stated confirmed or not ------------- (2022-03-24 09:57) @----
# conf_meta_sens <- conf_meta %>%
#   mutate(
#     # confirm = fct_recode(confirm, "≥0.9 confirmed" = "Not stated")
#     confirm = fct_recode(confirm, "Not confirmed" = "Not stated")
#   )
# # 
# rnmb_meta <- metaprop(rnmb9_n, arm_n,
#   data = conf_meta_sens,
#   studlab = study,
#   sm = "PAS",
#   hakn = TRUE,
#   subset = arm == "Neo",
#   subgroup = confirm,
#   backtransf = FALSE
# )
# 
# compare_ci(rnmb_meta)
```

Mod: moderate; Min: minimal; Oth: other; NS: not stated.<br/> Difference between confirmed and not confirmed --- risk ratio 0.13 (95% CI: 0.05, 0.30). <br/> 
Assuming all not stated were confirmed --- risk ratio 0.27 (95% CI: 0.08, 0.65). <br/> 
Assuming all not stated were not confirmed --- risk ratio 0.17 (95% CI: 0.07, 0.39). <br/>

<br/><br/>
